### 2017-04-24 PaperBCJ.tex

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Detecci\'on de malas hierbas a través\\ de técnicas de redes neuronales convolucionales y visión artificial}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Andrea Córdova Cruzatty}
\IEEEauthorblockA{Departamento de Energía y Mecánica\\Ingeniería Mecatrónica\\
Universidad de las Fuerzas Armadas ESPE \\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2017-04-24 PaperBCJ.tex
Corregido archivo de las tildes

@@
 % Do not put math or special symbols in the title.
-\title{Detecci\'on de malas hierbas a través\\ de técnicas de redes neuronales convolucionales y visión artificial}
+\title{Detecci\'on de malas hierbas a trav\'es\\ de t\'ecnicas de redes neuronales convolucionales y visi\'on artificial}
 
@@
 % affiliations
-\author{\IEEEauthorblockN{Andrea Córdova Cruzatty}
-\IEEEauthorblockA{Departamento de Energía y Mecánica\\Ingeniería Mecatrónica\\
+\author{\IEEEauthorblockN{Andrea C\'ordova Cruzatty}
+\IEEEauthorblockA{Departamento de Energ\'ia y Mec\'anica\\Ingenier\'ia Mecatr\'onica\\
 Universidad de las Fuerzas Armadas ESPE \\
-Atlanta, Georgia 30332--0250\\
+Latacunga, Georgia 30332--0250\\
 Email: http://www.michaelshell.org/contact.html}

### 2017-04-24 PaperBCJ.tex
Inclusion Correcta de Nombres

@@
 % affiliations
-\author{\IEEEauthorblockN{Andrea C\'ordova Cruzatty}
-\IEEEauthorblockA{Departamento de Energ\'ia y Mec\'anica\\Ingenier\'ia Mecatr\'onica\\
-Universidad de las Fuerzas Armadas ESPE \\
-Latacunga, Georgia 30332--0250\\
-Email: http://www.michaelshell.org/contact.html}
-\and
-\IEEEauthorblockN{Homer Simpson}
-\IEEEauthorblockA{Twentieth Century Fox\\
-Springfield, USA\\
-Email: homer@thesimpsons.com}
-\and
-\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-\IEEEauthorblockA{Starfleet Academy\\
-San Francisco, California 96678--2391\\
-Telephone: (800) 555--1212\\
-Fax: (888) 555--1212}}
-
+\author{\IEEEauthorblockN{Andrea Concepci\'on C\'ordova Cruzatty \IEEEauthorrefmark{1},
+Mauricio Daniel Barreno Barreno \IEEEauthorrefmark{2} and Jos\'e Misael J\'acome Barrionuevo\IEEEauthorrefmark{3}}
+\IEEEauthorblockA{Department of Energy and Mechanics,
+University of the Army ESPE\\
+Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
+Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
+\IEEEauthorrefmark{2}mdbarreno@espe.edu.ec,
+\IEEEauthorrefmark{3}jmjacome1@espe.edu.ec}}
 % conference papers do not typically use \thanks and this command

### 2017-05-04 PaperBCJ.tex
Subsecciones agregadas
Fist part of the State of the Art

@@
 \begin{abstract}
-The abstract goes here.
+Today the computation stays i 
 \end{abstract}
@@
 % no \IEEEPARstart
-This demo file is intended to serve as a ``starter file''
-for IEEE conference papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8b and later.
+
 % You must have at least 2 lines in the paragraph with the drop letter
@@
 Subsubsection text here.
+
+\section{State of Art}
+Along the last centuries there had been developed  huge progress in the science and technology, significant milestones such as Communications, Computer Numerical Control and the miniaturization of components has permitted to the social and industrial sectors to benefit in order to reach their objectives.
+
+The globalization in the world also allow to countries like Ecuador(which isn’t larger producer of technology) to receive products and technological knowledge to satisfy requirements o propose   solutions for problems of the country still unresolved.
+
+The transformation of the industry is a example of the evolution of the science, the Manufacturing , the Food and Drink,Information Industries, etc.
+are signs of this industrial revolution.
+However there are fields still unexplored  in Ecuador like the agroindustry.
+Agriculture in Ecuador has changed a bit since the epoch of the Incas, it isn’t so bad mainly due there are good agriculture knowledge like terraces but the faulty exploitation of technological resources make impossible to the country to exploit its true potential like agricultural producer.
+
+Today the agriculture has many challenges for the Precision Agriculture such as the Weed and Crop segmentation \cite{Brivot:Marchant} ,
+
+\section{Implementation of the Algorithm}
+%Codigo para la Implementacion del Algoritmo
+
+\section{Test}
+%Codigo para la Implementacion del Algoritmo
 
@@
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+\bibitem{Brivot:Marchant}
+R.~Brivot and J.~A. Marchant, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images}\hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proc-Vis Image Signal Process, 1996.
+
+\bibitem{IEEEhowto:yo}
+Youtube, \emph{Gmail \LaTeX}, 3rd~ed.\hskip 1em plus
   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

### 2017-05-04 PaperBCJ.tex
Without references, Second Part of State of Art

@@
 
-Today the agriculture has many challenges for the Precision Agriculture such as the Weed and Crop segmentation \cite{Brivot:Marchant} ,
+Today the agriculture has many challenges for the Precision Agriculture such as the Weed and Crop segmentation, according to Suarez, Piñero y Valladores, el yield of the corn is affected by 5000 kg/ha.
+Actually the growing development of techniques of Artificial Vision and Machine Learning permit to researchers propose solutions for the Segmentation of Weeds in Crops.
+
+One of the first approximations to the algorithms of detection of Crops is the developed in 1996 by Brivot and Mercant, this could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
+In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently Chend and Mason had developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN(Density-based spartial clustering of apllications with noise) as Machine Learnin, it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice.
+Hong, Lei and Heping use an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, Araguez et.
+al perform their analysis through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
+Su Hnin Hlaing1, Aung Soe Khaing used the binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+Romeo et.
+al propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
+Potena, Nardi and Pretto use a multispectral camera to obtain RGB and NIR images, for the segmentation and classification they use a light CNN for the first process and a Deep CNN for classification, its accuracy is up to 98\%.
+There is an approximation to Cicco, Potena, Griseeti CNN through the generation of datasets
 

### 2017-05-05 PaperBCJ.tex
Revisions of the State of art

--- 2017-04-24 PaperBCJ.tex
@@
 Subsubsection text here.
+
+\section{State of Art}
+During the last centuries, huge progress has taken place in science and technology developments.
+Significant milestones such as Communications, Numerical Computer Control and the miniaturization of components have benefited social and industrial sectors on its approach to solve specific problems.
+\\
+Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive leading edge technological products in order to satisfy requirements and propose   solutions to still-unresolved problems.
+\\
+Industry transformation is a science evolution example; manufacturing, food, and information industries, among others, are signs of this industrial revolution.
+However there are fields still unexplored  in Ecuador like agroindustry.
+Agriculture in Ecuador has not changed much since precolombine times; while it is true that there are efficient agriculture practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer.
+\\
+Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation.
+There are studies that show the impact of Weed in corn crops \cite{Suarez:Pinero}; its yield is affected by 5000 kg/ha.
+Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops.
+\\
+One of the first approximations to the algorithms of detection of Crops is the developed \cite{Brivot:Marchant}, this could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
+In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently Chend and Mason had developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN(Density-based spartial clustering of apllications with noise) as Machine Learnin, it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice.
+Hong, Lei and Heping use an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, Araguez et.
+al perform their analysis through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
+Su Hnin Hlaing1, Aung Soe Khaing used the binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+Romeo et.
+al propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
+Potena, Nardi and Pretto use a multispectral camera to obtain RGB and NIR images, for the segmentation and classification they use a light CNN for the first process and a Deep CNN for classification, its accuracy is up to 98\%.
+There is an approximation to Cicco, Potena, Griseeti CNN through the generation of datasets
+\\
+\section{Implementation of the Algorithm}
+%Codigo para la Implementacion del Algoritmo
+
+\section{Test}
+%Codigo para la Implementacion del Algoritmo
 
@@
 
+\bibitem{Suarez:Pinero}
+R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
+  0.5em minus 0.4em\relax Gij\'on: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.
+
+\bibitem{Brivot:Marchant}
+R.~Brivot and J.~A. Marchant, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
 \bibitem{IEEEhowto:kopka}

### 2017-05-10 PaperBCJ.tex
Add Matherial and Methods instead of Algorithm
Fix names of Bibliography

@@
 \\
+
 Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive leading edge technological products in order to satisfy requirements and propose   solutions to still-unresolved problems.
 \\
+
 Industry transformation is a science evolution example; manufacturing, food, and information industries, among others, are signs of this industrial revolution.
@@
 \\
+
 Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation.
@@
 \\
+
 One of the first approximations to the algorithms of detection of Crops is the developed \cite{Brivot:Marchant}, this could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
-In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently Chend and Mason had developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN(Density-based spartial clustering of apllications with noise) as Machine Learnin, it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice.
-Hong, Lei and Heping use an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, Araguez et.
-al perform their analysis through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
-Su Hnin Hlaing1, Aung Soe Khaing used the binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
-Romeo et.
-al propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
-Potena, Nardi and Pretto use a multispectral camera to obtain RGB and NIR images, for the segmentation and classification they use a light CNN for the first process and a Deep CNN for classification, its accuracy is up to 98\%.
-There is an approximation to Cicco, Potena, Griseeti CNN through the generation of datasets
+In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN(Density-based spartial clustering of apllications with noise) as Machine Learning, it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice.
+\cite{Hong:Lei} Other approximations are the use an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, \cite{Araguez}  perform their analysis through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
+\cite{Su:Hnin} used the binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+\cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
+\cite{Potena:Nardi} use a multispectral camera to obtain RGB and NIR images, for the segmentation and classification they use a light CNN for the first process and a Deep CNN for classification, its accuracy is up to 98\%.
+There is an approximation to \cite{Cicco:Potena} CNN through the generation of datasets
 \\
-\section{Implementation of the Algorithm}
+
+\section{Matherial and Methods}
 %Codigo para la Implementacion del Algoritmo
@@
 
+  \bibitem{Cheng:Mason}
+R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
+  \bibitem{Hong:Lei}
+R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
+  \bibitem{Araguez}
+D.~Abad\'ia, R.
+Aragu\'es, A.
+~Cirujeda, R.
+~del Hoyo, J.
+~Paniagua, T.
+~Seco, V.
+~Urdanoz, F.
+~Us\'on and C.
+~Zaragoza , \emph{SAAPIN: Un robot para el desherbado de cultivos y valoraci\'on de salinidad del suelo} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 206.
+
+ \bibitem{Su:Hnin}
+R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
+%Revisar la extension de los nombres  
+ \bibitem{Romeo}
+J.~Romeo, G. ~Pajares M. ~Montalvo, J.M. ~Guerrero, M. ~Guijarro, and A. ~Ribeiro, \emph{Crop Row Detection in Maize fields Inspired on the Human VIsual Perception} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2012.
+
+%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres
+ \bibitem{Potena:Nardi}
+ C.~Potena,  D.~Nardi and A. ~Pretto \emph{Fast and Accurate Crop and Weed Identification with Summarized Train Sets for Precision Agriculture} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
+%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
+ \bibitem{Cicco:Potena}
+ M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
 \bibitem{IEEEhowto:kopka}

### 2017-05-10 PaperBCJ.tex
First Cheng Bibliography

@@
 R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
-  0.5em minus 0.4em\relax Gij\'on: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.
+  0.5em minus 0.4em\relax Gij\'on , Spain: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.
 
@@
   \bibitem{Cheng:Mason}
-R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+B.~Cheng and E.T.
+~Matson, \emph{A Feature-Based Machine Learning Agent for Automatic Rice and Weed Discrimination} Artificial Intelligence and Soft Computing: 14th International Conference, ICAISC 2015 Part II \hskip 1em plus
+  0.5em minus 0.4em\relax Zakopane, Poland , 2015.
 
@@
 
+\bibliography{•}
+
 \end{thebibliography}

### 2017-05-11 PaperBCJ.tex
Pequeñas Correciones

@@
 
-\section{State of Art}
+\section{Introduction}
 During the last centuries, huge progress has taken place in science and technology developments.
@@
 
-Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive leading edge technological products in order to satisfy requirements and propose   solutions to still-unresolved problems.
+Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive bleeding edge technological products in order to satisfy requirements and propose solutions to still-unresolved problems.
 \\
@@
 
-One of the first approximations to the algorithms of detection of Crops is the developed \cite{Brivot:Marchant}, this could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
-In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN(Density-based spartial clustering of apllications with noise) as Machine Learning, it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice.
-\cite{Hong:Lei} Other approximations are the use an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, \cite{Araguez}  perform their analysis through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
-\cite{Su:Hnin} used the binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
-\cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
-\cite{Potena:Nardi} use a multispectral camera to obtain RGB and NIR images, for the segmentation and classification they use a light CNN for the first process and a Deep CNN for classification, its accuracy is up to 98\%.
-There is an approximation to \cite{Cicco:Potena} CNN through the generation of datasets
+One of the first approximations to the algorithms of detection of Crops was  developed in 1996\cite{Brivot:Marchant}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
+In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et.
+al} \cite{Araguez}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
+\\
+
+Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} methos trough binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+Romeo \textit{et.
+al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
+The segmentation of weed and crops is not closed in Color Images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
+One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets
 \\
@@
   \bibitem{Hong:Lei}
-R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+~Hong. Y. Jeon, ~Lei F. Tian  and ~Heping Zhu, \emph{Robust Crop and Weed Segmentation under Uncontrolled Outdoor Ilumination} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2011.
 
@@
 
-\bibliography{•}
-
 \end{thebibliography}

### 2017-05-17 PaperBCJ.tex
Habilitado Ingreso de Figuras
Start fo Convolutional Neural Networks

@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+\usepackage{graphicx}
 
@@
 % Do not put math or special symbols in the title.
-\title{Detecci\'on de malas hierbas a trav\'es\\ de t\'ecnicas de redes neuronales convolucionales y visi\'on artificial}
+\title{Weed and Corn segmentation through Convolutional Neuronal Networks }
 
@@
 
-Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} methos trough binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} through binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
 Romeo \textit{et.
 al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
-The segmentation of weed and crops is not closed in Color Images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
+\\
+
+The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
 One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets
@@
 
+\begin{figure}
+  \centering
+
+  \caption{Some figure}
+\end{figure}
+
+\subsection{Convolutional Neuronal Network}
+After the segmentation of the pictures have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}.
+Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants.
 \section{Test}
@@
   0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
+
+ \bibitem{Razavian}
+ A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
+
 \bibitem{IEEEhowto:kopka}

### 2017-05-17 PaperBCJ.tex
Dataset

--- 2017-05-11 PaperBCJ.tex
@@
 %Codigo para la Implementacion del Algoritmo
+Dataset Desciption:
+\\
+For the model we have two categories, the first maize in its initial stage, and the second weed, All images for the dataset were obtained from maize cultivations in their initial stage in Pillaro canton, where they had a total of 2000 images, of which 1600 images were used for the training and 400 for the validation, once obtained the images are processed by openCV to segment them and can be obtained as follows:
+\\
+\includegraphics[width=3in]{im1}\\[1ex]
 
@@
   0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
+
 \bibitem{IEEEhowto:kopka}

### 2017-05-19 PaperBCJ.tex

--- 2017-05-17 PaperBCJ.tex
@@
 %Codigo para la Implementacion del Algoritmo
+The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
+\\
+\subsection{Hardward}
+The card used is a Raspberry Pi 3.
+The camera used for both the sampling and the model was a RaspBerry Pi Camera module v2, 		which is configured to obtain a video at a resolution of 640 by 480 pixels , In order to improve the performance of image 	processing.
+\\
 
-\begin{figure}
+\subsection{Software}
+
+The programs / packages used were OpenCV and Qt, for the acquisition, segmentation of images, Cafe for the realization of neural networks,
+\\
+\subsection{Neural networks}
+For the training of neural networks we used an AlexNet architecture, but we do quizes with others architectures like Let Net, Inception Ned, but the results wont good.
+\\
+\subsection{Dataset Desciption}
+	\begin{figure}[!t]
+	For the model we have two categories, the first maize in its initial stage, and the second weed, All images for the dataset were obtained from maize cultivations in their initial stage in Pillaro canton, where they had a total of  2225 images, of which 1622 images were of maize and 603 of weed, once obtained the images are processed by openCV to segment them and can be obtained as follows:
+	\\
+
 	\centering
-
-  \caption{Some figure}
-\end{figure}
+	\includegraphics[width=2.5in]{im1}
+	\caption{Simulation results for the network.}
+	\label{fig_sim}
 
@@
 
+\end{figure}
+
 \section{Conclusion}

### 2017-05-19 PaperBCJ.tex
imagen
datas

@@
 \\
-\subsection{Hardward}
+\subsection{Hardware}
 The card used is a Raspberry Pi 3.
@@
 
-The programs / packages used were OpenCV and Qt, for the acquisition, segmentation of images, Cafe for the realization of neural networks,
+The packages used were OpenCV and c/++, for the acquisition, segmentation of images, Caffe an Cuda for the realization of neural networks,
 \\
@@
 \\
-\subsection{Dataset Desciption}
-	\begin{figure}[!t]
-	For the model we have two categories, the first maize in its initial stage, and the second weed, All images for the dataset were obtained from maize cultivations in their initial stage in Pillaro canton, where they had a total of  2225 images, of which 1622 images were of maize and 603 of weed, once obtained the images are processed by openCV to segment them and can be obtained as follows:
+For the model we have two categories, the first maize in its initial stage, and the second weed, We had a total of  2225 images, of which 1622 images were of maize and 603 of weed
 \\
 
+\subsection{Dataset Desciption}
+	Samples were obtained from images captured in maize fields in their initial stage, when there was no exaggerated presence of weeds in the culture, the camera was configured at a resolution of 640 by 480 pixels, to obtain raw samples of the two Categories to be classified.
+\\
+Then, through a digital image processing, the raw samples were segmented to differentiate them from the soil and other non-plant elements, thereby obtaining unique images from each class.
+\\
+Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it/'s the size of the layer of entrance of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, Which is the purpose of this document.
+
+	\begin{figure}[h]
 	\centering
@@
 	\label{fig_sim}
+	\end{figure}
 
@@
 Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants.
+
 	\section{Test}
@@
 	% \fnbelowfloat command of the stfloats package.
-
-\end{figure}
 

### 2017-06-01 PaperBCJ.tex
Add matherials and methods

--- 2017-05-19 PaperBCJ.tex
@@
 
-\section{Matherial and Methods}
-%Codigo para la Implementacion del Algoritmo
+\section{Matherials and Methods}
 The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
 \\
-\subsection{Hardward}
-The card used is a Raspberry Pi 3.
-The camera used for both the sampling and the model was a RaspBerry Pi Camera module v2, 		which is configured to obtain a video at a resolution of 640 by 480 pixels , In order to improve the performance of image 	processing.
+\subsection{Hardware}
+For the stages of obtaining images and training net we  used the following elements: A Raspberry Pi 3 with Pi Camera V2.1 for the record of images, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing.
+Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
 \\
@@
 
-The programs / packages used were OpenCV and Qt, for the acquisition, segmentation of images, Cafe for the realization of neural networks,
-\\
-\subsection{Neural networks}
-For the training of neural networks we used an AlexNet architecture, but we do quizes with others architectures like Let Net, Inception Ned, but the results wont good.
-\\
-\subsection{Dataset Desciption}
-	\begin{figure}[!t]
-	For the model we have two categories, the first maize in its initial stage, and the second weed, All images for the dataset were obtained from maize cultivations in their initial stage in Pillaro canton, where they had a total of  2225 images, of which 1622 images were of maize and 603 of weed, once obtained the images are processed by openCV to segment them and can be obtained as follows:
+For the application in this documents requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use  in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{OpenCV} in this  case, it was used for acquisition and segmentation of the sample images.
+Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,
 \\
 
+Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above.
+For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi we used the Pixel OS for acquire images and processing of the CNN.
+\\
+
+\subsection{Dataset Description}
+Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadoring Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
+\\
+
+Samples were obtained from images captured in those maize fields , we considered to choose Maize Crops where we could visually discriminate the plants of the crop and the weed.
+To record the samples we centered the camera insuring that the capture shows all the features of the maize plant, it was possible by monitoring the get of samples by an external display.
+An examples of the images captured are shown below.
+\\
+
+	\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.2in]{entradamaiz}
+	\caption{Crops chosen to obtain samples, notice that it is easy to discrimante weed from maize}
+	\label{fig_sim}
+	\end{figure}
+
+Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed.
+Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document.
+To highlight we had labelled the samples manually in two classes.
+In the following image we present the final results of the processed images that conform the dataset.
+
+	\begin{figure}[h]
 	\centering
 	\includegraphics[width=2.5in]{im1}
-	\caption{Simulation results for the network.}
+	\caption{ Segmented and Masked images of dataset Above: Weed, Below: Maize}
 	\label{fig_sim}
+	\end{figure}
+
+Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, because we will develop a  system  for classify the maize in any position , we considered to rotate the source sample to 90º,180º and 270º so the dataset will be treble, improving the accuracy of the model.
+\\
+
+For the Validation Phase, we had chosen randomly a fifth part of the total images of each class, so we have the following chart with the distribution of the dataset.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{||c c c c c||} 
+ \hline
+ Phase & Train & Validation & Test & Total \\ [0.5ex] 
+ \hline\hline
+ Maize & 7581 & 1895 & 787 & 9476 \\ 
+ Weed & 2023 & 505 & 300 & 2528\\[1ex] 
+ \hline
+\end{tabular}
+\caption{Distribution of the Dataset of each class}
+\label{table:1}
+\end{table}
 
 \subsection{Convolutional Neuronal Network}
-	After the segmentation of the pictures have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}.
+	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}.
 Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants.
+\\
+
+One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{Potena:Nardi}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+\\
+\begin{table}[h!]
+\centering
+\begin{tabular}{||c c c c c||} 
+ \hline
+ Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
+ \hline\hline
+ Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
+ Layers numbers & 9 & 11 & 8 & 4\\
+ Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
+ Iterations & 3000 & 3000 & 4500 & 3000 \\ 
+  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
+  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
+ \hline
+\end{tabular}
+\caption{Distribution of the Dataset of each class}
+\label{table:1}
+\end{table}
+
+Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
+The following picture shows the process of training of the cNET \\
+
+	\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.5in]{entrenamiento}
+	\caption{ Left: Accuracy vs Iterations, Right: Loss vs Iterations}
+	\label{fig_sim}
+	\end{figure}
+
 	\section{Test}
@@
 
-\end{figure}
-
 \section{Conclusion}
@@
 
+   \bibitem{OpenCV}
+ A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
+
+     \bibitem{caffe}
+Jia, Yangqing and Shelhamer, Evan and Donahue, Jeff and Karayev, Sergey and Long, Jonathan and Girshick, Ross and Guadarrama, Sergio and Darrell, Trevor, \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.
+
+       \bibitem{SengChang}
+Seng Chang \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.
+
 \bibitem{IEEEhowto:kopka}

### 2017-06-02 PaperBCJ.tex
Fix Training Graph

@@
 \subsection{Dataset Description}
-Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadoring Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
+Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
 \\
 
-Samples were obtained from images captured in those maize fields , we considered to choose Maize Crops where we could visually discriminate the plants of the crop and the weed.
-To record the samples we centered the camera insuring that the capture shows all the features of the maize plant, it was possible by monitoring the get of samples by an external display.
+Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed.
+Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples.
+To record the samples we centered the camera insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display.
 An examples of the images captured are shown below.
@@
 	\centering
-	\includegraphics[width=3.5in]{entrenamiento}
-	\caption{ Left: Accuracy vs Iterations, Right: Loss vs Iterations}
+	\includegraphics[width=3.2in]{entrenamiento}
+	\caption{ Graph of the Training Process }
 	\label{fig_sim}
@@
 
+       \bibitem{Fassio}
+Fassio, A., Carriquiry, A., Tojo, C. and Romero, R  \emph{MAIZ: Aspectos sobre fenolog\'ia}  \hskip 1em plus
+  0.5em minus 0.4em\relax Montevideo, Uruguay:Seria T\'ecnica Nº 101, 1998.
+
 \bibitem{IEEEhowto:kopka}

### 2017-06-02 PaperBCJ.tex
Fix Tables

@@
 \centering
-\begin{tabular}{||c c c c c||} 
+\begin{tabular}{|c | c | c | c | c|} 
  \hline
  Phase & Train & Validation & Test & Total \\ [0.5ex] 
- \hline\hline
+ \hline
  Maize & 7581 & 1895 & 787 & 9476 \\ 
@@
 \centering
-\begin{tabular}{||c c c c c||} 
+\begin{tabular}{|l c c c c|} 
  \hline
  Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
- \hline\hline
+ \hline
  Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
@@
   Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
- \hline
+ \hline \\
 \end{tabular}

### 2017-06-08 PaperBCJ.tex

@@
 \subsection{Hardware}
-For the stages of obtaining images and training net we  used the following elements: A Raspberry Pi 3 with Pi Camera V2.1 for the record of images, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing.
+For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image recording, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing.
 Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.

### 2017-07-04 PaperBCJ.tex
data

@@
 
-Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, because we will develop a  system  for classify the maize in any position , we considered to rotate the source sample to 90º,180º and 270º so the dataset will be treble, improving the accuracy of the model.
+Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{Sladojevic}  they measure that this allows to reduce the overfitting and to improve the presicion in the training, reason why we use rotations that go from the 30 to the 330 degrees in steps of 30, obtaining in this way to increase The date for 12 times and have better chances of recognizing plants that are in any orientation.
 \\
@@
 
+\bibitem{Sladojevic}
+S. Sladojevic,M. Arsenovic, A. Andarela, D. Culibrk and D, Stefanovic, \emph{Deep Neural Networks Based Recognition Diseases by Leaf Image Classification \LaTeX}, 3rd~ed.\hskip 1em plus
+  0.5em minus 0.4em\relax Trento, Italy: Srdjan Sladojevic, 2016.
+
 \end{thebibliography}

### 2017-07-04 PaperBCJ.tex
data

@@
 Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed.
-Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document.
-To highlight we had labelled the samples manually in two classes.
-In the following image we present the final results of the processed images that conform the dataset.
+Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document.\\
+	\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.2in]{procesamiento}
+	\caption{Preprocessing to obtain samples for the dataset}
+	\label{fig_sim}
+	\end{figure}
+
+To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.\\
 
@@
   Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
- \hline \\
+ \hline
 \end{tabular}  
 \caption{Distribution of the Dataset of each class}
+%%\endlastfoot
 \label{table:1} 
 \end{table}
-
 Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.

### 2017-07-05 PaperBCJ.tex
data

@@
 
-Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{Sladojevic}  they measure that this allows to reduce the overfitting and to improve the presicion in the training, reason why we use rotations that go from the 30 to the 330 degrees in steps of 30, obtaining in this way to increase The date for 12 times and have better chances of recognizing plants that are in any orientation.
+Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{Sladojevic}  they measure that this allows to reduce the overfitting and to improve the presicion in the training, reason why we use rotations that go from the 30 to the 330 degrees in steps of 30, obtaining in this way to increase the date for 12 times and have better chances of recognizing plants that are in any orientation.
 \\
@@
 The following picture shows the process of training of the cNET \\
+
+	\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.2in]{arquitectura}
+	\caption{ The schematic of CNet }
+	\label{fig_sim}
+	\end{figure}
 

### 2017-07-05 PaperBCJ.tex
new
Ingreso de Datos

--- 2017-07-04 PaperBCJ.tex
@@
+	
 %% bare_conf.tex
@@
 \usepackage{graphicx}
+\usepackage{array}
+\usepackage{caption}
+\captionsetup[table]{position=bottom}   %% or below
 
@@
 % Do not put math or special symbols in the title.
-\title{Weed and Corn segmentation through Convolutional Neuronal Networks }
+\title{Precise Weed and Maize classification through Convolutional Neuronal Networks }
 
@@
 \subsection{Hardware}
-For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image recording, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing.
+For the stages of obtaining images and training net we  used the following elements: A Raspberry Pi 3 with Pi Camera V2.1 for the record of images, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing.
 Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
@@
 
-Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{Sladojevic}  they measure that this allows to reduce the overfitting and to improve the presicion in the training, reason why we use rotations that go from the 30 to the 330 degrees in steps of 30, obtaining in this way to increase The date for 12 times and have better chances of recognizing plants that are in any orientation.
+Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, because we will develop a  system  for classify the maize in any position , we considered to rotate the source sample to 90º,180º and 270º so the dataset will be treble, improving the accuracy of the model.
 \\
@@
 \centering
-\begin{tabular}{|c | c | c | c | c|} 
+\begin{tabular}{| c | c | c | c | c |} 
  \hline
- Phase & Train & Validation & Test & Total \\ [0.5ex] 
+ Phase & Train & Validation & Test & Total \\ [1ex] 
  \hline
  Maize & 7581 & 1895 & 787 & 9476 \\ 
- Weed & 2023 & 505 & 300 & 2528\\[1ex] 
+ Weed & 2023 & 505 & 300 & 2528\\ 
  \hline
@@
  \hline
- Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
+ Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
  \hline
@@
   Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
- \hline \\
+ \hline 
 \end{tabular}
 \caption{Distribution of the Dataset of each class}
-\label{table:1}
+\label{table:2}
 \end{table}
 
-Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
-The following picture shows the process of training of the cNET \\
+Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
+The following picture shows the process of training of the cNET.
+\\
 
@@
 	\centering
-	\includegraphics[width=3.2in]{entrenamiento}
+	\includegraphics[width=2.3in]{entrenamiento}
 	\caption{ Graph of the Training Process }
@@
 
+Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
+To achive this, it was neccesary to reduce the number of filters from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.
+
 	\section{Test}
-	%Codigo para la Implementacion del Algoritmo
+
+For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|c|c|c|} 
+ \hline
+ \multicolumn{4}{ |c| }{GPU} \\
+ \hline
+   & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
+ \hline 
+ cNET(64 Filters) & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
+ \hline
+ cNET(16 Filters) & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
+  \hline
+ \multicolumn{4}{ |c| }{CPU} \\
+ \hline
+   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
+ \hline 
+ cNET(64 Filters) & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
+ \hline
+ cNET(16 Filters) & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
+  \hline
+ \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
+ \hline
+   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
+ \hline 
+ cNET(64 Filters) & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
+ \hline
+ cNET(16 Filters) & 85.71 & 87.13 & 951 us \\ [0.75ex]
+  \hline
+\end{tabular}
+\caption{Test}
+\label{table:2}
+\end{table}
 
@@
 
-\bibitem{Sladojevic}
-S. Sladojevic,M. Arsenovic, A. Andarela, D. Culibrk and D, Stefanovic, \emph{Deep Neural Networks Based Recognition Diseases by Leaf Image Classification \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Trento, Italy: Srdjan Sladojevic, 2016.
-
 \end{thebibliography}

### 2017-07-05 PaperBCJ.tex
Add Conclusions and Acknoledgements

--- 2017-07-05 PaperBCJ.tex
@@
 \caption{Distribution of the Dataset of each class}
-%%\endlastfoot
-\label{table:1} 
+\label{table:2}
 \end{table}
+
 Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
 The following picture shows the process of training of the cNET \\
+Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
+The following picture shows the process of training of the cNET.
+\\
+
+	\begin{figure*}[htb]
+	\centering
+	\includegraphics[width=6.5 in]{arquitectura}
+	\caption{ The schematic of CNet }
+	\label{fig_sim}
+	\end{figure*}
 
@@
 	\centering
-	\includegraphics[width=3.2in]{arquitectura}
-	\caption{ The schematic of CNet }
-	\label{fig_sim}
-	\end{figure}
-
-	\begin{figure}[h]
-	\centering
-	\includegraphics[width=3.2in]{entrenamiento}
+	\includegraphics[width=2.3in]{entrenamiento}
 	\caption{ Graph of the Training Process }
@@
 
+Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
+To achive this, it was neccesary to reduce the number of filters from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.
+
 	\section{Test}
-	%Codigo para la Implementacion del Algoritmo
+
+For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|c|c|c|} 
+ \hline
+ \multicolumn{4}{ |c| }{GPU} \\
+ \hline
+   & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
+ \hline 
+ cNET(64 Filters) & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
+ \hline
+ cNET(16 Filters) & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
+  \hline
+ \multicolumn{4}{ |c| }{CPU} \\
+ \hline
+   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
+ \hline 
+ cNET(64 Filters) & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
+ \hline
+ cNET(16 Filters) & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
+  \hline
+ \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
+ \hline
+   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
+ \hline 
+ cNET(64 Filters) & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
+ \hline
+ cNET(16 Filters) & 85.71 & 87.13 & 161 s \\ [0.75ex]
+  \hline
+\end{tabular}
+\caption{Test}
+\label{table:2}
+\end{table}
 
@@
 \section{Conclusion}
-The conclusion goes here.
+
+In this paper we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 99.33 \% of accuracy of training, using a dataset of both classes  of 44580 segmented images.
+\\
+
+In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuray of the net, it value fell 1 \% in comparation with the original net.
+\\
+
+Also, by using different methods to classify the images in our experiments, the results showed that the best time of classification was achieved by using a Nvidia Graphic Cards, this is due the Parallel Architecture that this GPU has and also it has fully support for the computation platform CUDA, it demostrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3.
+\\
+
+The study demostrated that is better to perform some geometrical tranformations to the Dataset images due it benefits to improve the  classification of plants because the plants ever have different orientations in the crop field.
 
@@
 
-The authors would like to thank...
+The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to obtain to conform the dataset of the project.
+\\
+
+This work has been supported by the University of the Army "ESPE"  Latacunga.
 

### 2017-07-06 PaperBCJ.tex
cambio
abstrac

@@
 \begin{abstract}
-Today the computation stays i 
+Deep Learning has played a very important role in modern times, being very used in artificial vision and especially in pattern recognition, which opens many doors in the fields of application among which is agriculture of presicion.
+In this paper we present the study of a convolutional neural network applied to the classification of plants of maize and weeds in real time, directed to fields of maize in its initial stage.
+The algorithm has two stages, segmentation of images and classification.
+In the segmentation it is sought to separate from the image the plants individually.
+While the classification is given through the convolutional neural network, previously trained with a dataset generated through the segmentation stage.The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results, we experimented by modifying its number of filters, to analyze their behavior.
+Finally, the resulting network was tested on different processors to compare classification times.\\
 \end{abstract}
@@
 \IEEEpeerreviewmaketitle
-
-\section{Introduction}
-% no \IEEEPARstart
-
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
-
-\hfill mds
-
-\hfill August 26, 2015
-
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
 
@@
 \centering
-\begin{tabular}{|l|c|c|c|} 
+\begin{tabular}{|l|c|c|p{2cm}|}  
  \hline
@@
  \hline
-   & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
+   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
  \hline 
- cNET(64 Filters) & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
+ 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
  \hline
- cNET(16 Filters) & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
+ 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
   \hline
@@
  \hline 
- cNET(64 Filters) & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
+ 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
  \hline
- cNET(16 Filters) & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
+ 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
   \hline
@@
  \hline 
- cNET(64 Filters) & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
+ 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
  \hline
- cNET(16 Filters) & 85.71 & 87.13 & 161 s \\ [0.75ex]
+ 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
   \hline
@@
 % (used to reserve space for the reference number labels box)
+%\bibliographystyle{IEEEtran}
+%\bibliography{/home/mauricio/PaperIEEE/ref.bib}
+
 \begin{thebibliography}{1}
 
+%\bibliographystyle{IEEEtran}
+%\bibliography{/home/mauricio/PaperIEEE/ref.bib}
+%\bibitem{ref}
 \bibitem{Suarez:Pinero}

### 2017-07-06 PaperBCJ.tex
cambios_tabla

@@
 
-Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed.
+Samples were obtained from images captured in those maize fields, we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed.
 Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples.
@@
 
-Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
+Inside of the shown parameters in the Table {table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
 The following picture shows the process of training of the cNET \\

### 2017-07-06 PaperBCJ.tex
Fixes until CNN
Fixes until CNN

@@
 \usepackage{array}
+\usepackage{filecontents}
 \usepackage{caption}
+\usepackage[noadjust]{cite}
 \captionsetup[table]{position=bottom}   %% or below
@@
 \begin{abstract}
-Deep Learning has played a very important role in modern times, being very used in artificial vision and especially in pattern recognition, which opens many doors in the fields of application among which is agriculture of presicion.
-In this paper we present the study of a convolutional neural network applied to the classification of plants of maize and weeds in real time, directed to fields of maize in its initial stage.
+Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture.
+In this paper we present the study of a convolutional neural network with two classes applied to the classification of plants of maize and weeds in real time, focused to fields of maize in its initial stage.
 The algorithm has two stages, segmentation of images and classification.
-In the segmentation it is sought to separate from the image the plants individually.
-While the classification is given through the convolutional neural network, previously trained with a dataset generated through the segmentation stage.The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results, we experimented by modifying its number of filters, to analyze their behavior.
+In the segmentation we wanted to separate the target plant from the original image.
+While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage.
+The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, we experimented by modifying its number of filters, to analyze their  behavior.
 Finally, the resulting network was tested on different processors to compare classification times.\\
@@
 Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation.
-There are studies that show the impact of Weed in corn crops \cite{Suarez:Pinero}; its yield is affected by 5000 kg/ha.
+There are studies that show the impact of Weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha.
 Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops.
@@
 
-One of the first approximations to the algorithms of detection of Crops was  developed in 1996\cite{Brivot:Marchant}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
-In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et.
-al} \cite{Araguez}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
+One of the first approximations to the algorithms of detection of Crops was  developed in 1996 \cite{brivot1996segmentation}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
+In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{cheng2015feature} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et.
+al} \cite{equipo2006proceedings}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
 \\
 
-Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} through binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+Hong and Lei \cite{jeon2011robust} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed an algorithm \cite{hlaing2014weed}, that through binarization methods of OTSU and Watershed for the segmentation of the images.
+While its classification was given through an areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
 Romeo \textit{et.
-al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
+al} \cite{romeo2012crop} propose to use a fuzzy clustering approach to correctly segment the crop green.
 \\
 
-The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
-One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets
+The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{potena2016fast} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
+One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{di2016automatic} achieving a acceptable accuracy for the generation of Datasets.
 \\
@@
 \subsection{Hardware}
-For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image recording, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing.
+For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image acquisition, it was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
 Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
+Also it was neccesary to consider the use of a CPU Core i7 2.7 Ghz, 8 cores and the CPU of the Raspberry Pi 3, a ARM Cortex-A53, 1.2GHz, 4 cores for testing the classification of images of the Network.
 \\
@@
 
-For the application in this documents requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use  in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{OpenCV} in this  case, it was used for acquisition and segmentation of the sample images.
-Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,
+For the application in this documents it requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{opencv_library} in this  case, it was used for acquisition and segmentation of the sample images.
+Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{jia2014caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,
 \\
@@
 \subsection{Dataset Description}
-Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
+Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
 \\
 
-Samples were obtained from images captured in those maize fields, we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed.
-Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples.
-To record the samples we centered the camera insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display.
+Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed.
+Maize in stages V3-V7(3-7 leafs) \cite{fassio1998maiz} were used to take samples.
+To record the samples we centered the camera over the target plant, insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display.
 An examples of the images captured are shown below.
-\\
 
@@
 
+Also it was neccesary  to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the Network to discriminate both classes of the Dataset. \\
+
 Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed.
-Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document.\\
+Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format.
+The process described before, was illustrated in the next figure.
+\\
 	\begin{figure}[h]
@@
 
-Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{Sladojevic}  they measure that this allows to reduce the overfitting and to improve the presicion in the training, reason why we use rotations that go from the 30 to the 330 degrees in steps of 30, obtaining in this way to increase the date for 12 times and have better chances of recognizing plants that are in any orientation.
+Once we completed the processing of the images, it were obtained 2835 images of Maize and 880 images of Weed, Lee \textit{et.
+al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{sladojevic2016deep}  they mention that this allows to reduce the overfitting and to improve the precision in the training, reason why we made 11 rotations each 30 degrees, obtaining in this way to increase the dataset in 12 times and have better chances of recognizing plants that are in any orientation.
 \\
@@
  \hline
- Maize & 7581 & 1895 & 787 & 9476 \\ 
- Weed & 2023 & 505 & 300 & 2528\\ 
+ Maize & 25695 & 8325 & 200 & 34220  \\ 
+ Weed & 8560 & 2000 & 200 & 10760\\ 
  \hline
@@
 \subsection{Convolutional Neuronal Network}
-	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}.
-Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants.
+	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{sharif2014cnn}.
+Their are also applied in Precision Agriculture \cite{potena2016fast} for the correct identification of plants.
 \\
 
-One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{Potena:Nardi}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
 \\
@@
 % (used to reserve space for the reference number labels box)
-%\bibliographystyle{IEEEtran}
-%\bibliography{/home/mauricio/PaperIEEE/ref.bib}
 
-\begin{thebibliography}{1}
-
-%\bibliographystyle{IEEEtran}
-%\bibliography{/home/mauricio/PaperIEEE/ref.bib}
-%\bibitem{ref}
-\bibitem{Suarez:Pinero}
-R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
-  0.5em minus 0.4em\relax Gij\'on , Spain: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.
-
-\bibitem{Brivot:Marchant}
-R.~Brivot and J.~A. Marchant, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
-
-  \bibitem{Cheng:Mason}
-B.~Cheng and E.T.
-~Matson, \emph{A Feature-Based Machine Learning Agent for Automatic Rice and Weed Discrimination} Artificial Intelligence and Soft Computing: 14th International Conference, ICAISC 2015 Part II \hskip 1em plus
-  0.5em minus 0.4em\relax Zakopane, Poland , 2015.
-
-  \bibitem{Hong:Lei}
-~Hong. Y. Jeon, ~Lei F. Tian  and ~Heping Zhu, \emph{Robust Crop and Weed Segmentation under Uncontrolled Outdoor Ilumination} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2011.
-
-  \bibitem{Araguez}
-D.~Abad\'ia, R.
-Aragu\'es, A.
-~Cirujeda, R.
-~del Hoyo, J.
-~Paniagua, T.
-~Seco, V.
-~Urdanoz, F.
-~Us\'on and C.
-~Zaragoza , \emph{SAAPIN: Un robot para el desherbado de cultivos y valoraci\'on de salinidad del suelo} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 206.
-
- \bibitem{Su:Hnin}
-R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
-
-%Revisar la extension de los nombres  
- \bibitem{Romeo}
-J.~Romeo, G. ~Pajares M. ~Montalvo, J.M. ~Guerrero, M. ~Guijarro, and A. ~Ribeiro, \emph{Crop Row Detection in Maize fields Inspired on the Human VIsual Perception} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2012.
-
-%Poner Bibliografia Correcta, Revisar	 si es neceario poner cuatro nombres
- \bibitem{Potena:Nardi}
- C.~Potena,  D.~Nardi and A. ~Pretto \emph{Fast and Accurate Crop and Weed Identification with Summarized Train Sets for Precision Agriculture} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
-
-%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
- \bibitem{Cicco:Potena}
- M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
-
- \bibitem{Razavian}
- A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
-
-   \bibitem{OpenCV}
- A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
-
-     \bibitem{caffe}
-Jia, Yangqing and Shelhamer, Evan and Donahue, Jeff and Karayev, Sergey and Long, Jonathan and Girshick, Ross and Guadarrama, Sergio and Darrell, Trevor, \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.
-
-       \bibitem{SengChang}
-Seng Chang \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.
-
-       \bibitem{Fassio}
-Fassio, A., Carriquiry, A., Tojo, C. and Romero, R  \emph{MAIZ: Aspectos sobre fenolog\'ia}  \hskip 1em plus
-  0.5em minus 0.4em\relax Montevideo, Uruguay:Seria T\'ecnica Nº 101, 1998.
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\bibitem{Sladojevic}
-S. Sladojevic,M. Arsenovic, A. Andarela, D. Culibrk and D, Stefanovic, \emph{Deep Neural Networks Based Recognition Diseases by Leaf Image Classification \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Trento, Italy: Srdjan Sladojevic, 2016.
-
-\end{thebibliography}
+\bibliographystyle{IEEEtran}
+\bibliography{bibliografiapaper}
 

### 2017-07-06 PaperBCJ.tex
Auto stash before merge of "master" and "origin/master"

@@
  Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
- Iterations & 3000 & 3000 & 4500 & 3000 \\ 
-  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
-  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
+ Iterations & 3000 & 3000 & 3000 & 3000 \\ 
+  Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
+  Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
  \hline 
@@
 
-Inside of the shown parameters in the Table {table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
-The following picture shows the process of training of the cNET \\
-Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
+Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission near to human classification.
 The following picture shows the process of training of the cNET.
@@
 Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
-To achive this, it was neccesary to reduce the number of filters from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.
+To achive this, it was neccesary to reduce the number of filters of cNET from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.
 
@@
 
-For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
+For this stage, we considered an extra dataset with 200 images of maize plants in stage of V3-V7 and 203 images of weed, obtained in maize crops, the results were comparated between cNET with 64 and 16 filters in the Table \ref{table:3}.\\
 \begin{table}[h!]
@@
 \caption{Test}
-\label{table:2}
+\label{table:3}
 \end{table}
+
+Like the table shown the results were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so we consider the RaspBerry Pi for the analysis of performance.
+With cNET of 64 filters the results fo time of classification was 615 miliseconds, so it time isn\'t the optimum for our objective that it is the processing in a real time.\\
 

### 2017-07-06 PaperBCJ.tex
modificacion_Imagen_arquitectura

@@
 
-Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission near to human classification.
-The following picture shows the process of training of the cNET.
-\\
+Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission near to human classification.\\
 
-	\begin{figure*}[htb]
+Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
+To achive this, it was neccesary to reduce the number of filters of cNET from 64 to 16.\\
+
+\begin{table}[h!]
 \centering
-	\includegraphics[width=6.5 in]{arquitectura}
-	\caption{ The schematic of CNet }
-	\label{fig_sim}
-	\end{figure*}
+\begin{tabular}{|l c c |} 
+ \hline
+ Parameters & cNET 16 filters & cNET 64 filters \\ [0.75ex] 
+ \hline
+ Number of parameters & 1651376 & 6421568 \\ 
+ Iterations & 9000 & 9000  \\ 
+  Accuracy(\%) & 97.26 & 96.40  \\
+  Loss(\%) & 8.39 & 14.48  \\ [1ex] 
+ \hline 
+\end{tabular}
+\caption{Distribution of the Dataset of each class}
+\label{table:3}
+\end{table}
+
+This permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy.\\
 
@@
 	\centering
-	\includegraphics[width=2.3in]{entrenamiento}
+	\includegraphics[width=3.6 in]{arquitectura}
+	\caption{ The schematic of CNet }
+	\label{fig_sim}
+	\end{figure}
+
+	\begin{figure}[h]
+	\centering
+	\includegraphics[width=2.4in]{entrenamiento}
 	\caption{ Graph of the Training Process }
@@
 
-Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
-To achive this, it was neccesary to reduce the number of filters of cNET from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.
+The before pictures shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\
 
@@
 
-For this stage, we considered an extra dataset with 200 images of maize plants in stage of V3-V7 and 203 images of weed, obtained in maize crops, the results were comparated between cNET with 64 and 16 filters in the Table \ref{table:3}.\\
+For this stage, we considered an extra dataset with 200 images of maize plants in stage of V3-V7 and 203 images of weed, obtained in maize crops, the results were comparated between cNET with 64 and 16 filters in the Table \ref{table:4}.\\
 \begin{table}[h!]
@@
 \caption{Test}
-\label{table:3}
+\label{table:4}
 \end{table}

### 2017-07-06 PaperBCJ.tex
modifaciones
06-julio

--- 2017-07-06 PaperBCJ.tex
@@
-	
 %% bare_conf.tex
@@
 \usepackage{graphicx}
-\usepackage{array}
-\usepackage{filecontents}
-\usepackage{caption}
-\usepackage[noadjust]{cite}
-\captionsetup[table]{position=bottom}   %% or below
 
@@
 % Do not put math or special symbols in the title.
-\title{Precise Weed and Maize classification through Convolutional Neuronal Networks }
+\title{Weed and Corn segmentation through Convolutional Neuronal Networks }
 
@@
 \begin{abstract}
-Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture.
-In this paper we present the study of a convolutional neural network with two classes applied to the classification of plants of maize and weeds in real time, focused to fields of maize in its initial stage.
-The algorithm has two stages, segmentation of images and classification.
-In the segmentation we wanted to separate the target plant from the original image.
-While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage.
-The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, we experimented by modifying its number of filters, to analyze their  behavior.
-Finally, the resulting network was tested on different processors to compare classification times.\\
+Today the computation stays i 
 \end{abstract}
@@
 \section{Introduction}
-During the last centuries, huge progress has taken place in science and technology developments.
-Significant milestones such as Communications, Numerical Computer Control and the miniaturization of components have benefited social and industrial sectors on its approach to solve specific problems.
+% no \IEEEPARstart
+
+% You must have at least 2 lines in the paragraph with the drop letter
+% (should never be an issue)
+I wish you the best of success.
+
+\hfill mds
+
+\hfill August 26, 2015
+
+\subsection{Subsection Heading Here}
+Subsection text here.
+
+\subsubsection{Subsubsection Heading Here}
+Subsubsection text here.
+
+\section{Introduction}
+During the last centuries, significant progress has taken place in science and technology developments.
+Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems differently.
 \\
 
-Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive bleeding edge technological products in order to satisfy requirements and propose solutions to still-unresolved problems.
+The availability of leading edge technologies  has considerably increased, thus becoming more accessible to people.
+This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.
+
 \\
 
-Industry transformation is a science evolution example; manufacturing, food, and information industries, among others, are signs of this industrial revolution.
-However there are fields still unexplored  in Ecuador like agroindustry.
-Agriculture in Ecuador has not changed much since precolombine times; while it is true that there are efficient agriculture practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer.
+Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with industrial revolution.
+However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
+Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer.
+Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality.
 \\
@@
 Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation.
-There are studies that show the impact of Weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha.
+There are studies that show the impact of Weed in corn crops \cite{Suarez:Pinero}; its yield is affected by 5000 kg/ha.
 Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops.
@@
 
-One of the first approximations to the algorithms of detection of Crops was  developed in 1996 \cite{brivot1996segmentation}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
-In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{cheng2015feature} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et.
-al} \cite{equipo2006proceedings}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
+One of the first approximations to the algorithms of detection of Crops was  developed in 1996\cite{Brivot:Marchant}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
+In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et.
+al} \cite{Araguez}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
 \\
 
-Hong and Lei \cite{jeon2011robust} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed an algorithm \cite{hlaing2014weed}, that through binarization methods of OTSU and Watershed for the segmentation of the images.
-While its classification was given through an areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} through binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
 Romeo \textit{et.
-al} \cite{romeo2012crop} propose to use a fuzzy clustering approach to correctly segment the crop green.
+al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
 \\
 
-The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{potena2016fast} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
-One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{di2016automatic} achieving a acceptable accuracy for the generation of Datasets.
+The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
+One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets
 \\
@@
 \subsection{Hardware}
-For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image acquisition, it was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
+For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image recording, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing.
 Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
-Also it was neccesary to consider the use of a CPU Core i7 2.7 Ghz, 8 cores and the CPU of the Raspberry Pi 3, a ARM Cortex-A53, 1.2GHz, 4 cores for testing the classification of images of the Network.
 \\
@@
 
-For the application in this documents it requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{opencv_library} in this  case, it was used for acquisition and segmentation of the sample images.
-Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{jia2014caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,
+For the application in this documents requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use  in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{OpenCV} in this  case, it was used for acquisition and segmentation of the sample images.
+Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,
 \\
@@
 \subsection{Dataset Description}
-Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
+Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
 \\
@@
 Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed.
-Maize in stages V3-V7(3-7 leafs) \cite{fassio1998maiz} were used to take samples.
-To record the samples we centered the camera over the target plant, insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display.
+Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples.
+To record the samples we centered the camera insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display.
 An examples of the images captured are shown below.
+\\
 
@@
 
-Also it was neccesary  to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the Network to discriminate both classes of the Dataset. \\
-
 Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed.
-Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format.
-The process described before, was illustrated in the next figure.
-\\
-	\begin{figure}[h]
-	\centering
-	\includegraphics[width=3.2in]{procesamiento}
-	\caption{Preprocessing to obtain samples for the dataset}
-	\label{fig_sim}
-	\end{figure}
-
-To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.\\
+Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document.
+To highlight we had labelled the samples manually in two classes.
+In the following image we present the final results of the processed images that conform the dataset.
 
@@
 
-Once we completed the processing of the images, it were obtained 2835 images of Maize and 880 images of Weed, Lee \textit{et.
-al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{sladojevic2016deep}  they mention that this allows to reduce the overfitting and to improve the precision in the training, reason why we made 11 rotations each 30 degrees, obtaining in this way to increase the dataset in 12 times and have better chances of recognizing plants that are in any orientation.
+Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, because we will develop a  system  for classify the maize in any position , we considered to rotate the source sample to 90º,180º and 270º so the dataset will be treble, improving the accuracy of the model.
 \\
@@
 \centering
-\begin{tabular}{| c | c | c | c | c |} 
+\begin{tabular}{|c | c | c | c | c|} 
  \hline
- Phase & Train & Validation & Test & Total \\ [1ex] 
+ Phase & Train & Validation & Test & Total \\ [0.5ex] 
  \hline
- Maize & 25695 & 8325 & 200 & 34220  \\ 
- Weed & 8560 & 2000 & 200 & 10760\\ 
+ Maize & 7581 & 1895 & 787 & 9476 \\ 
+ Weed & 2023 & 505 & 300 & 2528\\[1ex] 
  \hline 
@@
 \subsection{Convolutional Neuronal Network}
-	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{sharif2014cnn}.
-Their are also applied in Precision Agriculture \cite{potena2016fast} for the correct identification of plants.
+	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}.
+Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants.
 \\
 
-One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{Potena:Nardi}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
 \\
@@
  \hline
- Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
+ Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
  \hline
@@
   Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
- \hline 
+ \hline \\
 \end{tabular}
 \caption{Distribution of the Dataset of each class}
-\label{table:2}
+\label{table:1}
 \end{table}
 
-Inside of the shown parameters in the Table {table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
+Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
 The following picture shows the process of training of the cNET \\
-Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification.
-The following picture shows the process of training of the cNET.
-\\
-
-	\begin{figure*}[htb]
-	\centering
-	\includegraphics[width=6.5 in]{arquitectura}
-	\caption{ The schematic of CNet }
-	\label{fig_sim}
-	\end{figure*}
 
@@
 	\centering
-	\includegraphics[width=2.3in]{entrenamiento}
+	\includegraphics[width=3.2in]{entrenamiento}
 	\caption{ Graph of the Training Process }
@@
 
-Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
-To achive this, it was neccesary to reduce the number of filters from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.
-
 	\section{Test}
-
-For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l|c|c|p{2cm}|}  
- \hline
- \multicolumn{4}{ |c| }{GPU} \\
- \hline
-   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
- \hline 
- 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
- \hline
- 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
-  \hline
- \multicolumn{4}{ |c| }{CPU} \\
- \hline
-   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
- \hline 
- 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
- \hline
- 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
-  \hline
- \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
- \hline
-   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
- \hline 
- 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
- \hline
- 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
-  \hline
-\end{tabular}
-\caption{Test}
-\label{table:2}
-\end{table}
+	%Codigo para la Implementacion del Algoritmo
 
@@
 \section{Conclusion}
-
-In this paper we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 99.33 \% of accuracy of training, using a dataset of both classes  of 44580 segmented images.
-\\
-
-In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuray of the net, it value fell 1 \% in comparation with the original net.
-\\
-
-Also, by using different methods to classify the images in our experiments, the results showed that the best time of classification was achieved by using a Nvidia Graphic Cards, this is due the Parallel Architecture that this GPU has and also it has fully support for the computation platform CUDA, it demostrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3.
-\\
-
-The study demostrated that is better to perform some geometrical tranformations to the Dataset images due it benefits to improve the  classification of plants because the plants ever have different orientations in the crop field.
+The conclusion goes here.
 
@@
 
-The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to obtain to conform the dataset of the project.
-\\
-
-This work has been supported by the University of the Army "ESPE"  Latacunga.
+The authors would like to thank...
 
@@
 % (used to reserve space for the reference number labels box)
+\begin{thebibliography}{1}
 
-\bibliographystyle{IEEEtran}
-\bibliography{bibliografiapaper}
+\bibitem{Suarez:Pinero}
+R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
+  0.5em minus 0.4em\relax Gij\'on , Spain: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.
+
+\bibitem{Brivot:Marchant}
+R.~Brivot and J.~A. Marchant, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
+  \bibitem{Cheng:Mason}
+B.~Cheng and E.T.
+~Matson, \emph{A Feature-Based Machine Learning Agent for Automatic Rice and Weed Discrimination} Artificial Intelligence and Soft Computing: 14th International Conference, ICAISC 2015 Part II \hskip 1em plus
+  0.5em minus 0.4em\relax Zakopane, Poland , 2015.
+
+  \bibitem{Hong:Lei}
+~Hong. Y. Jeon, ~Lei F. Tian  and ~Heping Zhu, \emph{Robust Crop and Weed Segmentation under Uncontrolled Outdoor Ilumination} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2011.
+
+  \bibitem{Araguez}
+D.~Abad\'ia, R.
+Aragu\'es, A.
+~Cirujeda, R.
+~del Hoyo, J.
+~Paniagua, T.
+~Seco, V.
+~Urdanoz, F.
+~Us\'on and C.
+~Zaragoza , \emph{SAAPIN: Un robot para el desherbado de cultivos y valoraci\'on de salinidad del suelo} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 206.
+
+ \bibitem{Su:Hnin}
+R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
+%Revisar la extension de los nombres  
+ \bibitem{Romeo}
+J.~Romeo, G. ~Pajares M. ~Montalvo, J.M. ~Guerrero, M. ~Guijarro, and A. ~Ribeiro, \emph{Crop Row Detection in Maize fields Inspired on the Human VIsual Perception} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2012.
+
+%Poner Bibliografia Correcta, Revisar	 si es neceario poner cuatro nombres
+ \bibitem{Potena:Nardi}
+ C.~Potena,  D.~Nardi and A. ~Pretto \emph{Fast and Accurate Crop and Weed Identification with Summarized Train Sets for Precision Agriculture} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.
+
+%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
+ \bibitem{Cicco:Potena}
+ M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
+
+ \bibitem{Razavian}
+ A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
+
+   \bibitem{OpenCV}
+ A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
+
+     \bibitem{caffe}
+Jia, Yangqing and Shelhamer, Evan and Donahue, Jeff and Karayev, Sergey and Long, Jonathan and Girshick, Ross and Guadarrama, Sergio and Darrell, Trevor, \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.
+
+       \bibitem{SengChang}
+Seng Chang \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.
+
+       \bibitem{Fassio}
+Fassio, A., Carriquiry, A., Tojo, C. and Romero, R  \emph{MAIZ: Aspectos sobre fenolog\'ia}  \hskip 1em plus
+  0.5em minus 0.4em\relax Montevideo, Uruguay:Seria T\'ecnica Nº 101, 1998.
+
+\bibitem{IEEEhowto:kopka}
+H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+\end{thebibliography}
 

### 2017-07-06 PaperBCJ.tex

--- 2017-07-06 PaperBCJ.tex
@@
 \section{Introduction}
-During the last centuries, huge progress has taken place in science and technology developments.
-Significant milestones such as Communications, Numerical Computer Control and the miniaturization of components have benefited social and industrial sectors on its approach to solve specific problems.
+During the last centuries, significant progress has taken place in science and technology developments.
+Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems differently.
 \\
 
-Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive bleeding edge technological products in order to satisfy requirements and propose solutions to still-unresolved problems.
+The availability of leading edge technologies  has considerably increased, thus becoming more accessible to people.
+This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.
+
 \\
 
-Industry transformation is a science evolution example; manufacturing, food, and information industries, among others, are signs of this industrial revolution.
-However there are fields still unexplored  in Ecuador like agroindustry.
-Agriculture in Ecuador has not changed much since precolombine times; while it is true that there are efficient agriculture practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer.
+Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with industrial revolution.
+However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
+Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer.
+Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality.
 \\

### 2017-07-06 PaperBCJ.tex
Modificacion tablas

--- 2017-07-06 PaperBCJ.tex
@@
 
-To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.\\
+It should be noted that we had manually labeled the samples in two classes, maize and grass, having no account that the images are not repeated.
+In the following image we present the final results of the processed images that conform the dataset.\\
 
@@
 \centering
-\begin{tabular}{| c | c | c | c | c |} 
+\begin{tabular}{| c  c  c  c  c |} 
  \hline
- Phase & Train & Validation & Test & Total \\ [1ex] 
+ \textbf{Phase} & \textbf{Train} & \textbf{Validation} &\textbf{Test}  & \textbf{Total} \\ [1ex] 
  \hline
@@
  \hline
- Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
+ \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
  \hline
@@
  \hline
- Parameters & cNET 16 filters & cNET 64 filters \\ [0.75ex] 
+ \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
  \hline
@@
 
+Once the network architecture was chosen, it is constituted as follows: the input, a 64x64 RGB image layer followed by a convolution layer which reduces the image by taking only its main characteristics, then a layer of pooling which finds the maximum values of the characteristics found in the previous layer, followed by a second convolution, and a second layer of pooling, and finally two layers of type fully connected, from which in the end we have the output representing the two classes established in this network.\\
+
 	\begin{figure}[h]
@@
 	\end{figure}
+
+The follow picture shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\
 
@@
 
-The before pictures shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\
-
 	\section{Test}
@@
 \centering
-\begin{tabular}{|l|c|c|p{2cm}|}  
+\begin{tabular}{|p{1.1cm}|p{1.9cm}|p{1.95cm}|p{2cm}|}  
  \hline
- \multicolumn{4}{ |c| }{GPU} \\
+ \multicolumn{4}{ |c| }{\textbf{GPU}} \\
  \hline
-   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
+   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\ 
  \hline 
- 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
+ 64 Filters & 95.05\% & 74.75\% & 2.34 ms  \\ [0.75ex]
  \hline
- 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
+ 16 Filters & 94.55\% & 87.13\% & 951  $\mu$s \\ [0.75ex]
   \hline
- \multicolumn{4}{ |c| }{CPU} \\
+ \multicolumn{4}{ |c| }{\textbf{CPU}} \\
  \hline
-   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
+   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\ 
  \hline 
- 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
+ 64 Filters & 95.05\% & 74.75\% & 51.6 ms  \\ [0.75ex]
  \hline
- 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
+ 16 Filters & 94.55\% & 87.13\% & 17.23 ms \\ [0.75ex]
   \hline
- \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
+ \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
  \hline
-   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
+   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\
  \hline 
- 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
+ 64 Filters & 95.05 \% & 74.75\% & 615 ms  \\ [0.75ex]
  \hline
- 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
+ 16 Filters & 94.55\% & 87.13\% & 161 ms \\ [0.75ex]
   \hline

### 2017-07-07 PaperBCJ.tex
description_arquitectura

@@
 This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.
-
 \\
@@
 
-Once the network architecture was chosen, it is constituted as follows: the input, a 64x64 RGB image layer followed by a convolution layer which reduces the image by taking only its main characteristics, then a layer of pooling which finds the maximum values of the characteristics found in the previous layer, followed by a second convolution, and a second layer of pooling, and finally two layers of type fully connected, from which in the end we have the output representing the two classes established in this network.\\
+The complete network model is formed as follows: the input layer where an RGB image 64x64 pixels, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel, this layer  obtaining only its main characteristics, then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2, then again a second layer of convolution is applied that has 16 filters, 5 kernels and a stride of 1, followed by a new layer of pooling with a kernel size and stride of 2 again obtained a size of 16x16x16 and finally the layers of type fully-connected with a total of 478 neurons, where the last two neurons that is the output represent the two classes established in this network.\\
 
@@
 	\centering
-	\includegraphics[width=3.6 in]{arquitectura}
+	\includegraphics[width=3.5 in]{arquitectura}
 	\caption{ The schematic of CNet }

### 2017-07-13 PaperBCJ.tex
Add Equations
Add Equations

--- 2017-07-06 PaperBCJ.tex
@@
 
-Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed.
+Then, through a digital image processing, as first stage the image was normalized in its green channel, so it improve the detection of green color due it eliminates lights and shadows of the image, afeter we extracted the green color, through the next equation \cite{wang2013path}.
+\begin{equation}
+	S = 2*G - R - B
+\end{equation} 
+After the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed.
 Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format.
@@
 
-It should be noted that we had manually labeled the samples in two classes, maize and grass, having no account that the images are not repeated.
-In the following image we present the final results of the processed images that conform the dataset.\\
+To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.\\
 
@@
 \centering
-\begin{tabular}{| c  c  c  c  c |} 
+\begin{tabular}{| c | c | c | c | c |} 
  \hline
- \textbf{Phase} & \textbf{Train} & \textbf{Validation} &\textbf{Test}  & \textbf{Total} \\ [1ex] 
+ Phase & Train & Validation & Test & Total \\ [1ex] 
  \hline
@@
  \hline
- \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
+ Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
  \hline
@@
  \hline
- \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
+ Parameters & cNET 16 filters & cNET 64 filters \\ [0.75ex] 
  \hline
@@
 
-Once the network architecture was chosen, it is constituted as follows: the input, a 64x64 RGB image layer followed by a convolution layer which reduces the image by taking only its main characteristics, then a layer of pooling which finds the maximum values of the characteristics found in the previous layer, followed by a second convolution, and a second layer of pooling, and finally two layers of type fully connected, from which in the end we have the output representing the two classes established in this network.\\
-
 	\begin{figure}[h]
@@
 	\end{figure}
-
-The follow picture shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\
 
@@
 
+The before pictures shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\
+
 	\section{Test}
@@
 \centering
-\begin{tabular}{|p{1.1cm}|p{1.9cm}|p{1.95cm}|p{2cm}|}  
+\begin{tabular}{|l|c|c|p{2cm}|}  
  \hline
- \multicolumn{4}{ |c| }{\textbf{GPU}} \\
+ \multicolumn{4}{ |c| }{GPU} \\
  \hline
-   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\ 
+   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
  \hline 
- 64 Filters & 95.05\% & 74.75\% & 2.34 ms  \\ [0.75ex]
+ 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
  \hline
- 16 Filters & 94.55\% & 87.13\% & 951  $\mu$s \\ [0.75ex]
+ 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
   \hline
- \multicolumn{4}{ |c| }{\textbf{CPU}} \\
+ \multicolumn{4}{ |c| }{CPU} \\
  \hline
-   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\ 
+   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
  \hline 
- 64 Filters & 95.05\% & 74.75\% & 51.6 ms  \\ [0.75ex]
+ 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
  \hline
- 16 Filters & 94.55\% & 87.13\% & 17.23 ms \\ [0.75ex]
+ 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
   \hline
- \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
+ \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
  \hline
-   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\
+   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
  \hline 
- 64 Filters & 95.05 \% & 74.75\% & 615 ms  \\ [0.75ex]
+ 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
  \hline
- 16 Filters & 94.55\% & 87.13\% & 161 ms \\ [0.75ex]
+ 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
   \hline

### 2017-07-13 PaperBCJ.tex
Fixes of Green Channel
Fix redaction and picture of green Channel

--- 2017-07-07 PaperBCJ.tex
@@
 
-Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed.
+Then, through a digital image processing, as first stage the image was normalized in its green channel, it improves the detection of green color due it eliminates lights and shadows of the image, after we extracted the green color to obtain a grayscale image, through the next equation described by Wang, Meng, Luo and Mei \cite{wang2013path}, then we applied a OTSU Thresholding to grayscale image in order to obtain a binary mask.
+\begin{equation}
+	S = 2*G - R - B
+\end{equation} 
+After the images were segmented to differentiate them from the soil and other non-plant elements, the original images were masked to provide the dataset features of color of the Maize and Weed.
 Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format.

### 2017-07-17 PaperBCJ.tex
Add transcriptions in Spanish

@@
 \section{Matherials and Methods}
-The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
+
+El desarrollo del modelo para la identificacion de mala hierba y maiz usando Redes Neuronales Convoluciones se describe abajo: 
+\\
+
+The development of the model for the weed and maize identification algorithm using convolutional neural networks is described below.
 \\
 \subsection{Hardware}
+
+Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes.
+Debido a la popularidad de la computacion por GPU, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de procesamiento y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M.
+Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar los tiemposde clasificacion de imagenes en las arquitecturas de red.
+\\
+
 For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image acquisition, it was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
@@
 
+Para la aplicacion en este documento, se requiere el uso de Poderosas librerias de desarrollo para el procesamiento de imagenes y deep Learning, consideramos el uso de software libre para extender su uso en futuros prototipos, debido a esta consideracion hemos escogido la libreria de OpenCV debido a su eficiencia computacional y su enfoque a aplicaciones en tiempo real, para este caso fue utilizada(en referencia a OpenCV) para la adquisicion y segmentacion de las imagenes de muestra.
+Tambien hemos considerado Caffe debido a que esta desstinado a el entrenamiento y desarrollo de Redes Neuronales Convolucionales de Proposito General y otros modelos de Deep Learning con soporte completo de la Libreria de Computacion GPU CUDA y una generosa base de datos de recursos para aprendizaje  \\
+
 For the application in this documents it requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{opencv_library} in this  case, it was used for acquisition and segmentation of the sample images.
-Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{jia2014caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,
+Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{jia2014caffe} with fully support of CUDA GPU Computation Library and a generous database of resources for learning,
 \\
 
+Tambien el la etapa de desarrollo fue importante el suo del Sistema Operativo Linux, sus caracteristicas son: Sistema Operativo Ligero y Libre tambien completamente compatible con el software mencionado anteriormente.
+En la computadora principal fue usado la Distribucion Ubuntu Linux 16.04 por su soporte oficial a CUDA, Caffe y OpenCV, tambien en la Raspberry Pi fue usado el Sistema Operativo Pixel para adquirir imagenes y probar el rendimiento de clasificacion la Red Neuronal Convolucional \\
+
 Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above.
-For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi we used the Pixel OS for acquire images and processing of the CNN.
+For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi we used the Pixel OS for acquire images and test the classification performace of the CNN.
 \\
@@
 \subsection{Dataset Description}
-Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
+
+Debido a la falta de datasets de plantas de Maize y Mala Hierba, fue necesario la busqueda de cultivos de maiz en su etapa inicial, para ese proposito nos hemos traslatado a Pillaro, esta ciudad es localizada en la Provincia de Tungurahua, en el Centro de la Sierra Ecuatoriana.
+Pillaro es un productor reconocido de  cultivos andinos como: Maiz, Papas y frutas, por lo que podemos encontrar aqui muchos cultivos de maiz que sean utiles para nuestro proposito \\
+
+Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province, on the center of the Ecuadorian Highlands region P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
 \\
+
+Las muestras fueron obtenidas de imagenes capturas en esos campos de maiz, consideramos escoger cultivos de maiz donde podamos visualmente discrimiar las plantas del cultivo de la mala yerba.
+Las etapas del Maiz (V3-V7) fueron usadas para tomar muestras.
+Para obtener las muestra, centramos la camara sobre la platna objetivo, asegurandonos que la captura muestre todas las caracteristicas de la planta de maiz, esto fue posible al monitorear el proceso por una pantalla externa.
+Unas muestras de las imagenes capturadas son mostradas a continuacion: \\
 
@@
 
+Tambien fue necesario obtener imagenes de las malas hierbas mas comunes en los campos de maiz de Pillaro, para permitir a la Red discrimiar entre las dos clases definidas en el Dataset.\\
+
 Also it was neccesary to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the Network to discriminate both classes of the Dataset. \\
+
+Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria \\
 
@@
 \end{equation}
-After the images were segmented to differentiate them from the soil and other non-plant elements, the original images were masked to provide the dataset features of color of the Maize and Weed.
-Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format.
+
+Despues de la imagen fue segmentada, para diferenciarla del suelo y otros elementos que no sean plantas, las imagenes originales fueron enmascaradas con la mascara binaria para proveer al Dataset caracteristicas de Color del Maiz y de la Mala Hierba.
+Una vez ue las imagenes segmentedas fueron obtenidas, removimos aquellas que tenian una resolucion menor a 64x64 pixeles debido a que son mas pequenhas que el tamanho de entrada de la red, ademas no es conveniente procesarlas debido a que su area total es mucho mas pequenha que la de las muestras de maiz, las cuales son el proposito de este documento, despues las imagenes se almacenan en un formato Png.
+El proceso se ilustra de mejor manera en la siguiente figura.
+\\
+
+After the images were segmented to differentiate them from the soil and other non-plant elements, the original images were masked with the binary mask to provide the dataset features of color of the Maize and Weed.
+Once the segmented images were obtained, we were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format.
 The process described before, was illustrated in the next figure.
 \\
+
 	\begin{figure}[h]
@@
 
-It should be noted that we had manually labeled the samples in two classes, maize and grass, having no account that the images are not repeated.
+Debemos acotar que hemos etiquetado manualmente las imagenes en dos clases, maiz y mala hierba, teniendo en cuenta que las imagenes no se repitan(\textbf{corregir}).
+En la presente imagen presentamos los resultados finales de las imagenes procesadas que conforman el dataset.
+\\
+
+It should be noted that we had manually labeled the samples in two classes, maize and weed, having no account that the images are not repeated.
 In the following image we present the final results of the processed images that conform the dataset.\\
@@
 
+Una vez completada el procesamiento de imagenes, donde fueron obtenidas 2835 imagenes de maiz y 880 images de Mala Hierba, Lee et.
+Al dicen que una vez que la CNN ha alcanzado una precision aceptable, el dataset se puede extender por transformaciones geometricas, en adicion sladojevic mencionan que esto permite a reducir el sobreajuste y para mejorar la precision en el entrenamiento, razon por la cual hizimos 11 rotaciones cada 30 grados, obteniendo de esta forma el incremento(corregir) del dataset en 12 veces y tener mejores probabilidades de reconocer als plantas en cualquier orientaciones.
+\\
+
 Once we completed the processing of the images, it were obtained 2835 images of Maize and 880 images of Weed, Lee \textit{et.
@@
 \\
+
+Para la fase de validacion, hemos escogido aletariamente la quinta parte del total de imagenes de cada clase, asi que tenemos la siguiente tabla con la distribucion del dataset.\\
 

### 2017-07-18 PaperBCJ.tex
Some Translations
Translations

@@
 \subsection{Convolutional Neuronal Network}
+
+Despues que el ultimo paso ha sido terminado, fue necesario clasificar las imagenes del Maiz y Mala Hierba, un metodo muy preciso de Clasificacion de Imagenes son las Redes Neuronales Convolucionales(CNN), estos modelos son complejos pero eficientes  con un alto grado de discriminacion y han demostrado que tienen unos buenos resultados en la Clasificacion de Imagenes, Deteccion de Objetos y Fine*Grained Classification.
+Tambien son aplicados en la Agricultura de Precision para la correcta identificacion de plantas\\
+
 	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{sharif2014cnn}.
-Their are also applied in Precision Agriculture \cite{potena2016fast} for the correct identification of plants.
-\\
+Their are also applied in Precision Agriculture \cite{potena2016fast} for the correct identification of plants.\\
+
+Una de las caracteristicas de las CNN is que estas pueden tener multiples arquitecturas, cada arquitectura puede alcanzar diferentes resultados dependiendo de la aplicacion, para el presente documento hemos considerado cuatro arquitecturas de CNN: Dos modelos fueron escogidos del Caffe Zoo Model(es un recurso libre liberado por los Desarrolladores de Caffe) Lenet y AlexNet, tambien Potena y Nardi han usado adicionalmente dos tios de modelos, sNET y cNET, estos han sido exitosamente probados en la clasificacion de plantas en cultivos, con las redes secogidas, cada una fue entrenada con un mismo Solver de Tipo AdaDelta, con el mismo Dataset y los resultados del entrenamiento son los siguientes: \\
 
@@
 \end{table}
+
+Dentro de los parametros mostrados en la Tabla, consideramos la red que alcanze la mas alta tasa de precision y mas baja tasa de perdida, claramente la cNET es la escogida, debido a que esta presenta una precision cercana a la clasificacion humana\\
 

### 2017-07-18 PaperBCJ.tex
Traduccion
Traduccion de partes faltantes

@@
 \begin{abstract}
+Deep Learning ha tenido un papel muy importante en los tiempos modernos, siendo muy utilizado en vision artificial y especialmente en reconocimiento de patrones, lo cual abre muchas puertas en los campos de aplicacion siendo uno de ellos la agricultura de presicion.En este paper presentamos el estudio una red neuronal convolucional aplicada a la  clasificacion de plantas de maiz y de mala hierba en tiempo real, dirigida a campos de maiz en su etapa inicial.El algoritmo cuenta con dos etapas, segmentacion de imagenes y la clasificacion.
+En la  segmentacion se busca separar de la imagen las plantas de forma individual.
+Mientras que la clasificacion se da a traves de la red neuronal convolucional, previamente entrenada con un dataset generado mediante la etapa de segmentacion.
+El rendimiento de la red se ilustra mediante analisis y comparaciones con diferentes arquitecturas de red, luego con la red que presento mejores resultados, se experimeto modificando su numero de filtros, para analizar su comportamiento.
+Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion.\\
+
 Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture.
@@
 
-Tambien el la etapa de desarrollo fue importante el suo del Sistema Operativo Linux, sus caracteristicas son: Sistema Operativo Ligero y Libre tambien completamente compatible con el software mencionado anteriormente.
+Tambien el la etapa de desarrollo fue importante el uso del Sistema Operativo Linux, sus caracteristicas son: Sistema Operativo Ligero y Libre tambien completamente compatible con el software mencionado anteriormente.
 En la computadora principal fue usado la Distribucion Ubuntu Linux 16.04 por su soporte oficial a CUDA, Caffe y OpenCV, tambien en la Raspberry Pi fue usado el Sistema Operativo Pixel para adquirir imagenes y probar el rendimiento de clasificacion la Red Neuronal Convolucional \\
@@
 Una vez completada el procesamiento de imagenes, donde fueron obtenidas 2835 imagenes de maiz y 880 images de Mala Hierba, Lee et.
-Al dicen que una vez que la CNN ha alcanzado una precision aceptable, el dataset se puede extender por transformaciones geometricas, en adicion sladojevic mencionan que esto permite a reducir el sobreajuste y para mejorar la precision en el entrenamiento, razon por la cual hizimos 11 rotaciones cada 30 grados, obteniendo de esta forma el incremento(corregir) del dataset en 12 veces y tener mejores probabilidades de reconocer als plantas en cualquier orientaciones.
+Al dicen que una vez que la CNN ha alcanzado una precision aceptable, el dataset se puede extender por transformaciones geometricas, en adicion sladojevic mencionan que esto permite a reducir el sobreajuste y para mejorar la precision en el entrenamiento, razon por la cual se realizaron 11 rotaciones cada 30 grados, obteniendo de esta forma el incremento(corregir) del dataset en 12 veces y tener mejores probabilidades de reconocer als plantas en cualquier orientaciones.
 \\
@@
 Once we completed the processing of the images, it were obtained 2835 images of Maize and 880 images of Weed, Lee \textit{et.
-al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{sladojevic2016deep}  they mention that this allows to reduce the overfitting and to improve the precision in the training, reason why we made 11 rotations each 30 degrees, obtaining in this way to increase the dataset in 12 times and have better chances of recognizing plants that are in any orientation.
+al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{sladojevic2016deep}  they mention that this allows to reduce the overfitting and to improve the precision in the training, reason for which 11 rotations were performed each 30 degrees, obtaining in this way to increase the dataset in 12 times and have better chances of recognizing plants that are in any orientation.
 \\
@@
 
-One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document was considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same solver of type AdaDelta and with the same dataset, the results of training are the following.
 \\
@@
 
+Aunque  los resultados de la red son excelentes,una de las propuestas de este trabajo es la implementacion en tiempo real,por lo que el numero de parametros a ser procesados sera importante, por lo que se conisdero modificar la red para mejorar el tiempo de procesamiento, para lograr esto fue encesario reducir el n\'umero de filtros de la cNET de 64 hasta 16.\\
+
 Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
@@
 
-This permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy.\\
+Esto permitió reducir el número de parámetros a 1651376 (es un 25 \% de parámetros que la red original),donde la precisión de la red, fue ligeramente afectada pero alcanza un 97.2 \% de exactitud.\\
 
+This permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), where the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy.\\
+
+El modelo completo de la red queda formado de la siguiente manera: la capa de entrada donde ingresa una imagen RGB 64x64 pixeles, seguida por una capa de convolucion de 5 kernels y un stride de 1 píxel, capa que reduce la imagen a un de tamaño de 16x32x32 obteniendo solamente sus características principales, luego se aplica una capa de pooling, que tiene la funcion de encontrar los valores máximos de la capa anterior mediante 16 filtros, dejando un tamaño de 32x32x48, entonces nuevamente se aplica una segunda capa de convolucion que tiene 5 kernels y un stride de 1, logrando un tamaño de 32x32x16 seguida por una nueva  capa de pooling con 16 filtros de tamaño 32x16x16 y finalmente las capas de tipo fully-connected con un total de 478 neuronas, donde las dos ultimas neuronas que estana la salida representan las dos clases establecidas en esta red.\\
 The complete network model is formed as follows: the input layer where an RGB image 64x64 pixels, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel, this layer  obtaining only its main characteristics, then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2, then again a second layer of convolution is applied that has 16 filters, 5 kernels and a stride of 1, followed by a new layer of pooling with a kernel size and stride of 2 again obtained a size of 16x16x16 and finally the layers of type fully-connected with a total of 478 neurons, where the last two neurons that is the output represent the two classes established in this network.\\
@@
 	\section{Test}
+Para esta etapa se consideró un conjunto de datos adicional con 200 imágenes de plantas de maíz en estadio de V3-V7 y 203 imágenes de malezas, obtenidas en cultivos de maíz, los resultados fueron comparados entre cNET con 64 y 16 filtros en la Tabla\\
 
@@
 \end{table}
+
+Como se muestra en la tabla, los resultados alcanzados por el procesador GPU, es la mejor opci\'on para clasificar una gran cantidad de imágenes sin embargo este proyecto se piensa que es port\'atil, por lo que consideramos el RaspBerry Pi para el an\'alisis de rendimiento.
+Con cNET de 64 filtros los resultados para el tiempo de clasificaci\'on fue de 615 milisegundos, por lo que el tiempo no es el \'optimo para nuestro objetivo que es el procesamiento en tiempo real.\\
 
@@
 \section{Conclusion}
+Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 99\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases.
+\\
 
@@
 
-In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuray of the net, it value fell 1 \% in comparation with the original net.
+Para buscar un procesamiento apropiado para trabajar en tiempo real, se experimento reduciendo el numero de filros de las capas de la red desde 64 hasta 16, logrando con esto disminuir el numero de parametros a ser computados durante la clasificacion, obteniendo tambien un tiempo de procesamiento de 2,5 veces menor al de la red original, este cambio tuvo un bajo impacto en la precision de entrenamiento de la red, pues este valor cayo en un 1\%, con respecto a la red original.
+
+In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obtained a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuray of the net, it value fell 1 \% in comparation with the original net.
 \\
+
+Ademas  nuestros experimentos al utilizar diferentes procesadores, demostraron que se obtienen mejores resultados en cuanto a velocidad al trabajar con una  a tarjeta grafica ENVIDIA que posee soporte CUDA debido a su arquitectura de computacion paralela, siendo este 10 veces mas rapido que el CPU normal y 100 veces mas rapido que una RaspBerry Pi3.\\
 
@@
 \\
+
+El estudio demostro que es mejor obtener las imagenes para el dataset realizar algunos giros en las imagenes de las plantas del dataset, debido a que esto aporta mejoras en la identificacion de plantas, pues estas siempre tienen orientaciones diferentes.\\
 
@@
 \section*{Acknowledgment}
+
+Damos gracias a la Graja Agroecologica y Demostrativa de Pillaro y a dueños de cultivos de maiz de lugares aledaños.
+que nos permitieron tomar muestras de plantas ,para la obtencion del dataset del proyecto.
+Este trabajo ha sido apoyada por la Universidad de las Fuerzas Armadas ESPE Extension Latacunga.
 

### 2017-07-18 PaperBCJ.tex
Traduction of test
test

--- 2017-07-18 PaperBCJ.tex
@@
 \end{tabular}
-\caption{Distribution of the Dataset of each class}
+\caption{Comparison of the 4 types of CNN}
 \label{table:2}
@@
 Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission near to human classification.\\
+
+Aunque lo resultados dados de la red fueron excelentes, uno de los propositos principales de este documento es una aproximacion de procesamiento en tiempo real, entonces el numero de parametros a ser computados va a ser un problema, entonces consideramos modificar la red para mejorar el tiempo de procesamiento.
+Para lograr esto, fue necesario reducir el numero de filtros de cNET de 64 a 16, en la tabla siguiente se muestran los resultados del entrenamiento para los dos tipos de red.
+\\
 
@@
 \end{tabular}
-\caption{Distribution of the Dataset of each class}
+\caption{Comparison between cNET of 16 and 64 filters}
 \label{table:3}
@@
 
-This permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy.\\
+Esta reduccion permitio reducir el numero de parametros de 1651376(es un 25\% de parametros de la red original), y acerca de la precision d ela red, fue affectada un poco pero asi consigue un 97.2\% de precision en el entrenamiento.
+\\
 
-The complete network model is formed as follows: the input layer where an RGB image 64x64 pixels, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel, this layer  obtaining only its main characteristics, then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2, then again a second layer of convolution is applied that has 16 filters, 5 kernels and a stride of 1, followed by a new layer of pooling with a kernel size and stride of 2 again obtained a size of 16x16x16 and finally the layers of type fully-connected with a total of 478 neurons, where the last two neurons that is the output represent the two classes established in this network.\\
+This reduction permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy.\\
+
+Entonces el modelo completo de red se forma de la siguiente manera: La capa de entrada que recibe una imagen RGB de 64x64 pixeles, seguida por una capa de convolucion de 16 filtros, un kernel de 5 y stride de 1 pixel, esta capa obtiene solo las principales caracteristicas de la imagen, despues una capa de pooling es aplicada, la cual tiene la funcion de encontrar los maximos valores de las capas, con un tamanho de kernel y stride de 2, despues nuevamente se aplica una segunda capa de convolucion que tiene 16 filtros, ancho de kernel de 5 y un stride de 1, seguido nuevamente de una nueva  capa de pooling con un tamanho de kernel y de stride de 2, obteniendo asi una imagen de salida de de tamanho 16x16x16 y finalmente se completa la red con tres capas consecutivas fully-connected, la primera con 384 neuronas, la segunda con 192 y la ultima con dos neuronas que representara la capa las dos clases que se busca  clasificar, el modelo resultante se muestra en la siguiente imagen \\
+
+So, the complete network model is formed as follows: the input layer where an RGB image 64x64 pixels, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel, this layer  obtaining only the main characteristics of the image, then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2, then again a second layer of convolution is applied that has 16 filters, size of kernel 5 and a stride of 1, followed by a new layer of pooling with a kernel size and stride of 2, so the result image was has size of 16x16x16 and finally the net is completed with three fully-connected layers, the first with 384 neurons, the next with 192 and the last with 2 neurons which represent the both classes  the layers of type fully-connected with a total of 478 neurons, where the last two neurons that is the output represent the two classes to classify, the result model is shown in the next graph.\\
 
@@
 	\includegraphics[width=3.5 in]{arquitectura}
-	\caption{ The schematic of CNet }
+	\caption{ The schematic of cNET }
 	\label{fig_sim}
@@
 
-The follow picture shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\
+En la grafica de entrenamiento que se muestra a continuacion podemos apreciar el resultado final de precision de la red, la 9000 iteraciones fueron necesarias para reducir el la capa de Loss al minimo y la arquitectura demostro alcanzar rapidamente un valor aceptable de precision, notose que reduciendo el numero de filtros la red gano en precision porque las imagenes del dataset no tienen demasiadas caracteristicas para procesar, por lo que la red fue mejor solucionable con un numero menor parametros de red\\
+
+In the graph of training shown below, we can appreciate the final result of the net accuracy, 9000 iterations were neccesary to reduce the Loss value to its minimun and the architecture shows that it can reach an acceptable accuracy with few iterations.
+Note that by reducing the number of filters the network gained accuracy because the dataset does not have so much features learn, so the net found a better solution with a less number of parameters.
+\\
 
@@
 
-For this stage, we considered an extra dataset with 200 images of maize plants in stage of V3-V7 and 203 images of weed, obtained in maize crops, the results were comparated between cNET with 64 and 16 filters in the Table \ref{table:4}.\\
+Para esta etapa, consideramos otro dataset con 202 imagenes de plantas de maiz en la etapa V3-V7 y 202 dos imagenes de mala hierba obtenidas en campos de maiz diferentes a los que pertenecen al dataset de entrenamiento, para esta prueba se ha medido los tiempos de clasificacion promedio de diez clasificaciones de este dataset en los distintos hardwares que poseemos, empezamos con la clasificacion en Caffe sin modificaciones de software.
+Los resultados fueron comparados entre la red cNET de 64 y 16 filtros y se muestran en la siguiente Tabla\\
+
+For this stage, we considered another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weed, obtained in different maize crops that the training dataset.
+For this test we have measured the average time of ten classifications of each image of this dataset with the hardware that we own, we started the classification in Caffe without modifications in Software.
+The results were comparated between cNET with 64 and 16 filters and there are shown in the next Table \ref{table:4}.\\
+
 \begin{table}[h!]
@@
  \hline
-   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\ 
+   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}   \\ 
  \hline 
@@
  \hline
-   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\
+   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}   \\
  \hline 
@@
 
-Like the table shown the results were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so we consider the RaspBerry Pi for the analysis of performance.
-With cNET of 64 filters the results fo time of classification was 615 miliseconds, so it time isn\'t the optimum for our objective that it is the processing in a real time.\\
+Como la tabla muestra, los mejores resultados en tiempos de clasificacion fueron alcanzados por el procesador por GPU, esta es la mejor opcion para clasificar una gran cantidad de imagenes, sin embargo este proyecto esta psenado para ser portable, por lo que consideramos al Raspberry Pi para el analisis del rendimiento de classificacion.
+Con la cNET de 64 filtros, los ersultos de tiempo de clasificacion fueron de 615 milisegundos, pero este tiempo no es optimo para nuestro objetivo que es la aproximacion de clasificacion en tiempo real.
+\\
+
+Like the table shown the best results in times of classification were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so we consider the RaspBerry Pi for the analysis of classification performance.
+With cNET of 64 filters the results of time of classification was 615 miliseconds, so it time isn\'t the optimum for our objective that it is the approximation to classification in a real time.\\
+
+Los resultados presentados anteriormente no son definitivos, pues Caffe presenta algunas formas de optimizar la clasificacion de datasets de imagenes, para este documento se ha utilizado el Agrupamiento de Imagenes en una sola estructura(Batch) para clasificar el dataset de cada clase en un  single forward pass y la utilizacion de Multithreading a traves del software matematico OpenBLAS.
+Para cada hardware se volvio a compilar Caffe con OpenBLAS en lugar de Atlas y en el programa se ingresaron todas las imagenes en un vector para ser clasificado un solo grupo de imagenes por cada clase, ademas se  configuro a OpenBLAS para que use 4 Nucleos del cada hardware para obtener resultados parejos, los resultados obtenidos son los siguientes.
+\\
+
+The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document we used Batching to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS Math Software.
+For each hardware, we recompiled Caffe with OpenBLAS instead of Atlas, in the program we entered all images in a vector to be classified in an only batch per each class, also we configure OpenBLAS to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\
+
+\begin{table}[h!]
+\centering
+\begin{tabular}[c c c c]{|p{2.2 cm}|p{1.1cm}|p{1.1cm}|p{2.4cm}|}  
+ \hline
+   \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} &  \textbf{Average time of classification/image}\\ 
+ \hline 
+ GPU & 89.11\% & 92.08\% & 1.58 ms  \\ [0.95ex]
+ \hline
+ CPU & 89.11\% & 87.13\% & 10.92  ms \\ [0.95ex]
+  \hline
+   CPU(Raspberry Pi) & 89.11\% & 87.13\% & 150.8 ms \\ [0.95ex]
+  \hline
+\end{tabular}
+\caption{Test of cNET 16 filters with optimized software}
+\label{table:5}
+\end{table}
+
+Los resultados muestran que para el tiempo de Clasificacion por GPU ha empeorado un 66\%, principalmente debido a que la Libreria de OpenBLAS hace extenso uso de los hilos del CPU, con lo que no todos los parametros seran computados por GPU como en al anterior prueba.
+\\
 
@@
 
-The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to obtain to conform the dataset of the project.
+The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to conform the dataset of this project.
 \\

### 2017-07-18 PaperBCJ.tex
Fix Mauricio's Change

@@
 \begin{abstract}
+
+-Deep Learning ha tenido un papel muy importante en los tiempos modernos, siendo muy utilizado en vision artificial y especialmente en reconocimiento de patrones, lo cual abre muchas puertas en los campos de aplicacion siendo uno de ellos la agricultura de presicion.En este paper presentamos el estudio una red neuronal convolucional aplicada a la  clasificacion de plantas de maiz y de mala hierba en tiempo real, dirigida a campos de maiz en su etapa inicial.El algoritmo cuenta con dos etapas, segmentacion de imagenes y la clasificacion.
+En la  segmentacion se busca separar de la imagen las plantas de forma individual.
+Mientras que la clasificacion se da a traves de la red neuronal convolucional, previamente entrenada con un dataset generado mediante la etapa de segmentacion.
+El rendimiento de la red se ilustra mediante analisis y comparaciones con diferentes arquitecturas de red, luego con la red que presento mejores resultados, se experimeto modificando su numero de filtros, para analizar su comportamiento.
+Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion.\\
+
 Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture.
@@
 
+-Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 99\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases.
+\\
+
 In this paper we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 99.33 \% of accuracy of training, using a dataset of both classes  of 44580 segmented images.
 \\
+
+Para buscar un procesamiento apropiado para trabajar en tiempo real, se experimento reduciendo el numero de filros de las capas de la red desde 64 hasta 16, logrando con esto disminuir el numero de parametros a ser computados durante la clasificacion, obteniendo tambien un tiempo de procesamiento de 2,5 veces menor al de la red original, este cambio tuvo un bajo impacto en la precision de entrenamiento de la red, pues este valor cayo en un 1\%, con respecto a la red original.\\
 
@@
 
+-Ademas  nuestros experimentos al utilizar diferentes procesadores, demostraron que se obtienen mejores resultados en cuanto a velocidad al trabajar con una  a tarjeta grafica ENVIDIA que posee soporte CUDA debido a su arquitectura de computacion paralela, siendo este 10 veces mas rapido que el CPU normal y 100 veces mas rapido que una RaspBerry Pi3.\\
+
 Also, by using different methods to classify the images in our experiments, the results showed that the best time of classification was achieved by using a Nvidia Graphic Cards, this is due the Parallel Architecture that this GPU has and also it has fully support for the computation platform CUDA, it demostrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3.
 \\
+
+-El estudio demostro que es mejor obtener las imagenes para el dataset realizar algunos giros en las imagenes de las plantas del dataset, debido a que esto aporta mejoras en la identificacion de plantas, pues estas siempre tienen orientaciones diferentes.\\
+-
 
@@
 \section*{Acknowledgment}
+
+-Damos gracias a la Graja Agroecologica y Demostrativa de Pillaro y a dueños de cultivos de maiz de lugares aledaños.
+que nos permitieron tomar muestras de plantas ,para la obtencion del dataset del proyecto.
++The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to conform the dataset of this project.
+\\
+-Este trabajo ha sido apoyada por la Universidad de las Fuerzas Armadas ESPE Extension Latacunga. \\
 

### 2017-07-20 PaperBCJ.tex

@@
 During the last centuries, significant progress has taken place in science and technology developments.
-Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems differently.
+Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems in a different manner.
 \\
@@
 
-Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation.
+Nowadays, one of agriculture's challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation.
 There are studies that show the impact of Weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha.
@@
 
-The development of the model for the weed and maize identification algorithm using convolutional neural networks is described below.
+The model development for weed and maize identification algorithm using convolutional neural networks is described below.
 \\
@@
 Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes.
-Debido a la popularidad de la computacion por GPU, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de procesamiento y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M.
+Debido a la popularidad de la computacion por GPU(COMPLETAR IDEA), fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de procesamiento y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M.
 Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar los tiemposde clasificacion de imagenes en las arquitecturas de red.
@@
 
-For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image acquisition, it was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
-Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
-Also it was neccesary to consider the use of a CPU Core i7 2.7 Ghz, 8 cores and the CPU of the Raspberry Pi 3, a ARM Cortex-A53, 1.2GHz, 4 cores for testing the classification of images of the Network.
+For the training and image-capturing stages, the following elements were used: a Raspberry Pi 3 with a V2.1 Pi camera for image acquisition.
+The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
+Due to the popularity of GPU computing(COMPLETAR IDEA), it was necessary to consider hardware compatible with parallel computing such as the Graphic Cards manufactured by NVIDIA.
+These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M.
+Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, an ARM Cortex-A53, 1.2GHz, 4 cores (CLARIFICAR IDEA) for testing  classification speed of network images.
 \\
@@
 
-For the application in this documents it requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{opencv_library} in this  case, it was used for acquisition and segmentation of the sample images.
-Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{jia2014caffe} with fully support of CUDA GPU Computation Library and a generous database of resources for learning,
+The use of powerful libraries of Image Processing and Deep Learning Development was required due to....
+.
+The use of open software was required in order to provide the system with a certain level of flexibility to extend its use for future prototypes.
+Thus,  OpenCV library was chosen due to its computational efficiency and focus on real-time applications \cite{opencv_library}; it was used specificaly for sample images acquisition and segmentation.
+Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other Deep Lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for MACHINE(?) learning.
 \\
@@
 
-Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province, on the center of the Ecuadorian Highlands region P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose.
+Due to the lack of weed and maize plant datasets, it was necessary to search maize crops in its initial development stage for...(COMPLETAR IDEA).
+Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples.
+P\'illaro it is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits.
+Due to its year-long production season, many maize crops at its initial development stage were found in this area.
 \\
@@
 
-Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed.
-Maize in stages V3-V7(3-7 leafs) \cite{fassio1998maiz} were used to take samples.
-To record the samples we centered the camera over the target plant, insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display.
-An examples of the images captured are shown below.
+Samples were obtained from images captured in different maize fields.
+Crops were weed and maize plants could be visually discriminated were chosen in order to (SUSTENTAR IDEA).
+Maize at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
+To record the samples, a camera was centered over the target plant, insuring that the capture shows all features of the maize plant.
+This was achieved by monitoring the obtained samples through an external display.
+Examples of the images captured are shown below.
 
@@
 
-Also it was neccesary to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the Network to discriminate both classes of the Dataset. \\
+Also, it was necessary to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the network to discriminate between the two defined classes of the dataset. \\
 
@@
 
-Then, through a digital image processing, as first stage the image was normalized in its green channel, it improves the detection of green color due it eliminates lights and shadows of the image, after we extracted the green color to obtain a grayscale image, through the next equation described by Wang, Meng, Luo and Mei \cite{wang2013path}, then we applied a OTSU Thresholding to grayscale image in order to obtain a binary mask.
+Then, through a first-stage digital image processing procedure, the images were normalized in its green channel.
+This was done in order to improve green color detection based on the elimination of light and shadow in the images.
+Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through the following equation described by Wang, Meng, Luo and Mei \cite{wang2013path}.
+Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask.
 \begin{equation}
@@
 
-After the images were segmented to differentiate them from the soil and other non-plant elements, the original images were masked with the binary mask to provide the dataset features of color of the Maize and Weed.
-Once the segmented images were obtained, we were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format.
-The process described before, was illustrated in the next figure.
+Afterwards, the images were segmented in order to differentiate them from the soil and other non-plant elements.
+Original images were masked with the binary mask to provide the dataset with color features of maize and weed plants.
+Once the segmented images were obtained, images that had a resolution lower than 64x64 pixels were removed because its size was smaller than the size of the network input layer.
+Besides, the processing of these small images was not convenient since its total area was much smaller than the maize sample images.
+Following, the images were saved in a png format.
+The entire process described before is illustrated in the next figure.
 \\
@@
 
-It should be noted that we had manually labeled the samples in two classes, maize and weed, having no account that the images are not repeated.
-In the following image we present the final results of the processed images that conform the dataset.\\
+It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated.
+In the following image, final results of the processed images that conform the dataset are shown.\\
 
@@
 
-Once we completed the processing of the images, it were obtained 2835 images of Maize and 880 images of Weed, Lee \textit{et.
-al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{sladojevic2016deep}  they mention that this allows to reduce the overfitting and to improve the precision in the training, reason why we made 11 rotations each 30 degrees, obtaining in this way to increase the dataset in 12 times and have better chances of recognizing plants that are in any orientation.
+Once image processing was completed, a set of 2835 maize images and 880 weed images was obtained.
+Lee \textit{et.
+al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations.
+In addition, \cite{sladojevic2016deep} mention that geometric transformations(?) allow overfitting reduction  and improves the precision in the training process.
+For this reason, image rotations each 30 degrees were made, obtaining an increment of the dataset by 12 times, thus increasing the chances of recognizing plants that are in any orientation effectively.
 \\
@@
 
-For the Validation Phase, we had chosen randomly a fifth part of the total images of each class, so we have the following chart with the distribution of the dataset.
+For the Validation Phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the distribution of the dataset.
 
@@
 
-	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{sharif2014cnn}.
-Their are also applied in Precision Agriculture \cite{potena2016fast} for the correct identification of plants.\\
+	After the dataset was completed, it was neccesary to classify maize and weed images.
+Convolutional Neural Networks (CNN) can be used as a highly-accurate method for image classification, these models are complex but efficient with a high rate of discrimination and have proven to provide good results in image classification, object detection, and fine-grained  classification \cite{sharif2014cnn}.
+CNN are widely used in precision agriculture \cite{potena2016fast} for the correct identification of plants.\\
 
@@
 
-One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+One of the characteristics of the CNN is that these can have multiple architectures, each architecture can reach different results depending on the application.
+For the present document we have considered four CNN architectures: two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
 \\
@@
 
-Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission near to human classification.\\
+Within parameters shown on table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was considered; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\
 
@@
 
-Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time.
-To achive this, it was neccesary to reduce the number of filters of cNET from 64 to 16.\\
+Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of this system in real time.
+The number of parameters to be computed by the selected network were numerous, so network modifications in order to improve processing time had to be made.
+To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16.\\
 
@@
 
-This reduction permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy.\\
+This filter reduction permitted to decrease the number of parameters to 1651376 (this represents only 25\% of the original network parameters) without compromising the network precision in a significant way; it still reached a 97.2\% of accuracy.\\
 
@@
 
-So, the complete network model is formed as follows: the input layer where an RGB image 64x64 pixels, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel, this layer  obtaining only the main characteristics of the image, then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2, then again a second layer of convolution is applied that has 16 filters, size of kernel 5 and a stride of 1, followed by a new layer of pooling with a kernel size and stride of 2, so the result image was has size of 16x16x16 and finally the net is completed with three fully-connected layers, the first with 384 neurons, the next with 192 and the last with 2 neurons which represent the both classes  the layers of type fully-connected with a total of 478 neurons, where the last two neurons that is the output represent the two classes to classify, the result model is shown in the next graph.\\
+So, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2 (QUE?), then again a second layer of convolution that has 16 filters is applied, size of kernel 5 and a stride of 1 (QUE), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image was has size of 16x16x16.
+Finally the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons.
+The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify, the result model is shown in the next graph.\\
 
@@
 
-In the graph of training shown below, we can appreciate the final result of the net accuracy, 9000 iterations were neccesary to reduce the Loss value to its minimun and the architecture shows that it can reach an acceptable accuracy with few iterations.
-Note that by reducing the number of filters the network gained accuracy because the dataset does not have so much features learn, so the net found a better solution with a less number of parameters.
+In training graph shown below we can appreciate the final result of the net accuracy; 9000 iterations were neccesary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy with few iterations.
+Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters.
 \\

### 2017-07-20 PaperBCJ.tex
Enter Results
Enter Results

--- 2017-07-18 PaperBCJ.tex
@@
 
-Los resultados muestran que para el tiempo de Clasificacion por GPU ha empeorado un 66\%, principalmente debido a que la Libreria de OpenBLAS hace extenso uso de los hilos del CPU, con lo que no todos los parametros seran computados por GPU como en al anterior prueba.
-\\
+Los resultados muestran que para el tiempo de Clasificacion por GPU ha empeorado un 66\%, principalmente debido a que la Libreria de OpenBLAS hace extenso uso de los hilos del CPU causando que no todos los parametros seran computados por GPU como en la anterior prueba.
+En cambio, cuando se utiliza el CPU los resultados son mejores, debido a que las operaciones se ejecutan utilizando cada uno de los nucleos disponibles, en el caso de la CPU se noto un 22\% y para 6.3\% para el Raspberry Pi  \\
+
+The results shown that classification time by GPU get worse by 66\%, mainly due OpenBLAS make extense use of CPU Threads causing that not all the parameters of the net were computed by GPU like
 

### 2017-07-20 PaperBCJ.tex
Corrections
Corrections of Paper

@@
 Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture.
-In this paper we present the study of a convolutional neural network with two classes applied to the classification of plants of maize and weeds in real time, focused to fields of maize in its initial stage.
+In this paper the study of a convolutional neural network is presented, with two classes applied to the classification of plants of maize and weeds in real time, focused to fields of maize in its initial stage.
 The algorithm has two stages, segmentation of images and classification.
-In the segmentation we wanted to separate the target plant from the original image.
+Segmentation is intended to separate the target plant from the original image.
 While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage.
-The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, we experimented by modifying its number of filters, to analyze their  behavior.
+The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, (revisar esta linea) we experimented by modifying its number of filters, to analyze their behavior.
 Finally, the resulting network was tested on different processors to compare classification times.\\
@@
 Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes.
-Debido a la popularidad de la computacion por GPU(COMPLETAR IDEA), fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de procesamiento y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M.
-Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar los tiemposde clasificacion de imagenes en las arquitecturas de red.
-\\
+Debido a la popularidad de la computacion por GPU(IDEA COMPLETADA) por sus ventajas en el desarrollo de modelos de Redes Neuronales Convolucionales, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de clasificacion y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M.
+Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar el rendimiento de red en un sistema portable para su aplicacion en un sistema movil independiente .
+El hardware escogido sera probado para clasificar las imagenes y medir los tiempos de clasificacion para su posterior analisis.
+El hardware elegido será probado para clasificar imágenes, en cada clasificación se medirán los tiempos de procesamiento, para realizar un análisis si el hardware puede procesar en tiempo real \\
 
@@
 The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
-Due to the popularity of GPU computing(COMPLETAR IDEA), it was necessary to consider hardware compatible with parallel computing such as the Graphic Cards manufactured by NVIDIA.
+Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks (COMPLETAR IDEA), it was necessary to consider hardware compatible with parallel computing such as the Graphic Cards manufactured by NVIDIA.
 These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M.
-Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, an ARM Cortex-A53, 1.2GHz, 4 cores (CLARIFICAR IDEA) for testing  classification speed of network images.
+Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, an ARM Cortex-A53, 1.2GHz, 4 cores (CLARIFICAR IDEA) for test its performance in this embedded system for a future aplication in a independent mobile system.
+The hardware chosen will be tested to classify images, in each classification  a measure the times of processing will be performed, for make an analysis if the hardware can process in real time.
 \\
@@
 
-Para la aplicacion en este documento, se requiere el uso de Poderosas librerias de desarrollo para el procesamiento de imagenes y deep Learning, consideramos el uso de software libre para extender su uso en futuros prototipos, debido a esta consideracion hemos escogido la libreria de OpenCV debido a su eficiencia computacional y su enfoque a aplicaciones en tiempo real, para este caso fue utilizada(en referencia a OpenCV) para la adquisicion y segmentacion de las imagenes de muestra.
-Tambien hemos considerado Caffe debido a que esta desstinado a el entrenamiento y desarrollo de Redes Neuronales Convolucionales de Proposito General y otros modelos de Deep Learning con soporte completo de la Libreria de Computacion GPU CUDA y una generosa base de datos de recursos para aprendizaje  \\
+Para la aplicacion en este documento, se requiere el uso de Poderosas librerias de desarrollo para el procesamiento de imagenes y Deep Learning, fueron requeridas debido a que se necesita de Vision Artificial para realizar la segmentacion de plantas del suelo y generar imagenes independientes de cada una y la otra libreria sirve para la clasificacion de las imagenes obtenidas y su analisis de precision en diferentes arquitecturas de red con el fin de elegir la mas adecuada para nuestro proposito.
+Consideramos el uso de software libre para extender su uso en futuros prototipos, debido a esta consideracion hemos escogido la libreria de OpenCV debido a su eficiencia computacional y su enfoque a aplicaciones en tiempo real, para este caso fue utilizada(en referencia a OpenCV) para la adquisicion y segmentacion de las imagenes de muestra.
+Tambien hemos considerado Caffe debido a que esta desstinado a el entrenamiento y desarrollo de Redes Neuronales Convolucionales de Proposito General y otros modelos de Deep Learning con soporte completo de la Libreria de Computacion GPU CUDA y una generosa base de datos de recursos para aprendizaje de aplicaciones como Simple Regresion, Robotica, large-scale visual classification, etc.
+\\
 
@@
 Thus, OpenCV library was chosen due to its computational efficiency and focus on real-time applications \cite{opencv_library}; it was used specificaly for sample images acquisition and segmentation.
-Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other Deep Lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for MACHINE(?) learning.
+Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other Deep Lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for learning of applications such as simple regression, speech, robotics ,large-scale visual classification, etc.
 \\
@@
 Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above.
-For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi we used the Pixel OS for acquire images and test the classification performace of the CNN.
+For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS were used for acquire images and test the classification performace of the CNN.
 \\
@@
 
-Debido a la falta de datasets de plantas de Maize y Mala Hierba, fue necesario la busqueda de cultivos de maiz en su etapa inicial, para ese proposito nos hemos traslatado a Pillaro, esta ciudad es localizada en la Provincia de Tungurahua, en el Centro de la Sierra Ecuatoriana.
+Debido a la falta de datasets de plantas de Maize y Mala Hierba, Fue necesario buscar los cultivos de maíz en su etapa de desarrollo inicial porque las acciones tomadas en esta etapa por el agricultor tendrán un impacto en el rendimiento futuro del cultivo, para ese proposito nos hemos traslatado a Pillaro, esta ciudad es localizada en la Provincia de Tungurahua, en el Centro de la Sierra Ecuatoriana.
 Pillaro es un productor reconocido de cultivos andinos como: Maiz, Papas y frutas, por lo que podemos encontrar aqui muchos cultivos de maiz que sean utiles para nuestro proposito \\
 
-Due to the lack of weed and maize plant datasets, it was necessary to search maize crops in its initial development stage for...(COMPLETAR IDEA).
+Due to the lack of weed and maize plant datasets, it was necessary to search maize crops in its initial development stage because the taken actions in this stage by the farmer will impact in the future yield of the crop (IDEA COMPLETADA).
 Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples.
@@
 
-Las muestras fueron obtenidas de imagenes capturas en esos campos de maiz, consideramos escoger cultivos de maiz donde podamos visualmente discrimiar las plantas del cultivo de la mala yerba.
+Las muestras fueron obtenidas de imagenes capturas en esos campos de maiz, consideramos escoger cultivos de maiz donde podamos visualmente discrimiar las plantas del cultivo de la mala yerba para para facilitar la segmentacion de las imágenes y para proporcionar a red de muestras confiables que permiten al modelo aprender correctamente todas las características de la planta real.
 Las etapas del Maiz (V3-V7) fueron usadas para tomar muestras.
@@
 Samples were obtained from images captured in different maize fields.
-Crops were weed and maize plants could be visually discriminated were chosen in order to (SUSTENTAR IDEA).
+Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and for provide to Net of reliable samples which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD).
 Maize at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
@@
 al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations.
-In addition, \cite{sladojevic2016deep} mention that geometric transformations(?) allow overfitting reduction  and improves the precision in the training process.
+In addition, the geometric transformations \cite{sladojevic2016deep} (Si es verdad) allow overfitting reduction and improves(revisar correspondencia persona) the precision in the training process.
 For this reason, image rotations each 30 degrees were made, obtaining an increment of the dataset by 12 times, thus increasing the chances of recognizing plants that are in any orientation effectively.
@@
 One of the characteristics of the CNN is that these can have multiple architectures, each architecture can reach different results depending on the application.
-For the present document we have considered four CNN architectures: two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+For the present document four CNN architectures have been considered: two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
 \\
@@
 
-So, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2 (QUE?), then again a second layer of convolution that has 16 filters is applied, size of kernel 5 and a stride of 1 (QUE), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image was has size of 16x16x16.
+So, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2 (QUE?
+corregido), then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1 (QUE corregido), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image was has size of 16x16x16.
 Finally the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons.
@@
 
-In training graph shown below we can appreciate the final result of the net accuracy; 9000 iterations were neccesary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy with few iterations.
+In training graph shown below the final result can be appreciated of the net accuracy; 9000 iterations were neccesary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy with few iterations.
 Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters.
@@
 
-For this stage, we considered another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weed, obtained in different maize crops that the training dataset.
-For this test we have measured the average time of ten classifications of each image of this dataset with the hardware that we own, we started the classification in Caffe without modifications in Software.
+For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weed were considered, obtained in different maize crops that the training dataset.
+For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image were obtained with the chosen hardware, we started the classification in Caffe without modifications in Software.
 The results were comparated between cNET with 64 and 16 filters and there are shown in the next Table \ref{table:4}.\\
@@
 \end{tabular}
-\caption{Test}
+\caption{Test with the three types of Hardware}
 \label{table:4}
@@
 
-Like the table shown the best results in times of classification were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so we consider the RaspBerry Pi for the analysis of classification performance.
+Like the table shown the best results in times of classification were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so the Raspberry Pi were considered for the analysis of classification performance.
 With cNET of 64 filters the results of time of classification was 615 miliseconds, so it time isn\'t the optimum for our objective that it is the approximation to classification in a real time.\\
@@
 
-The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document we used Batching to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS Math Software.
-For each hardware, we recompiled Caffe with OpenBLAS instead of Atlas, in the program we entered all images in a vector to be classified in an only batch per each class, also we configure OpenBLAS to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\
+The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document Batching were used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software.
+For each hardware, Caffe were recompiled with OpenBLAS instead of Atlas, in the program all images  were entered in a vector to be classified in an only batch per each class, also OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\
 

### 2017-07-20 PaperBCJ.tex
Corrections
Corrections

@@
 Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above.
-For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS were used for acquire images and test the classification performace of the CNN.
+For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS was used for acquire images and test the classification performace of the CNN.
 \\
@@
 Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and for provide to Net of reliable samples which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD).
-Maize at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
+Maize Plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
 To record the samples, a camera was centered over the target plant, insuring that the capture shows all features of the maize plant.
@@
  Iterations & 3000 & 3000 & 3000 & 3000 \\ 
- Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
+ Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
  Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
@@
 For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weed were considered, obtained in different maize crops that the training dataset.
-For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image were obtained with the chosen hardware, we started the classification in Caffe without modifications in Software.
+For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image was obtained with the chosen hardware, we started the classification in Caffe without modifications in Software.
 The results were comparated between cNET with 64 and 16 filters and there are shown in the next Table \ref{table:4}.\\
@@
 \centering
-\begin{tabular}{|p{1.1cm}|p{1.9cm}|p{1.95cm}|p{2cm}|} 
+\begin{tabular}{|p{1.1cm}|p{1.5cm}|p{1.5cm}|p{2.1cm}|} 
  \hline
@@
 
-The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document Batching were used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software.
+The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document batching was used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software.
 For each hardware, Caffe were recompiled with OpenBLAS instead of Atlas, in the program all images  were entered in a vector to be classified in an only batch per each class, also OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\
@@
 
-The results shown that classification time by GPU get worse by 66\%, mainly due OpenBLAS make extense use of CPU Threads causing that not all the parameters of the net were computed by GPU like
+The results show that for the GPU Classification time it has worsened by 66 \%, mainly because the OpenBLAS Library makes extensive use of the CPU threads causing that not all parameters will be computed by GPU as in the previous test.
+Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores, in the case of the CPU we notice a 22 \% and for 6.3 \% for the Raspberry Pi \\
 
@@
 
--Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 99\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases.
+-Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 97.26\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases.
 \\
 
-In this paper  we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 99.33 \% of accuracy of training, using a dataset of both classes of 44580 segmented images.
+In this paper  we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 97.23 \% of accuracy of training, using a dataset of both classes of 44580 segmented images.
 \\
@@
 
-In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuray of the net, it value fell 1 \% in comparation with the original net.
+In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuracy of the net, it value increased 1 \% in comparation with the original net.
 \\

### 2017-07-20 PaperBCJ.tex
Conclusion
A new conclusion

@@
  \hline
- CPU & 89.11\% & 87.13\% & 10.92 ms \\ [0.95ex]
+ CPU & 89.11\% & 92.08\% & 10.92 ms \\ [0.95ex]
  \hline
- CPU(Raspberry Pi) & 89.11\% & 87.13\% & 150.8 ms \\ [0.95ex]
+ CPU(Raspberry Pi) & 89.11\% & 92.08\% & 150.8 ms \\ [0.95ex]
  \hline
@@
 The study demostrated that is better to perform some geometrical tranformations to the Dataset images due it benefits to improve the classification of plants because the plants ever have different orientations in the crop field.
+\\
+
+-El uso de Multithreading y Batching a traves de la libreria OpenBLAS es muy beneficioso en el caso de usar CPU, aumentando la rapidez de procesamiento en el porcentaje superior al 20\%, con la Rasberry pi, se obtuvo una minima mejora, en cambio fue pejudicial con el uso de GPU , pues provoca que la rapidez se reduzca considerablemente.
+\\
+
+-The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%, with the Rasberry pi, a minimum improvement was obtained, instead it was pejudicioal with the use of GPU, because it causes that the speed is reduced considerably.
+\\
 

### 2017-07-20 PaperBCJ.tex
Changes
Full Paper translated in PDF

--- 2017-07-20 PaperBCJ.tex
@@
 \usepackage{graphicx}
+\usepackage{verbatim}
 \usepackage{array}
@@
 
--Deep Learning ha tenido un papel muy importante en los tiempos modernos, siendo muy utilizado en vision artificial y especialmente en reconocimiento de patrones, lo cual abre muchas puertas en los campos de aplicacion siendo uno de ellos la agricultura de presicion.En este paper presentamos el estudio una red neuronal convolucional aplicada a la clasificacion de plantas de maiz y de mala hierba en tiempo real, dirigida a campos de maiz en su etapa inicial.El algoritmo cuenta con dos etapas, segmentacion de imagenes y la clasificacion.
-En la segmentacion se busca separar de la imagen las plantas de forma individual.
-Mientras que la clasificacion se da a traves de la red neuronal convolucional, previamente entrenada con un dataset generado mediante la etapa de segmentacion.
-El rendimiento de la red se ilustra mediante analisis y comparaciones con diferentes arquitecturas de red, luego con la red que presento mejores resultados, se experimeto modificando su numero de filtros, para analizar su comportamiento.
-Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion.\\
-
 Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture.
@@
 Finally, the resulting network was tested on different processors to compare classification times.\\
+
+\begin{comment}
+-Deep Learning ha tenido un papel muy importante en los tiempos modernos, siendo muy utilizado en vision artificial y especialmente en reconocimiento de patrones, lo cual abre muchas puertas en los campos de aplicacion siendo uno de ellos la agricultura de presicion.En este paper presentamos el estudio una red neuronal convolucional aplicada a la clasificacion de plantas de maiz y de mala hierba en tiempo real, dirigida a campos de maiz en su etapa inicial.El algoritmo cuenta con dos etapas, segmentacion de imagenes y la clasificacion.
+En la segmentacion se busca separar de la imagen las plantas de forma individual.
+Mientras que la clasificacion se da a traves de la red neuronal convolucional, previamente entrenada con un dataset generado mediante la etapa de segmentacion.
+El rendimiento de la red se ilustra mediante analisis y comparaciones con diferentes arquitecturas de red, luego con la red que presento mejores resultados, se experimeto modificando su numero de filtros, para analizar su comportamiento.
+Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion.
+\end {comment}
 \end{abstract}
@@
 \section{Matherials and Methods}
-
+\begin{comment}
 El desarrollo del modelo para la identificacion de mala hierba y maiz usando Redes Neuronales Convoluciones se describe abajo: 
-\\
+\end{comment}
 
@@
 \subsection{Hardware}
-
+\begin{comment}
 Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes.
@@
 El hardware escogido sera probado para clasificar las imagenes y medir los tiempos de clasificacion para su posterior analisis.
-El hardware elegido será probado para clasificar imágenes, en cada clasificación se medirán los tiempos de procesamiento, para realizar un análisis si el hardware puede procesar en tiempo real \\
+El hardware elegido será probado para clasificar imágenes, en cada clasificación se medirán los tiempos de procesamiento, para realizar un análisis si el hardware puede procesar en tiempo real
+\end{comment}
 
@@
 \subsection{Software}
-
+\begin{comment}
 Para la aplicacion en este documento, se requiere el uso de Poderosas librerias de desarrollo para el procesamiento de imagenes y Deep Learning, fueron requeridas debido a que se necesita de Vision Artificial para realizar la segmentacion de plantas del suelo y generar imagenes independientes de cada una y la otra libreria sirve para la clasificacion de las imagenes obtenidas y su analisis de precision en diferentes arquitecturas de red con el fin de elegir la mas adecuada para nuestro proposito.
@@
 Tambien hemos considerado Caffe debido a que esta desstinado a el entrenamiento y desarrollo de Redes Neuronales Convolucionales de Proposito General y otros modelos de Deep Learning con soporte completo de la Libreria de Computacion GPU CUDA y una generosa base de datos de recursos para aprendizaje de aplicaciones como Simple Regresion, Robotica, large-scale visual classification, etc.
-\\
+\end{comment}
 
@@
 Thus, OpenCV library was chosen due to its computational efficiency and focus on real-time applications \cite{opencv_library}; it was used specificaly for sample images acquisition and segmentation.
-Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other Deep Lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for learning of applications such as simple regression, speech, robotics ,large-scale visual classification, etc.
+Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other Deep Lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for learning of applications such as simple regression, speech, robotics, large-scale visual classification, etc.
 \\
-
+\begin{comment}
 Tambien el la etapa de desarrollo fue importante el suo del Sistema Operativo Linux, sus caracteristicas son: Sistema Operativo Ligero y Libre tambien completamente compatible con el software mencionado anteriormente.
-En la computadora principal fue usado la Distribucion Ubuntu Linux 16.04 por su soporte oficial a CUDA, Caffe y OpenCV, tambien en la Raspberry Pi fue usado el Sistema Operativo Pixel para adquirir imagenes y probar el rendimiento de clasificacion la Red Neuronal Convolucional \\
+En la computadora principal fue usado la Distribucion Ubuntu Linux 16.04 por su soporte oficial a CUDA, Caffe y OpenCV, tambien en la Raspberry Pi fue usado el Sistema Operativo Pixel para adquirir imagenes y probar el rendimiento de clasificacion la Red Neuronal Convolucional
+\end{comment}
 
@@
 \subsection{Dataset Description}
-
+\begin{comment}
 Debido a la falta de datasets de plantas de Maize y Mala Hierba, Fue necesario buscar los cultivos de maíz en su etapa de desarrollo inicial porque las acciones tomadas en esta etapa por el agricultor tendrán un impacto en el rendimiento futuro del cultivo, para ese proposito nos hemos traslatado a Pillaro, esta ciudad es localizada en la Provincia de Tungurahua, en el Centro de la Sierra Ecuatoriana.
-Pillaro es un productor reconocido de cultivos andinos como: Maiz, Papas y frutas, por lo que podemos encontrar aqui muchos cultivos de maiz que sean utiles para nuestro proposito \\
+Pillaro es un productor reconocido de cultivos andinos como: Maiz, Papas y frutas, por lo que podemos encontrar aqui muchos cultivos de maiz que sean utiles para nuestro proposito
+\begin{comment}
 
@@
 
+\begin{comment}
 Las muestras fueron obtenidas de imagenes capturas en esos campos de maiz, consideramos escoger cultivos de maiz donde podamos visualmente discrimiar las plantas del cultivo de la mala yerba para para facilitar la segmentacion de las imágenes y para proporcionar a red de muestras confiables que permiten al modelo aprender correctamente todas las características de la planta real.
@@
 Para obtener las muestra, centramos la camara sobre la platna objetivo, asegurandonos que la captura muestre todas las caracteristicas de la planta de maiz, esto fue posible al monitorear el proceso por una pantalla externa.
-Unas muestras de las imagenes capturadas son mostradas a continuacion: \\
+Unas muestras de las imagenes capturadas son mostradas a continuacion:
+\begin{comment}
 
@@
 	\end{figure}
-
-Tambien fue necesario obtener imagenes de las malas hierbas mas comunes en los campos de maiz de Pillaro, para permitir a la Red discrimiar entre las dos clases definidas en el Dataset.\\
+\begin{comment}
+Tambien fue necesario obtener imagenes de las malas hierbas mas comunes en los campos de maiz de Pillaro, para permitir a la Red discrimiar entre las dos clases definidas en el Dataset.
+\end{comment}
 
 Also, it was necessary to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the network to discriminate between the two defined classes of the dataset. \\
-
-Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria \\
+\begin{comment}
+Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria
+\end{comment}
 
@@
 \end{equation} 
-
+\begin{comment}
 Despues de la imagen fue segmentada, para diferenciarla del suelo y otros elementos que no sean plantas, las imagenes originales fueron enmascaradas con la mascara binaria para proveer al Dataset caracteristicas de Color del Maiz y de la Mala Hierba.
@@
 El proceso se ilustra de mejor manera en la siguiente figura.
-\\
+\end{comment}
 
@@
 
+\begin{comment}	
 Debemos acotar que hemos etiquetado manualmente las imagenes en dos clases, maiz y mala hierba, teniendo en cuenta que las imagenes no se repitan(\textbf{corregir}).
 En la presente imagen presentamos los resultados finales de las imagenes procesadas que conforman el dataset.
-\\
+\end{comment}
 
@@
 
+\begin{comment}	
 Una vez completada el procesamiento de imagenes, donde fueron obtenidas 2835 imagenes de maiz y 880 images de Mala Hierba, Lee et.
 Al dicen que una vez que la CNN ha alcanzado una precision aceptable, el dataset se puede extender por transformaciones geometricas, en adicion sladojevic mencionan que esto permite a reducir el sobreajuste y para mejorar la precision en el entrenamiento, razon por la cual hizimos 11 rotaciones cada 30 grados, obteniendo de esta forma el incremento(corregir) del dataset en 12 veces y tener mejores probabilidades de reconocer als plantas en cualquier orientaciones.
-\\
+\end{comment}
 
@@
 
-Para la fase de validacion, hemos escogido aletariamente la quinta parte del total de imagenes de cada clase, asi que tenemos la siguiente tabla con la distribucion del dataset.\\
+\begin{comment}	
+Para la fase de validacion, hemos escogido aletariamente la quinta parte del total de imagenes de cada clase, asi que tenemos la siguiente tabla con la distribucion del dataset.
+\end{comment}
 
@@
 
+\begin{comment}	
 Despues que el ultimo paso ha sido terminado, fue necesario clasificar las imagenes del Maiz y Mala Hierba, un metodo muy preciso de Clasificacion de Imagenes son las Redes Neuronales Convolucionales(CNN), estos modelos son complejos pero eficientes con un alto grado de discriminacion y han demostrado que tienen unos buenos resultados en la Clasificacion de Imagenes, Deteccion de Objetos y Fine*Grained Classification.
-Tambien son aplicados en la Agricultura de Precision para la correcta identificacion de plantas\\
+Tambien son aplicados en la Agricultura de Precision para la correcta identificacion de plantas
+\end{comment}
 
@@
 
-Una de las caracteristicas de las CNN is que estas pueden tener multiples arquitecturas, cada arquitectura puede alcanzar diferentes resultados dependiendo de la aplicacion, para el presente documento hemos considerado cuatro arquitecturas de CNN: Dos modelos fueron escogidos del Caffe Zoo Model(es un recurso libre liberado por los Desarrolladores de Caffe) Lenet y AlexNet, tambien Potena y Nardi han usado adicionalmente dos tios de modelos, sNET y cNET, estos han sido exitosamente probados en la clasificacion de plantas en cultivos, con las redes secogidas, cada una fue entrenada con un mismo Solver de Tipo AdaDelta, con el mismo Dataset y los resultados del entrenamiento son los siguientes: \\
+\begin{comment}	
+Una de las caracteristicas de las CNN is que estas pueden tener multiples arquitecturas, cada arquitectura puede alcanzar diferentes resultados dependiendo de la aplicacion, para el presente documento hemos considerado cuatro arquitecturas de CNN: Dos modelos fueron escogidos del Caffe Zoo Model(es un recurso libre liberado por los Desarrolladores de Caffe) Lenet y AlexNet, tambien Potena y Nardi han usado adicionalmente dos tios de modelos, sNET y cNET, estos han sido exitosamente probados en la clasificacion de plantas en cultivos, con las redes secogidas, cada una fue entrenada con un mismo Solver de Tipo AdaDelta, con el mismo Dataset y los resultados del entrenamiento son los siguientes:
+\end{comment}
 
@@
 
-Dentro de los parametros mostrados en la Tabla, consideramos la red que alcanze la mas alta tasa de precision y mas baja tasa de perdida, claramente la cNET es la escogida, debido a que esta presenta una precision cercana a la clasificacion humana\\
+\begin{comment}	
+Dentro de los parametros mostrados en la Tabla, consideramos la red que alcanze la mas alta tasa de precision y mas baja tasa de perdida, claramente la cNET es la escogida, debido a que esta presenta una precision cercana a la clasificacion humana
+\end{comment}
 
@@
 
+\begin{comment}	
 Aunque lo resultados dados de la red fueron excelentes, uno de los propositos principales de este documento es una aproximacion de procesamiento en tiempo real, entonces el numero de parametros a ser computados va a ser un problema, entonces consideramos modificar la red para mejorar el tiempo de procesamiento.
 Para lograr esto, fue necesario reducir el numero de filtros de cNET de 64 a 16, en la tabla siguiente se muestran los resultados del entrenamiento para los dos tipos de red.
-\\
+\end{comment}
 
@@
 
+\begin{comment}	
 Esta reduccion permitio reducir el numero de parametros de 1651376(es un 25\% de parametros de la red original), y acerca de la precision d ela red, fue affectada un poco pero asi consigue un 97.2\% de precision en el entrenamiento.
-\\
+\end{comment}
 
@@
 
-Entonces el modelo completo de red se forma de la siguiente manera: La capa de entrada que recibe una imagen RGB de 64x64 pixeles, seguida por una capa de convolucion de 16 filtros, un kernel de 5 y stride de 1 pixel, esta capa obtiene solo las principales caracteristicas de la imagen, despues una capa de pooling es aplicada, la cual tiene la funcion de encontrar los maximos valores de las capas, con un tamanho de kernel y stride de 2, despues nuevamente se aplica una segunda capa de convolucion que tiene 16 filtros, ancho de kernel de 5 y un stride de 1, seguido nuevamente de una nueva capa de pooling con un tamanho de kernel y de stride de 2, obteniendo asi una imagen de salida de de tamanho 16x16x16 y finalmente se completa la red con tres capas consecutivas fully-connected, la primera con 384 neuronas, la segunda con 192 y la ultima con dos neuronas que representara la capa las dos clases que se busca clasificar, el modelo resultante se muestra en la siguiente imagen \\
+\begin{comment}	
+Entonces el modelo completo de red se forma de la siguiente manera: La capa de entrada que recibe una imagen RGB de 64x64 pixeles, seguida por una capa de convolucion de 16 filtros, un kernel de 5 y stride de 1 pixel, esta capa obtiene solo las principales caracteristicas de la imagen, despues una capa de pooling es aplicada, la cual tiene la funcion de encontrar los maximos valores de las capas, con un tamanho de kernel y stride de 2, despues nuevamente se aplica una segunda capa de convolucion que tiene 16 filtros, ancho de kernel de 5 y un stride de 1, seguido nuevamente de una nueva capa de pooling con un tamanho de kernel y de stride de 2, obteniendo asi una imagen de salida de de tamanho 16x16x16 y finalmente se completa la red con tres capas consecutivas fully-connected, la primera con 384 neuronas, la segunda con 192 y la ultima con dos neuronas que representara la capa las dos clases que se busca clasificar, el modelo resultante se muestra en la siguiente imagen
+\end{comment}
 
@@
 
-En la grafica de entrenamiento que se muestra a continuacion podemos apreciar el resultado final de precision de la red, la 9000 iteraciones fueron necesarias para reducir el la capa de Loss al minimo y la arquitectura demostro alcanzar rapidamente un valor aceptable de precision, notose que reduciendo el numero de filtros la red gano en precision porque las imagenes del dataset no tienen demasiadas caracteristicas para procesar, por lo que la red fue mejor solucionable con un numero menor parametros de red\\
+\begin{comment}		
+En la grafica de entrenamiento que se muestra a continuacion podemos apreciar el resultado final de precision de la red, la 9000 iteraciones fueron necesarias para reducir el la capa de Loss al minimo y la arquitectura demostro alcanzar rapidamente un valor aceptable de precision, notose que reduciendo el numero de filtros la red gano en precision porque las imagenes del dataset no tienen demasiadas caracteristicas para procesar, por lo que la red fue mejor solucionable con un numero menor parametros de red
+\end{comment}
 
@@
 
+\begin{comment}	
 Para esta etapa, consideramos otro dataset con 202 imagenes de plantas de maiz en la etapa V3-V7 y 202 dos imagenes de mala hierba obtenidas en campos de maiz diferentes a los que pertenecen al dataset de entrenamiento, para esta prueba se ha medido los tiempos de clasificacion promedio de diez clasificaciones de este dataset en los distintos hardwares que poseemos, empezamos con la clasificacion en Caffe sin modificaciones de software.
-Los resultados fueron comparados entre la red cNET de 64 y 16 filtros y se muestran en la siguiente Tabla\\
+Los resultados fueron comparados entre la red cNET de 64 y 16 filtros y se muestran en la siguiente Tabla
+\end{comment}
 
@@
 
+\begin{comment}	
 Como la tabla muestra, los mejores resultados en tiempos de clasificacion fueron alcanzados por el procesador por GPU, esta es la mejor opcion para clasificar una gran cantidad de imagenes, sin embargo este proyecto esta psenado para ser portable, por lo que consideramos al Raspberry Pi para el analisis del rendimiento de classificacion.
 Con la cNET de 64 filtros, los ersultos de tiempo de clasificacion fueron de 615 milisegundos, pero este tiempo no es optimo para nuestro objetivo que es la aproximacion de clasificacion en tiempo real.
-\\
+\end{comment}
 
@@
 
+\begin{comment}	
 Los resultados presentados anteriormente no son definitivos, pues Caffe presenta algunas formas de optimizar la clasificacion de datasets de imagenes, para este documento se ha utilizado el Agrupamiento de Imagenes en una sola estructura(Batch) para clasificar el dataset de cada clase en un single forward pass y la utilizacion de Multithreading a traves del software matematico OpenBLAS.
 Para cada hardware se volvio a compilar Caffe con OpenBLAS en lugar de Atlas y en el programa se ingresaron todas las imagenes en un vector para ser clasificado un solo grupo de imagenes por cada clase, ademas se configuro a OpenBLAS para que use 4 Nucleos del cada hardware para obtener resultados parejos, los resultados obtenidos son los siguientes.
-\\
+\end{comment}
 
@@
  \hline
- CPU & 89.11\% & 87.13\% & 10.92 ms \\ [0.95ex]
+ CPU & 89.11\% & 92. 08\% & 10.92 ms \\ [0.95ex]
  \hline
- CPU(Raspberry Pi) & 89.11\% & 87.13\% & 150.8 ms \\ [0.95ex]
+ CPU(Raspberry Pi) & 92.08\% & 87.13\% & 150.8 ms \\ [0.95ex]
  \hline
@@
 
+\begin{comment}	
 Los resultados muestran que para el tiempo de Clasificacion por GPU ha empeorado un 66\%, principalmente debido a que la Libreria de OpenBLAS hace extenso uso de los hilos del CPU causando que no todos los parametros seran computados por GPU como en la anterior prueba.
-En cambio, cuando se utiliza el CPU los resultados son mejores, debido a que las operaciones se ejecutan utilizando cada uno de los nucleos disponibles, en el caso de la CPU se noto un 22\% y para 6.3\% para el Raspberry Pi \\
+En cambio, cuando se utiliza el CPU los resultados son mejores, debido a que las operaciones se ejecutan utilizando cada uno de los nucleos disponibles, en el caso de la CPU se noto un 22\% y para 6.3\% para el Raspberry Pi
+\end{comment}
 
@@
 
+\begin{comment}	
 -Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 97.26\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases.
 \\
+\end{comment}
 
@@
 
-Para buscar un procesamiento apropiado para trabajar en tiempo real, se experimento reduciendo el numero de filros de las capas de la red desde 64 hasta 16, logrando con esto disminuir el numero de parametros a ser computados durante la clasificacion, obteniendo tambien un tiempo de procesamiento de 2,5 veces menor al de la red original, este cambio tuvo un bajo impacto en la precision de entrenamiento de la red, pues este valor cayo en un 1\%, con respecto a la red original.\\
+\begin{comment}	
+Para buscar un procesamiento apropiado para trabajar en tiempo real, se experimento reduciendo el numero de filros de las capas de la red desde 64 hasta 16, logrando con esto disminuir el numero de parametros a ser computados durante la clasificacion, obteniendo tambien un tiempo de procesamiento de 2,5 veces menor al de la red original, este cambio tuvo un bajo impacto en la precision de entrenamiento de la red, pues este valor cayo en un 1\%, con respecto a la red original.
+\begin{end}
 
@@
 
--Ademas nuestros experimentos al utilizar diferentes procesadores, demostraron que se obtienen mejores resultados en cuanto a velocidad al trabajar con una a tarjeta grafica ENVIDIA que posee soporte CUDA debido a su arquitectura de computacion paralela, siendo este 10 veces mas rapido que el CPU normal y 100 veces mas rapido que una RaspBerry Pi3.\\
+\begin{comment}	
+-Ademas nuestros experimentos al utilizar diferentes procesadores, demostraron que se obtienen mejores resultados en cuanto a velocidad al trabajar con una a tarjeta grafica ENVIDIA que posee soporte CUDA debido a su arquitectura de computacion paralela, siendo este 10 veces mas rapido que el CPU normal y 100 veces mas rapido que una RaspBerry Pi3.
+\end{comment}
 
@@
 
--El estudio demostro que es mejor obtener las imagenes para el dataset realizar algunos giros en las imagenes de las plantas del dataset, debido a que esto aporta mejoras en la identificacion de plantas, pues estas siempre tienen orientaciones diferentes.\\
--
+\begin{comment}	
+-El estudio demostro que es mejor obtener las imagenes para el dataset realizar algunos giros en las imagenes de las plantas del dataset, debido a que esto aporta mejoras en la identificacion de plantas, pues estas siempre tienen orientaciones diferentes.
+\end{comment}
 
@@
 \section*{Acknowledgment}
-
+\begin{comment}	
 -Damos gracias a la Graja Agroecologica y Demostrativa de Pillaro y a dueños de cultivos de maiz de lugares aledaños.
 que nos permitieron tomar muestras de plantas ,para la obtencion del dataset del proyecto.
-+The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to conform the dataset of this project.
-\\
--Este trabajo ha sido apoyada por la Universidad de las Fuerzas Armadas ESPE Extension Latacunga. \\
+
+-Este trabajo ha sido apoyada por la Universidad de las Fuerzas Armadas ESPE Extension Latacunga. 
+\end{comment}
 

### 2017-07-20 PaperBCJ.tex
Auto stash before merge of "master" and "origin/master"
Table of fps

@@
  \hline
- CPU & 89.11\% & 92. 08\% & 10.92 ms \\ [0.95ex]
+ CPU & 89.11\% & 92.08\% & 10.92 ms \\ [0.95ex]
  \hline
- CPU(Raspberry Pi) & 92.08\% & 87.13\% & 150.8 ms \\ [0.95ex]
+ CPU(Raspberry Pi) & 89.11\% & 92.08\% & 150.8 ms \\ [0.95ex]
  \hline
@@
 Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores, in the case of the CPU we notice a 22 \% and for 6.3 \% for the Raspberry Pi \\
+
+\begin{comment}	
+Ahora para comparar todos estos resultados tomando en cuenta que una imagen capturada por la camara a una altura de 1,5 m puede enfocar un aproximado de 6 plantas de maiz, y segun la cantidad de mala hierba, se considerara un promedio de 12 plantas, dando un total de 18 plantas aproximadamente.
+Con esto se analiza cuantos frames por segundo seria lo adecuado para la adquisicion de imagenes.
+\end{comment}	
+Now to compare all these results taking into account that an image captured by the camera at a height of 1.5 m can focus an approximate 6 plants of maize, and according to the amount of weed, an average of 12 plants, Giving a total of about 18 plants.
+This analyzes how many frames per second would be appropriate for the acquisition of images.
+\begin{table}[h!]
+\centering
+\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.7cm}|p{1.7cm}|p{2.0cm}|} 
+ \hline
+ \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{RaspBerry Pi 3 with Threading} \\ 
+ \hline 
+ Time(s) & 0.0171 & 0.196 & 7.714  \\ [0.95ex]
+ \hline
+ FPS & 58.47  & 5.08 & 0.36  \\ [0.95ex]
+ \hline
+\end{tabular}
+\caption{Test of a complete image and the frames per second}
+\label{table:5}
+\end{table}
 

### 2017-07-20 PaperBCJ.tex
cambios20juliotarde
cambios hechos en la ultima hora de oficina

@@
 
-Nowadays, one of agriculture's challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation.
-There are studies that show the impact of Weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha.
-Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops.
+Nowadays, one of agriculture's challenges is the development of precision agriculture techniques focused on weed and crop segmentation.
+There are studies that show the impact of weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha.
+Currently, growing development of artificial vision and machine learning algorithms has allowed researchers to propose solutions for weed segmentation in different types of crops (con la finalidad de...).
 \\
@@
 The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
-Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks (COMPLETAR IDEA), it was necessary to consider hardware compatible with parallel computing such as the Graphic Cards manufactured by NVIDIA.
+Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better speed processing, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA.
 These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M.
-Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, an ARM Cortex-A53, 1.2GHz, 4 cores (CLARIFICAR IDEA) for test its performance in this embedded system for a future aplication in a independent mobile system.
-The hardware chosen will be tested to classify images, in each classification  a measure the times of processing will be performed, for make an analysis if the hardware can process in real time.
+Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in a independent mobile system that could be implemented in an embedded system.
+The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time.
 \\
@@
 
-The use of powerful libraries of Image Processing and Deep Learning Development was required due to....
+The use of powerful libraries of image processing and deep learning development was required due to..(ver espanol)..
 .
@@
 Thus, OpenCV library was chosen due to its computational efficiency and focus on real-time applications \cite{opencv_library}; it was used specificaly for sample images acquisition and segmentation.
-Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other Deep Lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for learning of applications such as simple regression, speech, robotics, large-scale visual classification, etc.
+Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other deep lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for learning of applications such as simple regression, speech, robotics, large-scale visual classification, etc.
 \\
@@
 For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS was used for acquire images and test the classification performace of the CNN.
+(cambiar union de ideas)
 \\
@@
 
-Due to the lack of weed and maize plant datasets, it was necessary to search maize crops in its initial development stage because the taken actions in this stage by the farmer will impact in the future yield of the crop (IDEA COMPLETADA).
+Due to the lack of weed and maize plant datasets, it was necessary to search for maize crops in its initial development stage because the taken actions in this stage by the farmer will impact in the future yield of the crop (IDEA COMPLETADA).
 Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples.
-P\'illaro it is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits.
+P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits.
 Due to its year-long production season, many maize crops at its initial development stage were found in this area.
@@
 Samples were obtained from images captured in different maize fields.
-Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and for provide to Net of reliable samples which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD).
+Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and to provide reliable samples to the network, which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD).
 Maize Plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
@@
 
-Also, it was necessary to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the network to discriminate between the two defined classes of the dataset. \\
+Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset. \\
 \begin{comment}
@@
 Original images were masked with the binary mask to provide the dataset with color features of maize and weed plants.
-Once the segmented images were obtained, images that had a resolution lower than 64x64 pixels were removed because its size was smaller than the size of the network input layer.
+Once the segmented images were obtained, the files that had a resolution lower than 64x64 pixels were removed because its size was smaller than the size of the network input layer.
 Besides, the processing of these small images was not convenient since its total area was much smaller than the maize sample images.
@@
 al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations.
-In addition, the geometric transformations \cite{sladojevic2016deep} (Si es verdad) allow overfitting reduction and improves(revisar correspondencia persona) the precision in the training process.
+In addition, the geometric transformations \cite{sladojevic2016deep} (Si es verdad) allow overfitting reduction and improve precision in the training process.
 For this reason, image rotations each 30 degrees were made, obtaining an increment of the dataset by 12 times, thus increasing the chances of recognizing plants that are in any orientation effectively.
@@
 
-One of the characteristics of the CNN is that these can have multiple architectures, each architecture can reach different results depending on the application.
-For the present document four CNN architectures have been considered: two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+One of the characteristics of CNN is that these can have multiple architectures, each architecture can reach different results depending on the application.
+For the present document four CNN architectures have been considered: two models were chosen from the Caffe Zoo Model(it is a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}.
+With the four Nets chosen, each one was trained with the same Solver of type AdaDelta and with the same dataset, the results of training are the following.
 \\
@@
 
-Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of this system in real time.
+Although results given by this type of network are excellent, one of the main purposes of this paper was the implementation of this system in real time.
 The number of parameters to be computed by the selected network were numerous, so network modifications in order to improve processing time had to be made.
@@
 
-This filter reduction permitted to decrease the number of parameters to 1651376 (this represents only 25\% of the original network parameters) without compromising the network precision in a significant way; it still reached a 97.2\% of accuracy.\\
+This filter reduction permitted to decrease the number of parameters to 1651376 (this represents only 25\% of the original network parameters) without compromising the network precision; it still reached a 97.2\% of accuracy.\\
 
@@
 So, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2 (QUE?
-corregido), then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1 (QUE corregido), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image was has size of 16x16x16.
+corregido), then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1 (QUE corregido), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16.
 Finally the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons.
@@
 
-For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weed were considered, obtained in different maize crops that the training dataset.
+For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weeds were considered, obtained in different maize crops that the training dataset.
 For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image was obtained with the chosen hardware, we started the classification in Caffe without modifications in Software.

### 2017-07-20 PaperBCJ.tex
Other Conclusion
add an other conclusion

@@
 Now to compare all these results taking into account that an image captured by the camera at a height of 1.5 m can focus an approximate 6 plants of maize, and according to the amount of weed, an average of 12 plants, Giving a total of about 18 plants.
-This analyzes how many frames per second would be appropriate for the acquisition of images.
+This analyzes how many frames per second(fps) would be appropriate for the acquisition of images.
 \begin{table}[h!]
 \centering
-\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.7cm}|p{1.7cm}|p{2.0cm}|} 
+\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.8cm}|p{1.8cm}|p{1.9cm}|} 
  \hline
- \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{RaspBerry Pi 3 with Threading} \\ 
+ \textbf{Parameter} &\textbf{GPU(Without Batching) } & \textbf{CPU with Batching} & \textbf{RaspBerry Pi 3 with Batching} \\ 
  \hline 
- Time(s) & 0.0171 & 0.196 & 7.714  \\ [0.95ex]
+ \textbf{Time(s)} & 0.0171 & 0.196 & 2.714  \\ [0.95ex]
  \hline
- FPS & 58.47  & 5.08 & 0.36  \\ [0.95ex]
+ \textbf{FPS} & 58.47  & 5.08 & 0.36  \\ [0.95ex]
  \hline
 \end{tabular}
-\caption{Test of a complete image and the frames per second}
+\caption{Test of comparation with the frames per second of the different processors}
 \label{table:5}
@@
 
+\begin{comment}	
 -El uso de Multithreading y Batching a traves de la libreria OpenBLAS es muy beneficioso en el caso de usar CPU, aumentando la rapidez de procesamiento en el porcentaje superior al 20\%, con la Rasberry pi, se obtuvo una minima mejora, en cambio fue pejudicial con el uso de GPU , pues provoca que la rapidez se reduzca considerablemente.
 \\
+\end{comment}
 
--The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%, with the Rasberry pi, a minimum improvement was obtained, instead it was pejudicioal with the use of GPU, because it causes that the speed is reduced considerably.
+The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%, with the Rasberry pi, a minimum improvement was obtained, instead it was pejudicioal with the use of GPU, because it causes that the speed is reduced considerably.
+\\
+
+\begin{comment}	
+-En el caso de querer implementar el algoritmo en un sitema embedded, no se recomienda trabajar con procesador como el de la Rasp Berry Pi 3, pues tiene  un procesamiento muy lento debido a que los frames por segundo necesario para analizar las imagenes es significativamente bajo, por lo que se debera elegir una targeta que disponga de GPU, sin necesidad del uso de Multithreading y Batching.
+\end{comment}
+
+In the case of wanting to implement the algorithm in an embedded system, it is not recommended to work with a processor like Rasp Berry Pi 3, because it has a very slow processing because the frames per second needed to analyze the images is significantly low, So you should choose a card that has GPU, without the need for Multithreading and Batching.
 \\

### 2017-07-21 PaperBCJ.tex
Cambios20jul
cambios hasta las 22:00pm

--- 2017-07-20 PaperBCJ.tex
@@
 % affiliations
-\author{\IEEEauthorblockN{Andrea Concepci\'on C\'ordova Cruzatty \IEEEauthorrefmark{1},
+\author{\IEEEauthorblockN{Andrea C\'ordova-Cruzatty \IEEEauthorrefmark{1},
 Mauricio Daniel Barreno Barreno \IEEEauthorrefmark{2} and Jos\'e Misael J\'acome Barrionuevo\IEEEauthorrefmark{3}}
@@
 
-Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture.
-In this paper the study of a convolutional neural network is presented, with two classes applied to the classification of plants of maize and weeds in real time, focused to fields of maize in its initial stage.
+Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition.
+The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture.
+This paper presents a study of a convolutional neural network with two classes, applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
 The algorithm has two stages, segmentation of images and classification.
@@
 
+\begin{comment}
 -El uso de Multithreading y Batching a traves de la libreria OpenBLAS es muy beneficioso en el caso de usar CPU, aumentando la rapidez de procesamiento en el porcentaje superior al 20\%, con la Rasberry pi, se obtuvo una minima mejora, en cambio fue pejudicial con el uso de GPU , pues provoca que la rapidez se reduzca considerablemente.
 \\
+\end{comment}
 

### 2017-07-21 PaperBCJ.tex
cambios21jul
cambios 1

@@
 The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture.
-This paper presents a study of a convolutional neural network with two classes, applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
+This paper presents a study of a convolutional neural network with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
 The algorithm has two stages, segmentation of images and classification.
-Segmentation is intended to separate the target plant from the original image.
-While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage.
-The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, (revisar esta linea) we experimented by modifying its number of filters, to analyze their behavior.
+Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes by means of a convolutional neural network previously trained with a dataset generated through the segmentation stage.
+The performance of the network was analyzed and compared with different network architectures.
+The network architecture that presented the best training results was chosen, we experimented by modifying its number of filters, to analyze their behavior.
 Finally, the resulting network was tested on different processors to compare classification times.\\

### 2017-07-21 PaperBCJ.tex

@@
 The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture.
-This paper presents a study of a convolutional neural network with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
+This paper presents a study of a convolutional neural network (CNN) with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
 The algorithm has two stages, segmentation of images and classification.
@@
 The performance of the network was analyzed and compared with different network architectures.
-The network architecture that presented the best training results was chosen, we experimented by modifying its number of filters, to analyze their behavior.
-Finally, the resulting network was tested on different processors to compare classification times.\\
+The network architecture that presented the best training results was chosen and afterwards its number of filters were reduced in order to analyze its behavior.
+Finally, the resulting network was tested on different processors to compare classification speed of each and determine which one could be used for an autonomous system in a real-time application.\\
 
@@
 El rendimiento de la red se ilustra mediante analisis y comparaciones con diferentes arquitecturas de red, luego con la red que presento mejores resultados, se experimeto modificando su numero de filtros, para analizar su comportamiento.
-Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion.
+Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion (verdad?).
 \end {comment}
@@
 
-Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with industrial revolution.
+Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with the new industrial revolution.
 However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
-Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer.
-Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality.
+Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer.
+Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control issues.
 \\
@@
 There are studies that show the impact of weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha.
-Currently, growing development of artificial vision and machine learning algorithms has allowed researchers to propose solutions for weed segmentation in different types of crops (con la finalidad de...).
+Currently, growing development of artificial vision and machine learning algorithms has allowed researchers to propose solutions for weed segmentation in different types of crops.
+These algorithms are intended to be used in different weed control systems, such as autonomous weed-removing robots.
 \\
 
-One of the first approximations to the algorithms of detection of Crops was developed in 1996 \cite{brivot1996segmentation}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops.
-In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{cheng2015feature} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of 98\% in the identification of Weeds in the Rice, Araguez \textit{et.
-al} \cite{equipo2006proceedings} performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document.
+One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared (IR) Images.
+The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop.
+In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process.
+Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of apllications with noise) \cite{cheng2015feature}.
+This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds.
+Araguez \textit{et.
+al} \cite{equipo2006proceedings} performed their segmentation through the  analysis of the green histogram and performing the crop and weed segmentation with unspecified classifiers in their document (revisar si esta bien 2 ultimas oraciones?).
 \\
 
-Hong and Lei \cite{jeon2011robust} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, also there had been developed an algorithm \cite{hlaing2014weed}, that through binarization methods of OTSU and Watershed for the segmentation of the images.
-While its classification was given through an areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed.
+Hong and Lei \cite{jeon2011robust} developed an approximation by using an optimal method for detection in various luminosity settings, they achived this by the use an artificial neural network (ANN) for weed and maize classification with a precision of 92.5\%.
+Also, another algorithm that uses OTSU and Watershed binarization methods for image segmentation has been developed \cite{hlaing2014weed}.
+While classification in this algorithm was done through an area analysis to perform a thresholding and the method is computationally effective when the weed distribution does not resemble the size to the crop plants, its error increases when crop density is higher compared to weeds.
 Romeo \textit{et.
-al} \cite{romeo2012crop} propose to use a fuzzy clustering approach to correctly segment the crop green.
+al} \cite{romeo2012crop} proposed to use a fuzzy clustering approach to correctly segment green within the crop.
 \\
 
-The segmentation of weed and crops is not closed to color images, using a multispectral camera \cite{potena2016fast} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds.
-One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{di2016automatic} achieving a acceptable accuracy for the generation of Datasets.
+Weed and crop segmentation is not limited to color images.
+In another application  \cite{potena2016fast}, the use of a a multispectral camera  permitted to obtain RGB and NIR images for the segmentation and classification purposes.
+The images used a light CNN for the first process and a deep CNN for classification, its accuracy was as high as 98\% in the identification of weeds.
+One of the most difficult things in crop identification is the generation of datasets due to weed presence in the training images, but these can be correctly generated by the use of a CNN \cite{di2016automatic}, achieving an acceptable accuracy for the generation of datasets (verdad?).
 \\
@@
 
-The model development for weed and maize identification algorithm using convolutional neural networks is described below.
+The developed model for weed and maize identification algorithm using convolutional neural networks is described below.
 \\
@@
 The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
-Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better speed processing, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA.
+Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA.
 These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M.
-Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in a independent mobile system that could be implemented in an embedded system.
+Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system.
 The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time.
@@
 
-Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above.
-For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS was used for acquire images and test the classification performace of the CNN.
-(cambiar union de ideas)
+Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with OpenCV.
+The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV.
+Likewise, Pixel OS was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
 \\
@@
 
-Due to the lack of weed and maize plant datasets, it was necessary to search for maize crops in its initial development stage because the taken actions in this stage by the farmer will impact in the future yield of the crop (IDEA COMPLETADA).
+Due to the lack of local weed and maize plants datasets, it was necessary to search for maize crops.
+The initial development stage of maize was selected  because actions taken by the farmer during this stage are easier to execute and these will impact the future crop yield.
 Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples.
@@
 Samples were obtained from images captured in different maize fields.
-Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and to provide reliable samples to the network, which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD).
-Maize Plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
-To record the samples, a camera was centered over the target plant, insuring that the capture shows all features of the maize plant.
+Crops where weed and maize plants could be visually discriminated were chosen in order to easily segment the images and provide reliable samples to the network, which allow the model to correctly learn all features of the real plant.
+Maize plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
+To record the samples, a camera was centered over the target plant, insuring that the captured image showed all its features.
 This was achieved by monitoring the obtained samples through an external display.
@@
 
-Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset. \\
+Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset: maize and weed.
+\\
 \begin{comment}
@@
 al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations.
-In addition, the geometric transformations \cite{sladojevic2016deep} (Si es verdad) allow overfitting reduction and improve precision in the training process.
-For this reason, image rotations each 30 degrees were made, obtaining an increment of the dataset by 12 times, thus increasing the chances of recognizing plants that are in any orientation effectively.
+In addition, geometric transformations \cite{sladojevic2016deep} allow overfitting reduction and improve precision in the training process.
+For this reason, initially obtained images were rotated every 30 degrees, obtaining an increment of the dataset by 12 times, thus increasing the chances of effectively recognizing plants that are in any orientation.
 \\
@@
 One of the characteristics of CNN is that these can have multiple architectures, each architecture can reach different results depending on the application.
-For the present document four CNN architectures have been considered: two models were chosen from the Caffe Zoo Model(it is a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}.
-With the four Nets chosen, each one was trained with the same Solver of type AdaDelta and with the same dataset, the results of training are the following.
+For the present document four CNN architectures have been considered.
+Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet.
+Also, Potena and Nardi used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes\cite{potena2016fast}.
+With the four Nets chosen, each one was trained with the same solver of type AdaDelta and with the same dataset.
+The training results are the following.
 \\
@@
 
-Within parameters shown on table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was considered; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\
+Based on the performance parameters shown on the table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\
 
@@
 
-So, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2 (QUE?
-corregido), then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1 (QUE corregido), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16.
-Finally the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons.
+Thus, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2.
+Then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1, followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16.
+Finally, the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons.
 The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify, the result model is shown in the next graph.\\
@@
 
-In training graph shown below the final result can be appreciated of the net accuracy; 9000 iterations were neccesary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy with few iterations.
+In the training graph shown below, the final net accuracy result can be appreciated; 9000 iterations were necessary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy within few iterations.
 Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters.

### 2017-07-21 PaperBCJ.tex
cambios21julio
cambio 7 am

@@
 
-For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weeds were considered, obtained in different maize crops that the training dataset.
-For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image was obtained with the chosen hardware, we started the classification in Caffe without modifications in Software.
-The results were comparated between cNET with 64 and 16 filters and there are shown in the next Table \ref{table:4}.\\
+For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for the the training dataset.
+In order to have a reliable value for this test its considered to classify ten times the dataset (CLARIFICAR IDEA).
+The average image classification time was obtained with the chosen hardware, the classification started in Caffe without modifications in the software.
+The results were comparated between cNET arquitecture with 64 and 16 filters, these are shown in the next Table \ref{table:4}.\\
 
@@
 
-Like the table shown the best results in times of classification were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so the Raspberry Pi were considered for the analysis of classification performance.
-With cNET of 64 filters the results of time of classification was 615 miliseconds, so it time isn\'t the optimum for our objective that it is the approximation to classification in a real time.\\
+As the table shows, the best results in classification time were achieved by the GPU processor, thus it is the best option to classify a large amount of images.
+However this project is thought to be portable, so the Raspberry Pi was selected for the classification performance analysis.
+Despite the fact that the classification time resul for the cNET of 64 filters was 615 miliseconds, this  time is not optimum for the approximation of real time classification.\\
 
@@
 
-The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document batching was used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software.
-For each hardware, Caffe were recompiled with OpenBLAS instead of Atlas, in the program all images  were entered in a vector to be classified in an only batch per each class, also OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\
+The results shown previously are not definitive because Caffe has ways to optimize image dataset classification.
+In this research project, batching was used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software (ORDENAR IDEA).
+For each hardware, Caffe was recompiled with OpenBLAS instead of Atlas.
+In the program, all images  were entered in a vector to be classified in an only batch per each class.
+Also, OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following.
+\\
 
@@
 
-The results show that for the GPU Classification time it has worsened by 66 \%, mainly because the OpenBLAS Library makes extensive use of the CPU threads causing that not all parameters will be computed by GPU as in the previous test.
-Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores, in the case of the CPU we notice a 22 \% and for 6.3 \% for the Raspberry Pi \\
+The results show that for the GPU classification time has decreased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing that not all parameters will be computed by GPU as in the previous test.
+Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores.
+In the case of the CPU, otice a 22 \% and for 6.3 \% for the Raspberry Pi \\
 

### 2017-07-21 PaperBCJ.tex
cambios21julio
cambios 8:30

@@
 
-For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for the the training dataset.
-In order to have a reliable value for this test its considered to classify ten times the dataset (CLARIFICAR IDEA).
-The average image classification time was obtained with the chosen hardware, the classification started in Caffe without modifications in the software.
-The results were comparated between cNET arquitecture with 64 and 16 filters, these are shown in the next Table \ref{table:4}.\\
+For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for gathering the training dataset images.
+Ten measurements of the mean classification time of the test dataset were obtained for each one of the different hardwares previously selected to run performance tests.
+Classification tests were started with Caffe without any software modifications.
+The obtained results were compared between cNET arquitecture with 64 and 16 filters, these are shown in the next Table \ref{table:4}.\\
 
@@
 As the table shows, the best results in classification time were achieved by the GPU processor, thus it is the best option to classify a large amount of images.
-However this project is thought to be portable, so the Raspberry Pi was selected for the classification performance analysis.
-Despite the fact that the classification time resul for the cNET of 64 filters was 615 miliseconds, this  time is not optimum for the approximation of real time classification.\\
+However, this project is thought to be implemented in an autonomous system so the Raspberry Pi was selected for the classification performance analysis due to its portability.
+The resulting classification time for the cNET of 64 filters was 615 miliseconds, however this  time is not optimum for an approximation of real time classification.\\
 
@@
 The results shown previously are not definitive because Caffe has ways to optimize image dataset classification.
-In this research project, batching was used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software (ORDENAR IDEA).
+Multithreading was applied to this research project with the help of the mathematical software OpenBLAS.
+Also, batching was used to classify each class dataset in a single forward pass.
 For each hardware, Caffe was recompiled with OpenBLAS instead of Atlas.
-In the program, all images  were entered in a vector to be classified in an only batch per each class.
-Also, OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following.
+In the program, all images  were entered in a vector to be classified in an only batch per each class (ACLARAR IDEA).
+Also, OpenBLAS was configured to use the 4 cores of each hardware to obtain even results, the obtained results are the following.
 \\
@@
 
-The results show that for the GPU classification time has decreased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing that not all parameters will be computed by GPU as in the previous test.
-Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores.
-In the case of the CPU, otice a 22 \% and for 6.3 \% for the Raspberry Pi \\
+The results show that for the GPU, classification time has decreased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing that not all parameters will be computed by GPU as in the previous test.
+On the other hand, when the CPU is used the results are better, because the operations are executed using each of the four cores.
+In the case of the CPU, notice a 22 \% and for 6.3 \% for the Raspberry Pi.(REVISAR) \\
 
@@
 \end{comment}	
-Now to compare all these results taking into account that an image captured by the camera at a height of 1.5 m can focus an approximate 6 plants of maize, and according to the amount of weed, an average of 12 plants, Giving a total of about 18 plants.
-This analyzes how many frames per second would be appropriate for the acquisition of images.
+Lastly, an image captured by the camera at a height of 1.5 m can focus an approximate 6 plants of maize.
+Taking into account the number of weeds, an average of 12 plants can show up in the image.
+The total number of plants per image would round 18 plants considering maize and weeds as well.
+This aids to determine how many frames per second would be appropriate for the acquisition of images.
 \begin{table}[h!]
@@
 
-In this paper  we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 97.23 \% of accuracy of training, using a dataset of both classes of 44580 segmented images.
+In this paper presented an analysis of a Convolutional Neuronal Networks application for classification between maize plants and weeds.
+With this purpose, several CNN Architectures were tested, the network that presented the best results in precision (de que?) was cNET, with a 97.23 \% of accuracy of training, using a dataset of both classes of 44580 segmented images.
 \\
@@
 
-In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuracy of the net, it value increased 1 \% in comparation with the original net.
+In order to have adequate image processing that could be implemented to work in real time, the number of the network filter layers was reduced from 64 to 16, achieving to reduce the number of parameters to be computed during the classification.
+A classification time reduced by 2.5 times compared the original Net of 64 filters was obtained.
+This change had a small impact in the training accuracy of the net, its value increased 1 \% in comparison to the original net.
 \\
@@
 
-Also, by using different methods to classify the images in our experiments, the results showed that the best time of classification was achieved by using a Nvidia Graphic Cards, this is due the Parallel Architecture that this GPU has and also it has fully support for the computation platform CUDA, it demostrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3.
+Also, by using different methods to classify the images in our experiments, the results showed that the best time of classification was achieved by using a Nvidia Graphic Cards, this was due to the parallel architecture that this GPU has.
+Also, it(que cosa?) was fully supported for the computational platform CUDA, it demonstrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3.
 \\
@@
 
-The study demostrated that is better to perform some geometrical tranformations to the Dataset images due it benefits to improve the classification of plants because the plants ever have different orientations in the crop field.
+The study demonstrated that is better to perform some geometrical transformations to the dataset images due to the benefits it offers, such as the improvement in  plant classification since the plants will have different orientations in the crop field.
 \\
@@
 
--The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%, with the Rasberry pi, a minimum improvement was obtained, instead it was pejudicioal with the use of GPU, because it causes that the speed is reduced considerably.
+-The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%.
+However with the Rasberry pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably.
 \\
@@
 
-The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to conform the dataset of this project.
+The authors would like to thank the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and the owners of corn crops of the city whom allowed us to take samples of plants, to conform the dataset of this project.
 \\

### 2017-07-21 PaperBCJ.tex
cambios21julio
cambios de 11:00

@@
 % affiliations
-\author{\IEEEauthorblockN{Andrea C\'ordova-Cruzatty \IEEEauthorrefmark{1},
-Mauricio Daniel Barreno Barreno \IEEEauthorrefmark{2} and Jos\'e Misael J\'acome Barrionuevo\IEEEauthorrefmark{3}}
+\author{\IEEEauthorblockN{C\'ordova-Cruzatty Andrea \IEEEauthorrefmark{1},
+Barreno Barreno Mauricio Daniel \IEEEauthorrefmark{2} and J\'acome Barrionuevo Jos\'e Misael \IEEEauthorrefmark{3}}
 \IEEEauthorblockA{Department of Energy and Mechanics,
@@
 The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture.
-This paper presents a study of a convolutional neural network (CNN) with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
-The algorithm has two stages, segmentation of images and classification.
-Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes by means of a convolutional neural network previously trained with a dataset generated through the segmentation stage.
+This paper presents the development of an algorithm that has two stages; one for image segmentation and another for classification.
+Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes defined.
+The study uses a convolutional neural network (CNN) with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
+This network has been trained with a dataset generated through the segmentation stage.
 The performance of the network was analyzed and compared with different network architectures.
@@
 Nowadays, one of agriculture's challenges is the development of precision agriculture techniques focused on weed and crop segmentation.
-There are studies that show the impact of weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha.
+There are studies that show the impact of weed in corn crops \cite{suarez2005distintos}; yield can be affected up to 5000 kg/ha.
 Currently, growing development of artificial vision and machine learning algorithms has allowed researchers to propose solutions for weed segmentation in different types of crops.
@@
 In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process.
-Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of apllications with noise) \cite{cheng2015feature}.
+Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}.
 This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds.
 Araguez \textit{et.
-al} \cite{equipo2006proceedings} performed their segmentation through the  analysis of the green histogram and performing the crop and weed segmentation with unspecified classifiers in their document (revisar si esta bien 2 ultimas oraciones?).
+al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers in their document.
 \\
 
-Hong and Lei \cite{jeon2011robust} developed an approximation by using an optimal method for detection in various luminosity settings, they achived this by the use an artificial neural network (ANN) for weed and maize classification with a precision of 92.5\%.
+Hong and Lei \cite{jeon2011robust} developed an approximation by using an optimal method for detection in various luminosity settings, they achived this by the use of an artificial neural network (ANN) for weed and maize classification with a precision of 92.5\%.
 Also, another algorithm that uses OTSU and Watershed binarization methods for image segmentation has been developed \cite{hlaing2014weed}.
-While classification in this algorithm was done through an area analysis to perform a thresholding and the method is computationally effective when the weed distribution does not resemble the size to the crop plants, its error increases when crop density is higher compared to weeds.
+While classification in this algorithm was done through an area analysis to perform a thresholding and the method is computationally efficient when the weed distribution does not resemble the size of the crop plants, its error increases when crop density is higher compared to weeds.
 Romeo \textit{et.
@@
 The images used a light CNN for the first process and a deep CNN for classification, its accuracy was as high as 98\% in the identification of weeds.
-One of the most difficult things in crop identification is the generation of datasets due to weed presence in the training images, but these can be correctly generated by the use of a CNN \cite{di2016automatic}, achieving an acceptable accuracy for the generation of datasets (verdad?).
+One of the most difficult things in crop identification is the generation of datasets due to weed presence in the training images, but these can be correctly generated by the use of a CNN \cite{di2016automatic}, achieving an acceptable accuracy for the generation of datasets.
 \\
@@
 
-The use of powerful libraries of image processing and deep learning development was required due to..(ver espanol)..
-.
+The use of powerful libraries of image processing and deep learning development was required because the images had to be processed with artificial vision algorithms and classified with a selected convolutional neural network architecture.
 The use of open software was required in order to provide the system with a certain level of flexibility to extend its use for future prototypes.
-Thus, OpenCV library was chosen due to its computational efficiency and focus on real-time applications \cite{opencv_library}; it was used specificaly for sample images acquisition and segmentation.
+Thus, OpenCV library was chosen due to its computational efficiency and focus on real-time applications \cite{opencv_library}; it was used specifically for sample images acquisition and segmentation.
 Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other deep lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for learning of applications such as simple regression, speech, robotics, large-scale visual classification, etc.
@@
 \begin{comment}
-Debido a la falta de datasets de plantas de Maize y Mala Hierba, Fue necesario buscar los cultivos de maíz en su etapa de desarrollo inicial porque las acciones tomadas en esta etapa por el agricultor tendrán un impacto en el rendimiento futuro del cultivo, para ese proposito nos hemos traslatado a Pillaro, esta ciudad es localizada en la Provincia de Tungurahua, en el Centro de la Sierra Ecuatoriana.
+Debido a la falta de datasets de plantas de Maize y Mala Hierba, Fue necesario buscar los cultivos de maíz en su etapa de desarrollo inicial porque las acciones tomadas en esta etapa por el agricultor tendrán un impacto en el rendimiento futuro del cultivo, para ese proposito nos hemos traslatado a , esta ciudad es localizada en la Provincia de Tungurahua, en el Centro de la Sierra Ecuatoriana.
 Pillaro es un productor reconocido de cultivos andinos como: Maiz, Papas y frutas, por lo que podemos encontrar aqui muchos cultivos de maiz que sean utiles para nuestro proposito
-\begin{comment}
+\end{comment}
 
@@
 Unas muestras de las imagenes capturadas son mostradas a continuacion:
-\begin{comment}
+\end{comment}
 
@@
 Examples of the images captured are shown below.
+\\
 
@@
 
-Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset: maize and weed.
+Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset: maize and weeds.
 \\
@@
 In addition, geometric transformations \cite{sladojevic2016deep} allow overfitting reduction and improve precision in the training process.
-For this reason, initially obtained images were rotated every 30 degrees, obtaining an increment of the dataset by 12 times, thus increasing the chances of effectively recognizing plants that are in any orientation.
+For this reason, the obtained images were rotated every 30 degrees, obtaining an increment of the dataset by 12 times, thus increasing the chances of effectively recognizing plants that are in any orientation.
 \\
@@
 
-For the Validation Phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the distribution of the dataset.
+For the Validation Phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the distribution of the dataset.\\
 
@@
 For the present document four CNN architectures have been considered.
-Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet.
-Also, Potena and Nardi used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes\cite{potena2016fast}.
+Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers): LeNet and AlexNet.
+Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes.
 With the four Nets chosen, each one was trained with the same solver of type AdaDelta and with the same dataset.
-The training results are the following.
+The training results are shown on table \ref{table:2}.
 \\
@@
 Although results given by this type of network are excellent, one of the main purposes of this paper was the implementation of this system in real time.
-The number of parameters to be computed by the selected network were numerous, so network modifications in order to improve processing time had to be made.
+The number of parameters to be computed by the selected network were numerous, so it is necessary to make network modifications in order to improve its processing speed.
 To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16.\\
@@
 Finally, the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons.
-The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify, the result model is shown in the next graph.\\
+The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify.
+The resulting model is shown in graph \ref{fig_sim}.
+\\
 
@@
 Ten measurements of the mean classification time of the test dataset were obtained for each one of the different hardwares previously selected to run performance tests.
-Classification tests were started with Caffe without any software modifications.
-The obtained results were compared between cNET arquitecture with 64 and 16 filters, these are shown in the next Table \ref{table:4}.\\
+Classification tests were started with Caffe in vanilla version.
+The obtained results were compared between cNET arquitecture with 64 and 16 filters, these are shown on  Table \ref{table:4}.\\
 
@@
 For each hardware, Caffe was recompiled with OpenBLAS instead of Atlas.
-In the program, all images  were entered in a vector to be classified in an only batch per each class (ACLARAR IDEA).
-Also, OpenBLAS was configured to use the 4 cores of each hardware to obtain even results, the obtained results are the following.
+In the program, all images  were entered in a vector to be classified in an only batch per each class.
+Also, OpenBLAS was configured to use the 4 cores of each CPU hardware to obtain even results among these two devices.
+Since GPU has thousands of cores, this test could not be configured under the same restriction for this device.
+The obtained results are the following.
 \\
@@
 
-The results show that for the GPU, classification time has decreased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing that not all parameters will be computed by GPU as in the previous test.
-On the other hand, when the CPU is used the results are better, because the operations are executed using each of the four cores.
-In the case of the CPU, notice a 22 \% and for 6.3 \% for the Raspberry Pi.(REVISAR) \\
+The results show that for the GPU, classification time has increased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, 
+causing some parameters to be computed in the CPU in stead of the GPU, thus making the process slower.
+For the CPU the results are better because the operations are executed using each of the four cores, for this case a decrease in time of 22\% was obtained.
+Finally, the result for the Raspberry Pi CPU was a time decrease of 6.3 \%.\\
 
@@
 The total number of plants per image would round 18 plants considering maize and weeds as well.
-This aids to determine how many frames per second would be appropriate for the acquisition of images.
+This aids to determine how many frames per second would be appropriate for the acquisition of images.\\
+
+For the estimation of the frames per second for each device, its optimal configuration was considered.
+The GPU classification time during the test without multithreading was considered for this device.
+For the CPU and the Raspberry Pi CPU, the results for classification time in the multithreading tests were considered.
+The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate.\\
+
 \begin{table}[h!]
@@
 \begin{comment}	
--Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 97.26\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases.
-\\
+Para buscar un procesamiento apropiado para trabajar en tiempo real, se experimento reduciendo el numero de filros de las capas de la red desde 64 hasta 16, logrando con esto disminuir el numero de parametros a ser computados durante la clasificacion, obteniendo tambien un tiempo de procesamiento de 2,5 veces menor al de la red original, este cambio tuvo un bajo impacto en la precision de entrenamiento de la red, pues este valor cayo en un 1\%, con respecto a la red original.
 \end{comment}
-
-In this paper presented an analysis of a Convolutional Neuronal Networks application for classification between maize plants and weeds.
-With this purpose, several CNN Architectures were tested, the network that presented the best results in precision (de que?) was cNET, with a 97.23 \% of accuracy of training, using a dataset of both classes of 44580 segmented images.
-\\
-
-\begin{comment}	
-Para buscar un procesamiento apropiado para trabajar en tiempo real, se experimento reduciendo el numero de filros de las capas de la red desde 64 hasta 16, logrando con esto disminuir el numero de parametros a ser computados durante la clasificacion, obteniendo tambien un tiempo de procesamiento de 2,5 veces menor al de la red original, este cambio tuvo un bajo impacto en la precision de entrenamiento de la red, pues este valor cayo en un 1\%, con respecto a la red original.
-\begin{end}
 
@@
 \begin{comment}	
+-Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 97.26\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases.
+\\
+\end{comment}
+
+This paper presented an analysis of a Convolutional Neuronal Networks application for classification between maize plants and weeds.
+With this purpose, several CNN Architectures were tested, the network that presented the best results was cNET of 16 filters, with a 97.23 \% of training accuracy, using a dataset of both classes of 44580 segmented images.
+\\
+
+\begin{comment}	
 -Ademas nuestros experimentos al utilizar diferentes procesadores, demostraron que se obtienen mejores resultados en cuanto a velocidad al trabajar con una a tarjeta grafica ENVIDIA que posee soporte CUDA debido a su arquitectura de computacion paralela, siendo este 10 veces mas rapido que el CPU normal y 100 veces mas rapido que una RaspBerry Pi3.
@@
 
-Also, by using different methods to classify the images in our experiments, the results showed that the best time of classification was achieved by using a Nvidia Graphic Cards, this was due to the parallel architecture that this GPU has.
-Also, it(que cosa?) was fully supported for the computational platform CUDA, it demonstrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3.
+Also, by using different methods to classify the images in our experiments the results showed that the best time of classification was achieved by using a Nvidia Graphics Card.
+This was due to the parallel architecture that this GPU has.
+Also, this Graphics Card is fully supported for the computational platform CUDA, it demonstrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3.
 \\
@@
 
--The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%.
+The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%.
 However with the Rasberry pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably.

### 2017-07-21 PaperBCJ.tex
Merge remote-tracking branch 'origin/master'
# Conflicts:
#	PaperBCJ.pdf
#	PaperBCJ.tex

@@
 	\caption{Crops chosen to obtain samples, notice that it is easy to discrimante weed from maize}
-	\label{fig_sim}
+	\label{figure1}
 	\end{figure}
@@
 	\caption{Preprocessing to obtain samples for the dataset}
-	\label{fig_sim}
+	\label{figure2}
 	\end{figure}
@@
 	\caption{ Segmented and Masked images of dataset Above: Weed, Below: Maize}
-	\label{fig_sim}
+	\label{figure3}
 	\end{figure}
@@
 Aunque lo resultados dados de la red fueron excelentes, uno de los propositos principales de este documento es una aproximacion de procesamiento en tiempo real, entonces el numero de parametros a ser computados va a ser un problema, entonces consideramos modificar la red para mejorar el tiempo de procesamiento.
-Para lograr esto, fue necesario reducir el numero de filtros de cNET de 64 a 16, en la tabla siguiente se muestran los resultados del entrenamiento para los dos tipos de red.
+Para lograr esto, fue necesario reducir el numero de filtros de cNET de 64 a 16.
+se selecciono este valor debido a que es el m[inimo valor para que el entregamiento de la red siga manteniendo su precision.
 \end{comment}
@@
 The number of parameters to be computed by the selected network were numerous, so it is necessary to make network modifications in order to improve its processing speed.
-To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16.\\
+To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16.
+This final number of filters used in the network was selected because this is the minimum number of filters that allow to maintain training accuracy.
+\\
 
@@
 The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify.
-The resulting model is shown in graph \ref{fig_sim}.
+The resulting model is shown in graph \ref{figure4}.
 \\
@@
 	\caption{ The schematic of cNET }
-	\label{fig_sim}
+	\label{figure4}
 	\end{figure}
@@
 	\caption{ Graph of the Training Process }
-	\label{fig_sim}
+	\label{figure5}
 	\end{figure}

### 2017-07-21 PaperBCJ.tex
nueva conclusion
nueva conclusion

@@
  \hline 
- Time(s) & 0.0171 & 0.196 & 7.714  \\ [0.95ex]
+ Time(s) & 0.0171 & 0.196 & 2.714  \\ [0.95ex]
  \hline
@@
 
+\begin{comment}	
+En el caso de querer implementar el algoritmo en un sitema embedded, no se recomienda trabajar con procesador como el de la Rasp Berry Pi 3, pues tiene  un procesamiento muy lento debido a que los frames por segundo necesario para analizar las imagenes es significativamente bajo, por lo que se debera elegir una targeta que disponga de GPU, sin necesidad del uso de Multithreading y Batching.
+\end{comment}
+
+In the case of wanting to implement the algorithm in an embedded system, it is not recommended to work with a processor like Rasp Berry Pi 3, because it has a very slow processing because the frames per second needed to analyze the images is significantly low, So you should choose a card that has GPU, without the need for Multithreading and Batching.
+\\
+
 % conference papers do not normally have an appendix

### 2017-07-21 PaperBCJ.tex
Nuevos Cambios
Nuevos cambios

@@
 
+\begin{IEEEkeywords}
+Machine Learning, Convolutional Neural Networks, GPU Computation, Caffe, Segmentation of plants, Classification of maize. 
+\end{IEEEkeywords}
+
 % no keywords
@@
 \\
-
 \section{Matherials and Methods}
@@
 \end{comment}
-
 The developed model for weed and maize identification algorithm using convolutional neural networks is described below.
-\\
 \subsection{Hardware}
@@
 This was achieved by monitoring the obtained samples through an external display.
-Examples of the images captured are shown below.
+Examples of the images captured are shown on the figure \ref{figure1}.
 \\
@@
 It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated.
-In the following image, final results of the processed images that conform the dataset are shown.\\
+In the following image, final results of the processed images that conform the dataset are shown on the figure \ref{figure3}.\\
 
@@
 
-For the Validation Phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the distribution of the dataset.\\
+For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the distribution of the dataset.\\
 
@@
  \hline
- Maize & 25695 & 8325 & 200 & 34220 \\ 
- Weed & 8560 & 2000 & 200 & 10760\\ 
+ Maize & 25695 & 8325 & 202 & 34222 \\ 
+ Weed & 8560 & 2000 & 202 & 10762\\ 
  \hline
@@
 Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes.
-With the four Nets chosen, each one was trained with the same solver of type AdaDelta and with the same dataset.
+With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset.
 The training results are shown on table \ref{table:2}.
@@
 The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify.
-The resulting model is shown in graph \ref{figure4}.
+The resulting model is shown in figure \ref{figure4}.
 \\
@@
  \hline
- 16 Filters & 94.55\% & 87.13\% & 951 $\mu$s \\ [0.75ex]
+ 16 Filters & 92.08\% & 89.11\% & 951 $\mu$s \\ [0.75ex]
  \hline
@@
  \hline
- 16 Filters & 94.55\% & 87.13\% & 17.23 ms \\ [0.75ex]
+ 16 Filters & 92.08\% & 89.11\% & 17.23 ms \\ [0.75ex]
  \hline
@@
  \hline
- 16 Filters & 94.55\% & 87.13\% & 161 ms \\ [0.75ex]
+ 16 Filters & 92.08\% & 89.11\% & 161 ms \\ [0.75ex]
  \hline
@@
 However, this project is thought to be implemented in an autonomous system so the Raspberry Pi was selected for the classification performance analysis due to its portability.
-The resulting classification time for the cNET of 64 filters was 615 miliseconds, however this  time is not optimum for an approximation of real time classification.\\
+The resulting classification time for the cNET of 16 filters was 161 miliseconds, however this time is not optimum for an approximation of real time classification.\\
 
@@
 For each hardware, Caffe was recompiled with OpenBLAS instead of Atlas.
-In the program, all images  were entered in a vector to be classified in an only batch per each class.
+In the program with cNET of 16 filters, all images were entered in a vector to be classified in an only batch per each class.
 Also, OpenBLAS was configured to use the 4 cores of each CPU hardware to obtain even results among these two devices.
@@
  \hline 
- GPU & 89.11\% & 92.08\% & 1.58 ms \\ [0.95ex]
+ GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
  \hline
- CPU & 89.11\% & 92.08\% & 10.92 ms \\ [0.95ex]
+ CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
  \hline
- CPU(Raspberry Pi) & 89.11\% & 92.08\% & 150.8 ms \\ [0.95ex]
+ CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]
  \hline

### 2017-07-22 PaperBCJ.tex
cambios21dejulio
cambios despues de revision

@@
 \IEEEauthorblockA{Department of Energy and Mechanics,
-University of the Army ESPE\\
+University of the Armed Forces ESPE\\
 Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
@@
 
-Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition.
+Deep Learning is playing an important role in big data processing for more accurate modeling of common productive processes.
+It is being widely used in artificial vision applications and specifically in pattern recognition.
 The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture.
-This paper presents the development of an algorithm that has two stages; one for image segmentation and another for classification.
-Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes defined.
-The study uses a convolutional neural network (CNN) with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages.
-This network has been trained with a dataset generated through the segmentation stage.
-The performance of the network was analyzed and compared with different network architectures.
-The network architecture that presented the best training results was chosen and afterwards its number of filters were reduced in order to analyze its behavior.
-Finally, the resulting network was tested on different processors to compare classification speed of each and determine which one could be used for an autonomous system in a real-time application.\\
+This paper presents the development of an algorithm capable of image segmentation and classification.
+Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two defined classes.
+It applies a convolutional neural network (CNN) to discriminate maize plants from weeds in real time, at early crop development stages.
+It was applied to maize crop because it is a common staple crop in the Ecuadorian Highlands.
+The convolutional neural network has been trained with a dataset generated in the segmentation stage.
+The performance of the network was analyzed with LeNET, AlexNet, cNET and sNET network architectures.
+The network architecture that presented the best training results was cNET based on its performance in terms of accuracy (96.4\%) and processing time of 161 miliseconds in a Raspberry Pi CPU.
+The minimum working filter number for this network architecture was 16.The best performing algorithms and processors have a significant potential for autonomous weed and crop classification systems in a real-time application.\\
 
@@
 During the last centuries, significant progress has taken place in science and technology developments.
-Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems in a different manner.
-\\
-
+Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors, providing new means to approach problems in a different manner.
 The availability of leading edge technologies has considerably increased, thus becoming more accessible to people.
@@
 However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
-Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer.
-Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control issues.
+Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer.
+Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects.
 \\
@@
 Araguez \textit{et.
-al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers in their document.
+al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers.
 \\
@@
 
-For the training and image-capturing stages, the following elements were used: a Raspberry Pi 3 with a V2.1 Pi camera for image acquisition.
+A Raspberry Pi 3 with a V2.1 Pi camera for image acquisition was used for the training and image-capturing stages.
 The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images.
@@
 Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples.
-P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits.
+P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as maize, potatoes and a wide variety of fruits.
 Due to its year-long production season, many maize crops at its initial development stage were found in this area.
@@
 
-Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset: maize and weeds.
-\\
+Also, it was necessary to obtain images of the most common weed plants found in maize crops in P\'illaro, in order to allow the network to discriminate between maize and weeds. \\
 \begin{comment}
@@
 For the present document four CNN architectures have been considered.
-Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers): LeNet and AlexNet.
+Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet.
 Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes.
@@
 Although results given by this type of network are excellent, one of the main purposes of this paper was the implementation of this system in real time.
-The number of parameters to be computed by the selected network were numerous, so it is necessary to make network modifications in order to improve its processing speed.
+The number of parameters to be computed by the selected network were numerous, so it was necessary to make network modifications in order to improve its processing speed.
 To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16.
-This final number of filters used in the network was selected because this is the minimum number of filters that allow to maintain training accuracy.
+This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy.
 \\
@@
 
-Thus, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2.
+Thus, the complete network model was conformed by an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2.
 Then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1, followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16.

### 2017-08-16 PaperBCJ.tex
correction 1

@@
 % Do not put math or special symbols in the title.
-\title{Precise Weed and Maize classification through Convolutional Neuronal Networks }
+\title{Precise Weed and Maize Classification through Convolutional Neuronal Networks }
 
@@
 The network architecture that presented the best training results was cNET based on its performance in terms of accuracy (96.4\%) and processing time of 161 miliseconds in a Raspberry Pi CPU.
-The minimum working filter number for this network architecture was 16.The best performing algorithms and processors have a significant potential for autonomous weed and crop classification systems in a real-time application.\\
+The minimum working filter number for this network architecture was 16.
+The best performing algorithms and processors have a significant potential for autonomous weed and crop classification systems in a real-time application.\\
 
@@
 Crops where weed and maize plants could be visually discriminated were chosen in order to easily segment the images and provide reliable samples to the network, which allow the model to correctly learn all features of the real plant.
-Maize plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
+Maize plants at a V3 to V7 development stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples.
 To record the samples, a camera was centered over the target plant, insuring that the captured image showed all its features.
 This was achieved by monitoring the obtained samples through an external display.
-Examples of the images captured are shown on the figure \ref{figure1}.
+Examples of the images captured are shown on the Fig.
+\ref{figure1}.
 \\
@@
 	\includegraphics[width=3.2in]{entradamaiz}
-	\caption{Crops chosen to obtain samples, notice that it is easy to discrimante weed from maize}
+	\caption{Crops chosen to obtain samples, it is easy to discrimante weed from maize}
 	\label{figure1}
@@
 Afterwards, the images were segmented in order to differentiate them from the soil and other non-plant elements.
-Original images were masked with the binary mask to provide the dataset with color features of maize and weed plants.
+Original images were masked to provide the dataset with color features of maize and weed plants.
 Once the segmented images were obtained, the files that had a resolution lower than 64x64 pixels were removed because its size was smaller than the size of the network input layer.
@@
 Following, the images were saved in a png format.
-The entire process described before is illustrated in the next figure.
+The entire process described before is illustrated in Fig.
+\ref{figure2}.
 \\
@@
 
-For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the distribution of the dataset.\\
+For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the dataset distribution.\\
 
 \begin{table}[h!]
+\renewcommand{\arraystretch}{1.3}
+\caption{DATASET DISTRIBUTION OF EACH CLASS}
+\label{table:1}
 \centering
@@
 \end{tabular}
-\caption{Distribution of the Dataset of each class}
-\label{table:1}
+
 \end{table}
@@
 	After the dataset was completed, it was neccesary to classify maize and weed images.
-Convolutional Neural Networks (CNN) can be used as a highly-accurate method for image classification, these models are complex but efficient with a high rate of discrimination and have proven to provide good results in image classification, object detection, and fine-grained classification \cite{sharif2014cnn}.
+Convolutional Neural Networks (CNN) can be used as a highly-accurate method for image classification.
+These models are complex but efficient with a high rate of discrimination and have proven to provide good results in image classification, object detection, and fine-grained classification \cite{sharif2014cnn}.
 CNN are widely used in precision agriculture \cite{potena2016fast} for the correct identification of plants.\\
@@
 
-One of the characteristics of CNN is that these can have multiple architectures, each architecture can reach different results depending on the application.
+One of the characteristics of CNN is these have multiple architectures, each architecture can reach different results depending on the application.
 For the present document four CNN architectures have been considered.
@@
 
-Although results given by this type of network are excellent, one of the main purposes of this paper was the implementation of this system in real time.
+Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of a real time system.
 The number of parameters to be computed by the selected network were numerous, so it was necessary to make network modifications in order to improve its processing speed.
@@
 Finally, the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons.
-The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify.
-The resulting model is shown in figure \ref{figure4}.
+The type of fully-connected layers contain a total of 478 neurons, where the last two neurons are the output representing the two classes to identify.
+The resulting model is shown in Fig.
+\ref{figure4}.
 \\
@@
  \hline
- \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{RaspBerry Pi 3 with Threading} \\ 
+ \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{Raspberry Pi 3 with Threading} \\ 
  \hline 
@@
 \begin{comment}	
--Ademas nuestros experimentos al utilizar diferentes procesadores, demostraron que se obtienen mejores resultados en cuanto a velocidad al trabajar con una a tarjeta grafica ENVIDIA que posee soporte CUDA debido a su arquitectura de computacion paralela, siendo este 10 veces mas rapido que el CPU normal y 100 veces mas rapido que una RaspBerry Pi3.
+-Ademas nuestros experimentos al utilizar diferentes procesadores, demostraron que se obtienen mejores resultados en cuanto a velocidad al trabajar con una a tarjeta grafica ENVIDIA que posee soporte CUDA debido a su arquitectura de computacion paralela, siendo este 10 veces mas rapido que el CPU normal y 100 veces mas rapido que una Raspberry Pi3.
 \end{comment}
@@
 
-In the case of wanting to implement the algorithm in an embedded system, it is not recommended to work with a processor like Rasp Berry Pi 3, because it has a very slow processing because the frames per second needed to analyze the images is significantly low, So you should choose a card that has GPU, without the need for Multithreading and Batching.
+In the case of implementing the algorithm in an embedded system, it is not recommended to work with a processor like Raspberry Pi 3, because it has a very slow processing because the frames per second needed to analyze the images is significantly low, So you should choose a card that has GPU, without the need for Multithreading and Batching.
 \\

### 2017-08-17 PaperBCJ.tex
Corrections of Review 2

@@
 The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV.
-Likewise, Pixel OS was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
+Likewise, PIXEL Distribution derived from Debian Linux was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
 \\
@@
 
-Due to the lack of local weed and maize plants datasets, it was necessary to search for maize crops.
+Due to the lack of local weed and maize plants datasets, it was necessary to search for those classes of plants in maize crops.
 The initial development stage of maize was selected because actions taken by the farmer during this stage are easier to execute and these will impact the future crop yield.
@@
 \begin{comment}	
-En el caso de querer implementar el algoritmo en un sitema embedded, no se recomienda trabajar con procesador como el de la Rasp Berry Pi 3, pues tiene un procesamiento muy lento debido a que los frames por segundo necesario para analizar las imagenes es significativamente bajo, por lo que se debera elegir una targeta que disponga de GPU, sin necesidad del uso de Multithreading y Batching.
+En el caso de querer implementar el algoritmo en un sitema embedded, no se recomienda trabajar con procesador como el de la Raspberry Pi 3, pues tiene un procesamiento muy lento debido a que los frames por segundo necesario para analizar las imagenes es significativamente bajo, por lo que se debera elegir una targeta que disponga de GPU, sin necesidad del uso de Multithreading y Batching.
 \end{comment}

### 2017-08-17 PaperBCJ.tex
Corrections of Tables

@@
 \usepackage{filecontents}
-\usepackage{caption}
-\usepackage[noadjust]{cite}
-\captionsetup[table]{position=bottom} %% or below
+%\usepackage[noadjust]{cite}
 
@@
 
+\IEEEoverridecommandlockouts
+\IEEEpubid{\makebox[\columnwidth]{\textbf{978-1-5386-3894-1/17/\$31.00~\copyright{}2017 IEEE} \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+
 % make the title area
@@
 Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system.
-The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time.
+The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on \textbf{(revisar)} analyze if the hardware can process information in real time.
 \\
@@
 
-Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with OpenCV.
+Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with the software chosen.
 The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV.
@@
 
-	\begin{figure}[h]
+	\begin{figure}[h!]
 	\centering
@@
 	\end{figure}
+
 \begin{comment}
@@
 Also, it was necessary to obtain images of the most common weed plants found in maize crops in P\'illaro, in order to allow the network to discriminate between maize and weeds. \\
+
 \begin{comment}
@@
 \end{equation}
+
 \begin{comment}
@@
 \ref{figure2}.
-\\
 
@@
 It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated.
-In the following image, final results of the processed images that conform the dataset are shown on the figure \ref{figure3}.\\
+In the following image, final results of the processed images that conform the dataset are shown on the Fig.
+\ref{figure3}.\\
 
@@
 	\includegraphics[width=2.5in]{im1}
-	\caption{ Segmented and Masked images of dataset Above: Weed, Below: Maize}
+	\caption{Segmented and Masked images of dataset Above: Weed, Below: Maize}
 	\label{figure3}
@@
 
-For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the dataset distribution.\\
+For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following Table \ref{table:1} with the dataset distribution.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{DATASET DISTRIBUTION OF EACH CLASS}
+\caption{Dataset distribution of each class}
 \label{table:1}
@@
 \end{tabular}
-
 \end{table}
@@
 With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset.
-The training results are shown on table \ref{table:2}.
+The training results are shown on Table \ref{table:2}.
 \\
@@
 \centering
+\renewcommand{\arraystretch}{1.2}
+\caption{Comparison of the 4 types of CNN}
+\label{table:2}
 \begin{tabular}{|l c c c c|} 
@@
 \end{tabular}
-\caption{Comparison of the 4 types of CNN}
-\label{table:2}
 \end{table}
@@
 This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy.
-\\
-
-\begin{table}[h!]
+The results of the experiment are shown in the Table \ref{table:3} \\
+
+\begin{table}[h]
 \centering
+\renewcommand{\arraystretch}{1.2}
+\caption{Comparison between cNET of 16 and 64 filters}
+\label{table:3}
 \begin{tabular}{|l c c |} 
@@
 \end{tabular}
-\caption{Comparison between cNET of 16 and 64 filters}
-\label{table:3}
 \end{table}
@@
 
-In the training graph shown below, the final net accuracy result can be appreciated; 9000 iterations were necessary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy within few iterations.
+In the training graph shown in Fig.
+\ref{figure5}, the final net accuracy result can be appreciated; 9000 iterations were necessary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy within few iterations.
 Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters.
@@
 
-For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for gathering the training dataset images.
+For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for \textbf{mejorar} gathering the training dataset images.
 Ten measurements of the mean classification time of the test dataset were obtained for each one of the different hardwares previously selected to run performance tests.
@@
 
-\begin{table}[h!]
+\begin{table}[h]
 \centering
-\begin{tabular}{|p{1.1cm}|p{1.5cm}|p{1.5cm}|p{2.1cm}|} 
- \hline
- \multicolumn{4}{ |c| }{\textbf{GPU}} \\
- \hline
- \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
- \hline 
- 64 Filters & 95.05\% & 74.75\% & 2.34 ms \\ [0.75ex]
- \hline
- 16 Filters & 92.08\% & 89.11\% & 951 $\mu$s \\ [0.75ex]
- \hline
- \multicolumn{4}{ |c| }{\textbf{CPU}} \\
- \hline
- \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
- \hline 
- 64 Filters & 95.05\% & 74.75\% & 51.6 ms \\ [0.75ex]
- \hline
- 16 Filters & 92.08\% & 89.11\% & 17.23 ms \\ [0.75ex]
- \hline
- \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
- \hline
- \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\
- \hline 
- 64 Filters & 95.05 \% & 74.75\% & 615 ms \\ [0.75ex]
- \hline
- 16 Filters & 92.08\% & 89.11\% & 161 ms \\ [0.75ex]
- \hline
-\end{tabular}
+\renewcommand{\arraystretch}{1.2}
 \caption{Test with the three types of Hardware}
 \label{table:4}
+\begin{tabular}{|p{1.1cm}|p{1.5cm}|p{1.5cm}|p{2.1cm}|} 
+ \hline
+ \multicolumn{4}{ |c| }{\textbf{GPU}} \\
+ \hline
+ \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
+ \hline 
+ 64 Filters & 95.05\% & 74.75\% & 2.34 ms \\ [0.75ex]
+ \hline
+ 16 Filters & 92.08\% & 89.11\% & 951 $\mu$s \\ [0.75ex]
+ \hline
+ \multicolumn{4}{ |c| }{\textbf{CPU}} \\
+ \hline
+ \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
+ \hline 
+ 64 Filters & 95.05\% & 74.75\% & 51.6 ms \\ [0.75ex]
+ \hline
+ 16 Filters & 92.08\% & 89.11\% & 17.23 ms \\ [0.75ex]
+ \hline
+ \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
+ \hline
+ \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\
+ \hline 
+ 64 Filters & 95.05 \% & 74.75\% & 615 ms \\ [0.75ex]
+ \hline
+ 16 Filters & 92.08\% & 89.11\% & 161 ms \\ [0.75ex]
+ \hline
+\end{tabular}
 \end{table}
@@
 Since GPU has thousands of cores, this test could not be configured under the same restriction for this device.
-The obtained results are the following.
-\\
+The obtained results are the shown in Table \ref{table:5}.
 
@@
 \centering
-\begin{tabular}[c c c c]{|p{2.2 cm}|p{1.1cm}|p{1.1cm}|p{2.4cm}|} 
- \hline
- \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
- \hline 
- GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
- \hline
- CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
- \hline
- CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]
- \hline
-\end{tabular}
+\renewcommand{\arraystretch}{1.2}
 \caption{Test of cNET 16 filters with optimized software}
 \label{table:5}
+\begin{tabular}[c c c c]{|p{2.2 cm} p{1.1cm} p{1.1cm} p{2.4cm}|} 
+ \hline
+ \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
+ \hline 
+ GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
+ CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
+ CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]
+ \hline
+\end{tabular}
 \end{table}
@@
 
-The results show that for the GPU, classification time has increased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, 
-causing some parameters to be computed in the CPU in stead of the GPU, thus making the process slower.
+The results show that for the GPU, classification time has increased by 66\%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing some parameters to be computed in the CPU instead of the GPU, thus making the process slower.
 For the CPU the results are better because the operations are executed using each of the four cores, for this case a decrease in time of 22\% was obtained.
@@
 The total number of plants per image would round 18 plants considering maize and weeds as well.
-This aids to determine how many frames per second would be appropriate for the acquisition of images.\\
+This aids to determine how many frames per second would be appropriate for the acquisition of images.
+\\
 
@@
 For the CPU and the Raspberry Pi CPU, the results for classification time in the multithreading tests were considered.
-The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate.\\
+The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate like it\'s shown in Table \ref{table:6}.\\
 
@@
 \centering
-\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.7cm}|p{1.7cm}|p{2.0cm}|} 
+\renewcommand{\arraystretch}{1.2}
+\caption{Test of a complete image and the frames per second}
+\label{table:6}
+\begin{tabular}[c c c c]{|p{1.1 cm} p{1.7cm} p{1.7cm} p{2.0cm}|} 
  \hline
@@
  Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
- \hline
  FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
@@
 \end{tabular}
-\caption{Test of a complete image and the frames per second}
-\label{table:5}
 \end{table}
@@
 The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%.
-However with the Rasberry pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably.
+However with the Rasberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably.
 \\
@@
 
-In the case of implementing the algorithm in an embedded system, it is not recommended to work with a processor like Raspberry Pi 3, because it has a very slow processing because the frames per second needed to analyze the images is significantly low, So you should choose a card that has GPU, without the need for Multithreading and Batching.
+In the case of implementing the algorithm in an embedded system, it is not recommended to work with a processor like Raspberry Pi 3 for now(due they are promising advances in external Deep Lerning devices for embedded systems such as the Intel Movidius Neural Compute Stick), because it has a very slow processing because the frames per second needed to analyze the images is significantly low, so you should choose a card that has GPU, without the need for Multithreading and Batching.
 \\

### 2017-08-18 PaperBCJ.tex
Revision
Cambios revision final
cambios realizados el 18 de agosto 11 am

@@
 \IEEEoverridecommandlockouts
-\IEEEpubid{\makebox[\columnwidth]{\textbf{978-1-5386-3894-1/17/\$31.00~\copyright{}2017 IEEE} \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+%\IEEEpubid{\makebox[\columnwidth]{\textbf{978-1-5386-3894-1/17/\$31.00~\copyright{}2017 IEEE	} \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+\IEEEpubid{\makebox[\columnwidth]{\textbf{978-1-5386-3894-1/17/\$31.00~\copyright{}2017 IEEE	} \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
 
@@
 Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system.
-The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on \textbf{(revisar)} analyze if the hardware can process information in real time.
+The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to analyze if the hardware can process information in real time.
 \\
@@
 This was achieved by monitoring the obtained samples through an external display.
-Examples of the images captured are shown on the Fig.
+Examples of the images captured are shown in Fig.
 \ref{figure1}.
@@
 It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated.
-In the following image, final results of the processed images that conform the dataset are shown on the Fig.
+In the following image, final results of the processed images that conform the dataset are shown in Fig.
 \ref{figure3}.\\
@@
 
-For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following Table \ref{table:1} with the dataset distribution.
+For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the dataset distribution shown in Table \ref{table:1}.
 
@@
 With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset.
-The training results are shown on Table \ref{table:2}.
+The training results are shown in Table \ref{table:2}.
 \\
@@
 
-Based on the performance parameters shown on the table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\
+Based on the performance parameters shown in table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\
 
@@
 This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy.
-The results of the experiment are shown in the Table \ref{table:3} \\
+The results of the experiment are shown in Table \ref{table:3} \\
 
@@
 
-For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for \textbf{mejorar} gathering the training dataset images.
+For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds.
 Ten measurements of the mean classification time of the test dataset were obtained for each one of the different hardwares previously selected to run performance tests.
 Classification tests were started with Caffe in vanilla version.
-The obtained results were compared between cNET arquitecture with 64 and 16 filters, these are shown on Table \ref{table:4}.\\
+The obtained results were compared between cNET arquitecture with 64 and 16 filters, these are shown in Table \ref{table:4}.\\
 

### 2017-08-18 PaperBCJ.tex

@@
 During the last centuries, significant progress has taken place in science and technology developments.
-Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors, providing new means to approach problems in a different manner.
+Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors \cite{davim2017microfabrication} , providing new means to approach problems in a different manner.
 The availability of leading edge technologies has considerably increased, thus becoming more accessible to people.
-This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.
-\\
-
-Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with the new industrial revolution.
+This effect of globalization has allowed many countries to have access to state-of-the-art technological products\cite{grossman2015globalization}, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.
+\\
+
+Technological advances have caused industry transformations; manufacturing, food processing, and agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Agriculture of Precision(AP)  which has opened a new field for researching \cite{ortiz2012máquinas}.
 However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
-Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer.
+Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}.
 Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects.

### 2017-08-18 PaperBCJ.tex

@@
 
-Technological advances have caused industry transformations; manufacturing, food processing, and agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Agriculture of Precision(AP)  which has opened a new field for researching \cite{ortiz2012máquinas}.
+Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Agriculture of Precision(AP)  which has opened a new field for researching \cite{ortiz2012máquinas}.
 However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
@@
 
-One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared (IR) Images.
+One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared(IR) images.
 The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop.
@@
 This was done in order to improve green color detection based on the elimination of light and shadow in the images.
-Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through the following equation described by Wang, Meng, Luo and Mei \cite{wang2013path}.
+Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through   (\ref{eqn:1}) described by Wang, Meng, Luo and Mei \cite{wang2013path}.
 Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask.
 \begin{equation}
+\label{eqn:1}
 	S = 2*G - R - B
@@
 It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated.
-In the following image, final results of the processed images that conform the dataset are shown in Fig.
-\ref{figure3}.\\
+In Fig.
+\ref{figure3}, final results of the processed images that conform the dataset are shown.\\
 
@@
 	\includegraphics[width=2.5in]{im1}
-	\caption{Segmented and Masked images of dataset Above: Weed, Below: Maize}
+	\caption{Segmented and masked images of dataset Above: Maize, Below: Weed}
 	\label{figure3}
@@
 
-Based on the performance parameters shown in table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\
+Based on the performance parameters shown in Table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\
 
@@
 This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy.
-The results of the experiment are shown in Table \ref{table:3} \\
+The results of the experiment are shown in Table \ref{table:3}.
 
@@
  Accuracy(\%) & 97.26 & 96.40 \\
- Loss(\%) & 8.39 & 14.48 \\ [1ex] 
+ Loss(\%) & 8.39 & 13.72 \\ [1ex] 
  \hline 
@@
 
-As the table shows, the best results in classification time were achieved by the GPU processor, thus it is the best option to classify a large amount of images.
+As the Table \ref{table:4} shows, the best results in classification time were achieved by the GPU processor, thus it is the best option to classify a large amount of images.
 However, this project is thought to be implemented in an autonomous system so the Raspberry Pi was selected for the classification performance analysis due to its portability.
@@
 For the CPU the results are better because the operations are executed using each of the four cores, for this case a decrease in time of 22\% was obtained.
-Finally, the result for the Raspberry Pi CPU was a time decrease of 6.3 \%.\\
+Finally, the result for the Raspberry Pi CPU was a time decrease of 6.3\%.\\
 
@@
 
-For the estimation of the frames per second for each device, its optimal configuration was considered.
+For the estimation of the frames per second(FPS) for each device, its optimal configuration was considered.
 The GPU classification time during the test without multithreading was considered for this device.
 For the CPU and the Raspberry Pi CPU, the results for classification time in the multithreading tests were considered.
-The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate like it\'s shown in Table \ref{table:6}.\\
+The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate like it\'s shown in Table \ref{table:6}.
 
@@
 \renewcommand{\arraystretch}{1.2}
-\caption{Test of a complete image and the frames per second}
+\caption{Test of complete image classification in FPS}
 \label{table:6}
@@
 The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%.
-However with the Rasberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably.
+However with the Raspberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably.
 \\

### 2017-08-19 PaperBCJ.tex

@@
 
-In order to have adequate image processing that could be implemented to work in real time, the number of the network filter layers was reduced from 64 to 16, achieving to reduce the number of parameters to be computed during the classification.
+In order to have adequate image processing that could be implemented to work in real time, the number of network filter layers was reduced from 64 to 16, reducing the number of parameters to be computed during the classification.
 A classification time reduced by 2.5 times compared the original Net of 64 filters was obtained.
@@
 
-This paper presented an analysis of a Convolutional Neuronal Networks application for classification between maize plants and weeds.
+This paper presented an analysis of a Convolutional Neuronal Network application for classification between maize plants and weeds.
 With this purpose, several CNN Architectures were tested, the network that presented the best results was cNET of 16 filters, with a 97.23 \% of training accuracy, using a dataset of both classes of 44580 segmented images.
@@
 
-Also, by using different methods to classify the images in our experiments the results showed that the best time of classification was achieved by using a Nvidia Graphics Card.
+Also, by using different methods to classify images, the results showed that the best classification time was achieved by using a Nvidia Graphics Card.
 This was due to the parallel architecture that this GPU has.
@@
 
-The study demonstrated that is better to perform some geometrical transformations to the dataset images due to the benefits it offers, such as the improvement in plant classification since the plants will have different orientations in the crop field.
-\\
+The study demonstrated that performimg geometrical transformations to the dataset images improves plant classification accuracy since the plants will have different orientations in the crop field. \\
 
@@
 
-The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%.
-However with the Raspberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably.
+The use of Multithreading and Batching through the library OpenBLAS is beneficial when using a CPU, increasing the processing speed higher than 20 \%.
+In contrast, a minimum improvement was obtained with the Raspberry Pi.
+On the contrary, the use of a GPU was prejudicial because it reduces the processing speed considerably.
 \\
@@
 
-In the case of implementing the algorithm in an embedded system, it is not recommended to work with a processor like Raspberry Pi 3 for now(due they are promising advances in external Deep Lerning devices for embedded systems such as the Intel Movidius Neural Compute Stick), because it has a very slow processing because the frames per second needed to analyze the images is significantly low, so you should choose a card that has GPU, without the need for Multithreading and Batching.
+For implementing the algorithm in an embedded system, it is not recommended to work with a processor such as the Raspberry Pi 3 at the moment.
+This embedded system has a very slow processing speed because the frames per second used to analyze the images are significantly low, so a card that has GPU should be chosen, without the need for Multithreading and Batching.
+Even though there are promising advances in external Deep Lerning devices for embedded systems such as the Intel Movidius Neural Compute Stick, these systems are not yet available.
 \\

### 2017-08-24 PaperBCJ.tex
Fix spaces

--- 2017-08-18 PaperBCJ.tex
@@
 During the last centuries, significant progress has taken place in science and technology developments.
-Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors \cite{davim2017microfabrication} , providing new means to approach problems in a different manner.
+Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors \cite{davim2017microfabrication}, providing new means to approach problems in a different manner.
 The availability of leading edge technologies has considerably increased, thus becoming more accessible to people.
@@
 
-Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Agriculture of Precision(AP)  which has opened a new field for researching \cite{ortiz2012máquinas}.
+Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching \cite{ortiz2012máquinas}.
 However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.

### 2017-08-25 PaperBCJ.tex
Final Student Revision
Revision

@@
 
+\usepackage{makecell}
+
 % *** SUBFIGURE PACKAGES ***
@@
 Barreno Barreno Mauricio Daniel \IEEEauthorrefmark{2} and J\'acome Barrionuevo Jos\'e Misael \IEEEauthorrefmark{3}}
-\IEEEauthorblockA{Department of Energy and Mechanics,
-University of the Armed Forces ESPE\\
-Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
+\IEEEauthorblockA{Departamento de Energ\'ia y Mec\'anica,
+Universidad de las Fuerzas Armadas  ESPE\\
+Sangolqu\'i - Ecuador \\
 Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
@@
 The performance of the network was analyzed with LeNET, AlexNet, cNET and sNET network architectures.
-The network architecture that presented the best training results was cNET based on its performance in terms of accuracy (96.4\%) and processing time of 161 miliseconds in a Raspberry Pi CPU.
+The network architecture that presented the best training results was cNET based on its performance in terms of accuracy and processing time.
 The minimum working filter number for this network architecture was 16.
@@
 The availability of leading edge technologies has considerably increased, thus becoming more accessible to people.
-This effect of globalization has allowed many countries to have access to state-of-the-art technological products\cite{grossman2015globalization}, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.
+This effect of globalization has allowed many countries to have access to state-of-the-art technological products \cite{grossman2015globalization}, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.
 \\
@@
 Weed and crop segmentation is not limited to color images.
-In another application \cite{potena2016fast}, the use of a a multispectral camera permitted to obtain RGB and NIR images for the segmentation and classification purposes.
+In another application \cite{potena2016fast}, the use of a multispectral camera permitted to obtain RGB and NIR images for the segmentation and classification purposes.
 The images used a light CNN for the first process and a deep CNN for classification, its accuracy was as high as 98\% in the identification of weeds.
@@
 Debido a la popularidad de la computacion por GPU(IDEA COMPLETADA) por sus ventajas en el desarrollo de modelos de Redes Neuronales Convolucionales, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de clasificacion y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M.
-Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar el rendimiento de red en un sistema portable para su aplicacion en un sistema movil independiente .
+Tambien fue necesario considerar el uso de un CPU Core i7 2.7GHz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar el rendimiento de red en un sistema portable para su aplicacion en un sistema movil independiente .
 El hardware escogido sera probado para clasificar las imagenes y medir los tiempos de clasificacion para su posterior analisis.
@@
 These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M.
-Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system.
+Also, it was necessary to consider the use of a Core i7 2.7 GHz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2 GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system.
 The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to analyze if the hardware can process information in real time.
@@
 
-Then, through a first-stage digital image processing procedure, the images were normalized in its green channel.
+Then, through a first-stage digital image processing, the images were normalized in its green channel.
 This was done in order to improve green color detection based on the elimination of light and shadow in the images.
@@
 Lee \textit{et.
-al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations.
+al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by applying geometric transformations.
 In addition, geometric transformations  \cite{sladojevic2016deep} allow overfitting reduction and improve precision in the training process.
@@
 
-For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the dataset distribution shown in Table \ref{table:1}.
+For the validation phase, randomly the fifth part of the total image set of each class was chosen, resulting in the dataset distribution shown in Table \ref{table:1}.
 
@@
 Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet.
-Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes.
+Also, Potena and Nardi  \cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes.
 With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset.
@@
 \label{table:6}
-\begin{tabular}[c c c c]{|p{1.1 cm} p{1.7cm} p{1.7cm} p{2.0cm}|} 
- \hline
- \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{Raspberry Pi 3 with Threading} \\ 
+\begin{tabular}[c c c c]{|p{1.0 cm} p{1.7cm} p{1.7cm} p{1.7cm}|} 
+ \hline
+ \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU (Threading)} & \textbf{Raspberry Pi (Threading)} \\ 
  \hline
@@
 
-In order to have adequate image processing that could be implemented to work in real time, the number of network filter layers was reduced from 64 to 16, reducing the number of parameters to be computed during the classification.
+In order to have an adequate image processing that could be implemented to work in real time, the number of network filter layers was reduced from 64 to 16, reducing the number of parameters to be computed during the classification.
 A classification time reduced by 2.5 times compared the original Net of 64 filters was obtained.
@@
 
-The study demonstrated that performimg geometrical transformations to the dataset images improves plant classification accuracy since the plants will have different orientations in the crop field. \\
+The study demonstrated that performing geometrical transformations to the dataset images improves plant classification accuracy since the plants will have different orientations in the crop field. \\
 
@@
 
-This work has been supported by the University of the Army "ESPE" Latacunga.
+This work has been supported by the Universidad de las Fuerzas Armadas ESPE.
 

### 2017-08-26 PaperBCJ.tex
Final Change

@@
 
-Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching  \cite{ortiz2012máquinas}.
-However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
+Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching  \cite{ortiz2012máquinas}.
+However, there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
 Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to  introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}.

### 2017-08-27 PaperBCJ.tex
cambio final 27 agosto
cambio final 27 agosto

@@
 % correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+%\hyphenation{op-tical net-works semi-conduc-tor}
 \usepackage{graphicx}
 \usepackage{verbatim}
-\usepackage{array}
-\usepackage{filecontents}
+%\usepackage{array}
+%\usepackage{filecontents}
 %\usepackage[noadjust]{cite}
@@
 
-Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching  \cite{ortiz2012máquinas}.
+Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as Precision agriculture(PA)  which has opened a new research field  \cite{ortiz2012máquinas}.
 However, there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.
@@
 
-One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared(IR) images.
+One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by obtaining a set of infrared(IR) images.
 The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop.
@@
 Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}.
-This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds.
+This algorithm demonstrated an effectiveness of 98\% in the identification of weeds in rice crops.
 Araguez \textit{et.
-al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers.
-\\
-
+al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image of plants and performed the crop and weed segmentation with unspecified classifiers.
+\\
+\\
 Hong and Lei \cite{jeon2011robust} developed an approximation by using an optimal method for detection in various luminosity settings, they achived this by the use of an artificial neural network (ANN) for weed and maize classification with a precision of 92.5\%.

### 2017-08-27 PaperBCJ.tex
Final Correction

@@
 
-Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as Precision agriculture(PA)  which has opened a new research field  \cite{ortiz2012máquinas}.
+Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching  \cite{ortiz2012máquinas}.
 However, there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry.

### 2017-10-05 Presentacion.tex
Creation of the Presentation

\documentclass[10pt,a4paper]{beamer}
\usepackage[utf8]{inputenc}
%\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{verbatim}
\author{Cristian Chimbo}
\usefonttheme{professionalfonts} % fuentes de LaTeX
\usetheme{Szeged}
\usecolortheme{beaver}
\setbeamercovered{transparent}
\begin{document}
%\font\myfont=cmr12 at 20pt
%\title{{\myfont Precise Weed and Maize Classification through Convolutional Neuronal Networks}}
%\author{{\bf C\'ordova Andrea\inst{1}, Barreno Mauricio, J\'acome Jos\'e }\\
%\institute{
%\inst{1}%
 % Universidad de las Fuerzas Armadas ESPE\\
 % Latacunga - Ecuador}
%{ 2nd IEEE Ecuador Technical Chapters Meeting}
%\vspace*{1cm}}
%\date{October 2017}
\title[Precise Weed and Maize Classification through Convolutional Neuronal Networks] %optional
{Precise Weed and Maize Classification through
Convolutional Neuronal Networks}

\author[C\'ordova Andrea, Barreno Mauricio and J\'acome Jos\'e] % (optional, for multiple authors)
{C\'ordova Andrea, Barreno Mauricio and J\'acome Jos\'e}

\institute[Universidad de las Fuerzas Armadas ESPE] % (optional)
{
  \inst{1}%
  Departamento de Energ\'ia y Mec\'anica\\
  Universidad de las Fuerzas Armadas ESPE
}

\date[Ecuador] % (optional)
{2nd IEEE Ecuador Technical Chapters Meeting, October 2017}
\frame{\titlepage}
%-----------------------------
\begin{frame}
\frametitle{Presentation Outline}
\tableofcontents
%\newpage
\end{frame}
%-----------------------------
\section{Introduction}
\begin{frame}
\frametitle{Introduction}
\begin{enumerate}
\item Maize is one of the most important food of the world.
\item Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
\item La robotica esta presentando grandes avances en la agricultura de precision.
\item Inteligencia artificial cada vez se acerca mas a la inteligencia humana.\\
\end{enumerate}
\end{frame}
%--------------
\section{The Propose of the present study}
\begin{frame}
\frametitle{The Propose of the present study}
\begin{enumerate}
\item Obtener muestras(imagenes) para conformar un dataset.
\item Segmentar las muestras.
\item Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
\item Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
\item Optimizar la red.
\end{enumerate}
\end{frame}
%-----------------------------
\section{Hardware and Software Used}
\begin{frame}
\frametitle{Hardware and Software Used}
\textbf{Hardware}
\begin{enumerate}
\item Raspberry Pi 3.
\item Pi camera V2.1.
\item Nvidia graphic Card GTX950M.
\end{enumerate}
\textbf{Software}
\begin{enumerate}
\item OpenCV Library
\item Caffe framework
\item Ubuntu 16.04
\item PIXEL Distribution derived from Debian.
\end{enumerate}
\end{frame}
%-----------------------------
\section{Image Processing}
\begin{frame}
\begin{itemize}
	\item Acquire  an RGB image through RPi Camera v2.1
	\item Detect contours and crop image to the contour
	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{Poner cita aqui}
	\item OTSU Thresholding
	\item Mask image
\end{itemize}
\frametitle{Image Processing}
	\begin{figure}[h]
	\centering
	\includegraphics[width=3.5 in]{procesamiento}
	\caption{The process of image processing, por lo pronto}
	\label{figure4}
	\end{figure}
\end{frame}
%-----------------------------
\section{Dataset}
\begin{frame}
\frametitle{Dataset}
{Dataset Description}
\begin{enumerate}
\item Place Pillaro Tungurahua Ecuador
\item La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) \cite{sladojevic2016deep}.
\item Imagenes rotadas cada 30 para mejorar la deteccion de las planta.
\item 1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion
\end{enumerate}
\begin{table}[h!]
\renewcommand{\arraystretch}{1.3}
\caption{Dataset distribution of each class}
\label{table:1}
\centering
\begin{tabular}{| c c c |} 
 \hline
 \textbf{Images} & \textbf{Maize} & \textbf{Weed}  \\ [1ex] 
 \hline
 Original  & 2835 & 880 \\ 
 Rotated & 34222 & 10762 \\ 
 Entrenamiento & 25695 & 8560 \\
 Validacion & 8325 & 2000 \\
 \hline
\end{tabular}
\end{table}
\end{frame}
%-----------------------------
\section{Convolutional Neural Networks}
\begin{frame}
\frametitle{Convolutional Neural Networks(CNN)}
\begin{itemize}
	\item Highly accurate method for image classification
	\item A class of deep, feed-forward artificial neural networks
	\item Tested on classification of plants, poner citas
	\item Multiple architectures and applications
\end{itemize}
	\begin{figure}[h]
	\centering
	\includegraphics[width=3.5 in]{arquitectura}
	\caption{Normal architecture in a Convolutional Neural Network}
	\label{figure4}
	\end{figure}
\end{frame}
\section{Architectures Tested}
\begin{frame}
\frametitle{Architectures tested}
\begin{itemize}
	\item Highly accurate method for image classification
\end{itemize}
\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\end{table}
\end{frame}
%-----------------------------
\section{cNET Performance}
\begin{frame}
\frametitle{cNET Performance}
\begin{enumerate}
\item Obtener muestras(imagenes) para conformar un dataset.
\end{enumerate}
\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of cNET 16 filters with optimized software}
\label{table:5}
\begin{tabular}[c c c c]{|p{2.2 cm} p{1.1cm} p{1.1cm} p{2.4cm}|} 
 \hline
 \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
 \hline 
 GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
 CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
 CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]
 \hline
\end{tabular}
\end{table}
\end{frame}
%-----------------------------
\section{Presuming performance of cNET 16 filters}
\begin{frame}
\frametitle{Presuming performance of cNET 16 filters}
\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of complete image classification in FPS}
\label{table:6}
\begin{tabular}[c c c c]{|p{1.0 cm} p{1.7cm} p{1.7cm} p{1.7cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU } & \textbf{CPU} & \textbf{Raspberry Pi} \\ 
 \hline
 Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
 FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
 \hline
\end{tabular}
\end{table}
\end{frame}
%--------------
\section{Conclusion}
\begin{frame}
\frametitle{Conclusion}
\begin{itemize}
\item
\item
\end{itemize}
\end{frame}
%--------------
\section{Recomendations}
\begin{frame}
\frametitle{Recomendations}
\begin{itemize}
\item
\item
\end{itemize}
\end{frame}
%--------------
\large
\begin{frame}
%\frametitle{The Propose of the present study}
\begin{center}
Thanks!
\end{center}
\end{frame}

%-----------------------------
\bibliographystyle{plain}
\bibliography{bibliografiapaper}
\end{document}

### 2017-10-06 Presentacion.tex
Add images

@@
 \usepackage[utf8]{inputenc}
-%\usepackage[spanish]{babel}
+\usepackage[english]{babel}
 \usepackage{amsmath}
@@
 \usepackage{makeidx}
+\usepackage[style=verbose]{biblatex}
 \usepackage{graphicx}
@@
 \usepackage{verbatim}
-\author{Cristian Chimbo}
 \usefonttheme{professionalfonts} % fuentes de LaTeX
@@
 \setbeamercovered{transparent}
+\addbibresource{bibliografiapaper.bib}
 \begin{document}
@@
 {2nd IEEE Ecuador Technical Chapters Meeting, October 2017}
+\logo{\includegraphics[height=1.5cm]{espe.png}}
 \frame{\titlepage}
@@
 %-----------------------------
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Introduction}
@@
 \frametitle{Introduction}
-\begin{enumerate}
-\item Maize is one of the most important food of the world.
-\item Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
-\item La robotica esta presentando grandes avances en la agricultura de precision.
-\item Inteligencia artificial cada vez se acerca mas a la inteligencia humana.\\
-\end{enumerate}
-\end{frame}
-%--------------
-\section{The Propose of the present study}
-\begin{frame}
-\frametitle{The Propose of the present study}
-\begin{enumerate}
-\item Obtener muestras(imagenes) para conformar un dataset.
-\item Segmentar las muestras.
-\item Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
-\item Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
-\item Optimizar la red.
-\end{enumerate}
+\textbf{Introduction}
+\begin{itemize}
+\item Maize is one of the most important \textbf{food or crop?} of the world.
+\item Weed can affect the maize crop up to 5000 Kg/Ha.\footnote{suarez2005distintos} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
+\item Robotics has presented a huge advance in Precision Agriculture.%La robotica esta presentando grandes avances en la agricultura de precision.
+\item Artificial Intelligence reached near-to-human precision.%Inteligencia artificial cada vez se acerca mas a la inteligencia humana.
+\end{itemize}
+\textbf{The Propose of the present study}
+\begin{itemize}
+\item Obtain samples to conform a dataset%Obtener muestras(imagenes) para conformar un dataset.
+\item Segment samples%Segmentar las muestras.
+\item Test diffent network architectures of Convolutional Neural Networks for classify Maize and Weed%Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
+\item Benchmark the best architure to analyse time of processing %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
+\item Optimize the time of processing of the net%Optimizar la red.
+\end{itemize}
 \end{frame}
 %-----------------------------
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Hardware and Software Used}
@@
 %-----------------------------
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Image Processing}
@@
 	\item Detect contours and crop image to the contour
-	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{Poner cita aqui}
+	\item Normalize Green Channel and then $S = 2*G - R - B$ \footcite{wang2013path}
 	\item OTSU Thresholding
@@
 	\includegraphics[width=3.5 in]{procesamiento}
-	\caption{The process of image processing, por lo pronto}
+	\caption{The process of image processing,\textbf{ por lo pronto}}
 	\label{figure4}
@@
 %-----------------------------
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Dataset}
@@
 \frametitle{Dataset}
-{Dataset Description}
-\begin{enumerate}
-\item Place Pillaro Tungurahua Ecuador
-\item La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) \cite{sladojevic2016deep}.
-\item Imagenes rotadas cada 30 para mejorar la deteccion de las planta.
-\item 1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion
-\end{enumerate}
+%{Dataset Description}
+\begin{itemize}
+\item Samples obtained in Pillaro-Tungurahua-Ecuador
+\item Images obtained in its initial stage(3-7 leaves) . %La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) 
+\item Rotated images every 30º to improve detection of plants\footcite{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
+\item 1/5 of the total images chosed randomly to validate training%1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion
+\end{itemize}
 \begin{table}[h!]
@@
  Rotated & 34222 & 10762 \\ 
- Entrenamiento & 25695 & 8560 \\
- Validacion & 8325 & 2000 \\
+ Training & 25695 & 8560 \\
+ Validation & 8325 & 2000 \\
  \hline
@@
 \end{frame}
+
 %-----------------------------
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Convolutional Neural Networks}
@@
 	\item A class of deep, feed-forward artificial neural networks
-	\item Tested on classification of plants, poner citas
+	\item Tested on classification of plants, \footcite{cheng2015feature} \footcite{potena2016fast} \footcite{di2016automatic}
 	\item Multiple architectures and applications
@@
 \end{frame}
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Architectures Tested}
@@
 \begin{itemize}
-	\item Highly accurate method for image classification
+	\item LeNET and AlexNet(Caffe Zoo Model) \
+	\item cNET and sNET \footnote{potena2016fast}
+	\item 3000 iterations in each training
 \end{itemize}
@@
 \renewcommand{\arraystretch}{1.2}
-\caption{Comparison of the 4 types of CNN}
+\caption{Comparison of the 4 types of CNN in training the dataset}
 \label{table:2}
@@
  Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
- Iterations & 3000 & 3000 & 3000 & 3000 \\ 
  Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
@@
 %-----------------------------
-\section{cNET Performance}
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
+\section{Tuning cNET}
 \begin{frame}
@@
 \begin{enumerate}
-\item Obtener muestras(imagenes) para conformar un dataset.
+\item cNET can be improved by decrease the number of filters
+\item Images can be batched and also Caffe can be multithreaded
+\item Both nets were trained with 9000 iterations
 \end{enumerate}
-\begin{table}[h!]
+\begin{table}[h]
 \centering
 \renewcommand{\arraystretch}{1.2}
-\caption{Test of cNET 16 filters with optimized software}
-\label{table:5}
-\begin{tabular}[c c c c]{|p{2.2 cm} p{1.1cm} p{1.1cm} p{2.4cm}|} 
+\caption{Comparison between cNET of 16 and 64 filters}
+\label{table:3}
+\begin{tabular}{|l c c |} 
  \hline
- \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
+ \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
  \hline
- GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
- CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
- CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]
+ Number of parameters & 1651376 & 6421568 \\ 
+ Accuracy(\%) & 97.26 & 96.40 \\
+ Loss(\%) & 8.39 & 13.72 \\ [1ex] 
  \hline 
@@
 %-----------------------------
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Presuming performance of cNET 16 filters}
@@
 \frametitle{Presuming performance of cNET 16 filters}
+\begin{itemize}
+	\item A dataset of test with 202 images of each class was used
+	\item In a single image it can be found 18 plants to classify
+\end{itemize}
 \begin{table}[h!]
@@
 \label{table:6}
-\begin{tabular}[c c c c]{|p{1.0 cm} p{1.7cm} p{1.7cm} p{1.7cm}|} 
+\begin{tabular}[c c c c]{|p{1.8 cm} p{1.5cm} p{2.1cm} p{2.3cm}|} 
  \hline
  \textbf{Parameter} &\textbf{GPU } & \textbf{CPU} & \textbf{Raspberry Pi} \\ 
+ \hline
+  \textbf{Method} &\textbf{One Core} & \textbf{Multithreading} & \textbf{Multithreading} \\ 
  \hline
@@
 %--------------
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 \section{Conclusion}
@@
 \begin{itemize}
-\item
-\item
-\end{itemize}
-\end{frame}
-%--------------
-\section{Recomendations}
-\begin{frame}
-\frametitle{Recomendations}
-\begin{itemize}
-\item
-\item
+\item cNET showed the better results in classification of maize and weed
+\item The reduce of the number of filters allow to decrease the processing time and increase the accuracy of the net
+\item GPU showed the best results but with Multithreading and Batching CPU and Raspberry Pi can improve its time of processing 
+\item Due to the limitations of the Raspberry Pi, it can't be used to classify in real time, but a Neural Module(such as Intel Movidius) can improve that result
 \end{itemize}
@@
 %-----------------------------
-\bibliographystyle{plain}
-\bibliography{bibliografiapaper}
+%\bibliographystyle{plain}
+%\bibliography{bibliografiapaper}
 \end{document}

### 2017-10-06 Presentacion.tex
cambio 6 octubre
cambio 6 de octubre

@@
 \begin{itemize}
-\item Maize is one of the most important \textbf{food or crop?} of the world.
-\item Weed can affect the maize crop up to 5000 Kg/Ha.\footnote{suarez2005distintos} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
-\item Robotics has presented a huge advance in Precision Agriculture.%La robotica esta presentando grandes avances en la agricultura de precision.
+\item Maize is one of the most important crops of the world.
+\item Weed can affect maize crop yield up to 5000 Kg/Ha.\footnote{suarez2005distintos} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
+\item Robotics has had significant contributions to Precision Agriculture.%La robotica esta presentando grandes avances en la agricultura de precision.
 \item Artificial Intelligence reached near-to-human precision.%Inteligencia artificial cada vez se acerca mas a la inteligencia humana.
 \end{itemize}
-\textbf{The Propose of the present study}
+\textbf{Purpose of the present study}
 \begin{itemize}
@@
 \item Segment samples%Segmentar las muestras.
-\item Test diffent network architectures of Convolutional Neural Networks for classify Maize and Weed%Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
-\item Benchmark the best architure to analyse time of processing %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
-\item Optimize the time of processing of the net%Optimizar la red.
+\item Test different network architectures of Convolutional Neural Networks for Maize and Weed Clasification %Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
+\item Benchmark the best network architecture to analyze processing time %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
+\item Optimize the network processing speed %Optimizar la red.
 \end{itemize}
@@
 }
-\section{Hardware and Software Used}
+\section{Used Hardware and Software}
 \begin{frame}
-\frametitle{Hardware and Software Used}
+\frametitle{Used Hardware and Software}
 \textbf{Hardware}
@@
 \item Images obtained in its initial stage(3-7 leaves) . %La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) 
-\item Rotated images every 30º to improve detection of plants\footcite{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
-\item 1/5 of the total images chosed randomly to validate training%1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion
+\item Rotated images every 30º to improve plant detection 
+\footcite{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
+\item 1/5 of the total images chosen randomly to validate training%1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion
 \end{itemize}
@@
 }
-\section{Architectures Tested}
+\section{Tested Architectures}
 \begin{frame}
-\frametitle{Architectures tested}
+\frametitle{Tested Architectures}
 \begin{itemize}
@@
 \begin{enumerate}
-\item cNET can be improved by decrease the number of filters
+\item cNET can be improved by decreasing the number of filters
 \item Images can be batched and also Caffe can be multithreaded
@@
 }
-\section{Presuming performance of cNET 16 filters}
+\section{Estimated performance of cNET 16 filters}
 \begin{frame}
-\frametitle{Presuming performance of cNET 16 filters}
+\frametitle{Estimated performance of cNET 16 filters}
 \begin{itemize}
-	\item A dataset of test with 202 images of each class was used
-	\item In a single image it can be found 18 plants to classify
+	\item A test dataset with 202 images of each class was used
+	\item 18 plants can be found in a single image approximately to be classified
 \end{itemize}
@@
 \begin{itemize}
-\item cNET showed the better results in classification of maize and weed
-\item The reduce of the number of filters allow to decrease the processing time and increase the accuracy of the net
-\item GPU showed the best results but with Multithreading and Batching CPU and Raspberry Pi can improve its time of processing 
+\item cNET showed the best results in classification of maize and weed
+\item The reduction of the number of filters decreased the processing time and increased the network accuracy 
+\item GPU showed the best results, but with Multithreading and Batching CPU and Raspberry Pi can improve its processing time
 \item Due to the limitations of the Raspberry Pi, it can't be used to classify in real time, but a Neural Module(such as Intel Movidius) can improve that result

### 2017-10-10 Presentacion.tex
add images

@@
 \usepackage{makeidx}
-\usepackage[style=verbose]{biblatex}
 \usepackage{graphicx}
@@
 \setbeamercovered{transparent}
-\addbibresource{bibliografiapaper.bib}
+
 \begin{document}
@@
 	\item Detect contours and crop image to the contour
-	\item Normalize Green Channel and then $S = 2*G - R - B$ \footcite{wang2013path}
+	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{wang2013path}
 	\item OTSU Thresholding
@@
 \item Images obtained in its initial stage(3-7 leaves) . %La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) 
-\item Rotated images every 30º to improve plant detection 
-\footcite{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
+\item Rotated images every 30º to improve plant detection \footnote{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
 \item 1/5 of the total images chosen randomly to validate training%1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion
@@
 \end{frame}
-
+\begin{frame}
+\frametitle{Samples}
+\begin{itemize}
+\item Maize Plants \textit{(Zea maiz)}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.5 in]{samplesmaize}
+	\caption{Normal architecture in a Convolutional Neural Network}
+	\label{figure4}
+	\end{figure}
+	\item Weed Plants \textit{(Zea maiz)}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.5 in]{samplesweed}
+	\caption{Normal architecture in a Convolutional Neural Network}
+	\label{figure4}
+	\end{figure}
+\end{itemize}
+\end{frame}
 %-----------------------------
@@
 	\item A class of deep, feed-forward artificial neural networks
-	\item Tested on classification of plants, \footcite{cheng2015feature} \footcite{potena2016fast} \footcite{di2016automatic}
+	\item Tested on classification of plants, \footnote{cheng2015feature} \footnote{potena2016fast} \footnote{di2016automatic}
 	\item Multiple architectures and applications
@@
 %\bibliographystyle{plain}
-%\bibliography{bibliografiapaper}
+\bibliography{bibliografiapaper}
 \end{document}

### 2017-10-17 Presentacion.tex
Changes of Plants

@@
 \documentclass[10pt,a4paper]{beamer}
+\usepackage[backend=biber]{biblatex}
+\addbibresource{bibliografiapaper}
 \usepackage[utf8]{inputenc}
@@
 \begin{document}
-%\font\myfont=cmr12 at 20pt
-%\title{{\myfont Precise Weed and Maize Classification through Convolutional Neuronal Networks}}
-%\author{{\bf C\'ordova Andrea\inst{1}, Barreno Mauricio, J\'acome Jos\'e }\\
-%\institute{
-%\inst{1}%
- % Universidad de las Fuerzas Armadas ESPE\\
- % Latacunga - Ecuador}
-%{ 2nd IEEE Ecuador Technical Chapters Meeting}
-%\vspace*{1cm}}
-%\date{October 2017}
 \title[Precise Weed and Maize Classification through Convolutional Neuronal Networks] %optional
@@
 \begin{itemize}
-\item Maize is one of the most important crops of the world.
-\item Weed can affect maize crop yield up to 5000 Kg/Ha.\footnote{suarez2005distintos} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
+\item Maize(\textit{Zea mays}) is one of the most important crops of the world.
+\item Weed can affect maize crop yield up to 5000 Kg/Ha.\footnote{ R.
+SU\'AREZ and J.
+P.
+Y.
+J.
+VALLADARES, “Distintos sistemas de escarda en ma\'iz forrajero,” \textit{Producciones agroganaderas: Gesti\'on eficiente
+y conservaci\'on del Medio Natural. Actas de la XLV RC de la SEEP. Gij\'on}, 2005.} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
 \item Robotics has had significant contributions to Precision Agriculture.%La robotica esta presentando grandes avances en la agricultura de precision.
@@
 \item Segment samples%Segmentar las muestras.
-\item Test different network architectures of Convolutional Neural Networks for Maize and Weed Clasification %Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
+\item Test accuracy in different network architectures of Convolutional Neural Networks for Maize and Weed Clasification %Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
 \item Benchmark the best network architecture to analyze processing time %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
@@
 \end{enumerate}
+\begin{figure}[hbtp]
+%\caption{•}
+\centering
+\includegraphics[scale=0.3]{SoftHard.png}
+\end{figure}
+
 \end{frame}
@@
 \begin{itemize}
-	\item Acquire  an RGB image through RPi Camera v2.1
+	\item Acquire  an RGB image through RPi Camera v2.1(Centered to the plant)
+
+	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{ P.
+Wang, Z.
+Meng, C.
+Luo, and H.
+Mei, “Path recognition for agricultural robot vision navigation under weed environment,” in \textit{7th International Conference on Computer and Computing Technologies in Agriculture (CCTA)}, no.
+Part I.
+Springer, 2013, pp.
+242–248.
+}
+	\item OTSU Thresholding
 	\item Detect contours and crop image to the contour 
-	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{wang2013path}
-	\item OTSU Thresholding
 	\item Mask image
+
 \end{itemize}
@@
 	\centering
-	\includegraphics[width=3.5 in]{procesamiento}
-	\caption{The process of image processing,\textbf{ por lo pronto}}
+	\includegraphics[width=3.5 in]{SegmentationPaper}
+	\caption{Steps of image processing(Cropped image)}
 	\label{figure4}
@@
   \begin{frame}
-    \frametitle{Table of Contents}
+    \frametitle{Table of
+     Contents}
     \tableofcontents[currentsection]
@@
 \item Images obtained in its initial stage(3-7 leaves) . %La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) 
-\item Rotated images every 30º to improve plant detection \footnote{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
+\item Rotated images every 30º to improve plant detection \footnote{ S.
+Sladojevic, M.
+Arsenovic, A.
+Anderla, D.
+Culibrk, and D.
+Stefanovic, “Deep neural networks based recognition of plant diseases by leaf image classification,” \textit{Computational intelligence and neuroscience}, vol.
+2016, 2016.
+}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
 \item 1/5 of the total images chosen randomly to validate training%1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion
@@
 	\includegraphics[width=3.5 in]{samplesmaize}
-	\caption{Normal architecture in a Convolutional Neural Network}
+	%\caption{Normal architecture in a Convolutional Neural Network}
 	\label{figure4}
 	\end{figure}
-	\item Weed Plants \textit{(Zea maiz)}
+	\item Weed Plants \textit{(Urtica Urens, Lysimachia vulgaris , Chenopodium \'album , Malva Capestri)} \footnote{COBA ROBALINO, José María.
+\textit{Monografía General del Cantón Píllaro.}} %Ortiga, Allpaquinua Cuchimalva, Forastera, Allpaquinua,
 \begin{figure}[h]
@@
 	\includegraphics[width=3.5 in]{samplesweed}
-	\caption{Normal architecture in a Convolutional Neural Network}
+	%\caption{Normal architecture in a Convolutional Neural Network}
 	\label{figure4}
@@
 	\item A class of deep, feed-forward artificial neural networks
-	\item Tested on classification of plants, \footnote{cheng2015feature} \footnote{potena2016fast} \footnote{di2016automatic}
+	\item Tested on classification of plants, \footnote{B.
+Cheng and E.
+T.
+Matson, “A feature-based machine learning agent for automatic rice and weed discrimination.”} \footnote{ C.
+Potena, D.
+Nardi, and A.
+Pretto, “Fast and accurate crop and weed identification with summarized train sets for precision agriculture”
+}
 	\item Multiple architectures and applications
@@
 	\item LeNET and AlexNet(Caffe Zoo Model) \
-	\item cNET and sNET \footnote{potena2016fast}
+	\item cNET and sNET \footnote{ C. Potena, D. Nardi, and A. Pretto, “Fast and accurate crop and weed identification with summarized train sets for precision agriculture”
+}
 	\item 3000 iterations in each training
@@
 %\bibliographystyle{plain}
-\bibliography{bibliografiapaper}
+%\bibliography{bibliografiapaper}
 \end{document}

### 2017-10-17 Lecture.tex
Add summary

\documentclass[10pt,a4paper]{proc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{José Jácome}
\title{Lecture for Conference}
\begin{document}
\section{Presentation}
Ladies and Gentlemen, my name is Jos\'e J\'acome, I'm student of Mechatronics Engineering and I'm representing to the Universidad de las Fuerzas Armadas ESPE and my co-authors Andrea C\'ordova and Mauricio Barreno, I'm going to present you our paper "Precise Weed and Maize Classification through Convolutional Neuronal Networks", so let's start...
\section{Introduction}
So first, we talk about Maize, it's one of the most important crops in the world, that Crop could be affected by weed in the yield up to 5000 Kg/Ha, so it is neccessary to develop solutions for Precision Agriculture with Robotics. It's possible due to AI has reached a near-to-human precision
\section{Purpose of the present study}
Well, we are going to develop a "Clasifier" of Maize and Weed, so we have to do:
Obtain Samples to conform datasets in Maize Crops, Make an Algorith of Image Processing to Segment Samples, after we test the accuracy in different network architectures of Convolutional Neural Networks for Maize and Weed Clasification, later it's neccesary to Benchmark the appropiate network architecture  and finally optimize the network for run in selected hardware 
\section{Used Hardware and Software}
To develop that objetives, we have chosen the present hardware: A popular embedded system: Raspberry Pi 3 with its camera to get the samples, a CPU Core i7 6Th Generation and a Nvidia Graphics Card the GTX950M. \\
And also we used free software to develop the elements of the net, first an image proccessing Library OpenCV, Caffe Framework to develop general-purpose convolutional (Fully Compatible with Python and C++) and Linux OS such as Ubuntu for the PC and Pixel for the Raspberry Pi.

\section{Image Processing}
With the help of OpenCV, we developed an algorithm, a firs step was Acquiere a RGB from the Pi Camera, centered and in a vertical position of the plant, next to we normalized the Geen Channel to avoid lights and shadows of the Image, afterwards we substracted the Green Channel from the Blue and Red Channel with the next equation described with Wang and others. After the image need to be thresholded through the OTSU Method, next it's neccesary to Detect the contours and crop te image, after for get the max detail we masked the imagen. After we have some examples of the processing of images, for weed we have common plants in the Ecuadorin Highlands such as Ortiga, Allpaquinua and Malva. 
\section{Dataset}
The dataset was conformed by samples took in Pillaro-Tungurahua-Ecuador a great producer of many crops such as maize, the samples were obtained in crops at stage V3-V7(3-7 leaves), after like Sladojevic said, we rotated images every 30º for improve the detection in any position, after the fifth part of the total images were chosen randomly to validate training and we have the following chart. 
\section{Convolutional Neural Networks}
Let's talk something about CNN, It's a highly accurate method for image classification, aclas of deep, feed-forwar artificial NN, it was tested in classification of plants and have multiple architectures and applications. We  can see a cNET architecture here, with the main layers such as Convolution, Pooling and Fully Connected.
\section{Tested Architectures}
We have chosen four architectures, the first two were choosen of the Caffe Zoo Model, a open resource of CNN Architectures, and the last two were choosen of the paper of Ciro Potena and others, sNET and cNET(beetroot). So, we have the following results, the net with best results was cNET with 96.4\% of accuracy and 13.72\$ of Loss. 
\section{cNET Performance}
cNET has 6 million of filters, so cNET can be improved by decresing the number of filtres, also Images can be batched and also Caffe ca be Multithreaded, and both nets were trained with 9000 iterations, so the result were better because the images of the dataset don't have too much features of shape and color to process. 
\section{Estimated performance of cNET 16 filters}
well, like I mentioned before, the nets in Caffe can be tuned, so we have the results with the next parameters and considering that 18 planst can be found in a single image of a row of crop, so.
\section{Conclusion}
\begin{itemize}
\item cNET showed the best results in classification of maize and weed
\item The reduction of the number of filters decreased the processing time and increased the network accuracy 
\item GPU showed the best results, but with Multithreading and Batching CPU and Raspberry Pi can improve its processing time
\item Due to the limitations of the Raspberry Pi, it can't be used to classify in real time, but a Neural Module(such as Intel Movidius) can improve that result
\end{itemize}
Thanks!
\end{document}

### 2017-10-17 Presentacion.tex
Add summary

@@
   Departamento de Energ\'ia y Mec\'anica\\
+  Mechatronics Engineering\\
   Universidad de las Fuerzas Armadas ESPE
@@
 \item Test accuracy in different network architectures of Convolutional Neural Networks for Maize and Weed Clasification %Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
-\item Benchmark the best network architecture to analyze processing time %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
+\item Benchmark the appropiate network architecture to analyze processing time %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
 \item Optimize the network processing speed %Optimizar la red.
@@
 \item Pi camera V2.1.
+\item Core i7 6th Generation
 \item Nvidia graphic Card GTX950M.
@@
 }
+\begin{frame}
+\frametitle{Samples}
+\begin{itemize}
+\item Maize Plants \textit{(Zea maiz)}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.5 in]{samplesmaize}
+	%\caption{Normal architecture in a Convolutional Neural Network}
+	\label{figure4}
+	\end{figure}
+	\item Weed Plants \textit{(Urtica Urens, Lysimachia vulgaris , Chenopodium \'album , Malva Capestri)} \footnote{COBA ROBALINO, José María.
+\textit{Monografía General del Cantón Píllaro.}} %Ortiga, Allpaquinua Cuchimalva, Forastera, Allpaquinua,
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=3.5 in]{samplesweed}
+	%\caption{Normal architecture in a Convolutional Neural Network}
+	\label{figure4}
+	\end{figure}
+\end{itemize}
+\end{frame}
+%-----------------------------
 \section{Dataset}
@@
 \item Images obtained in its initial stage(3-7 leaves) . %La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) 
-\item Rotated images every 30º to improve plant detection \footnote{ S.
+\item Rotated images every 30º to improve plant detection in any position \footnote{ S.
 Sladojevic, M.
@@
 \end{frame}
-\begin{frame}
-\frametitle{Samples}
-\begin{itemize}
-\item Maize Plants \textit{(Zea maiz)}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=3.5 in]{samplesmaize}
-	%\caption{Normal architecture in a Convolutional Neural Network}
-	\label{figure4}
-	\end{figure}
-	\item Weed Plants \textit{(Urtica Urens, Lysimachia vulgaris , Chenopodium \'album , Malva Capestri)} \footnote{COBA ROBALINO, José María.
-\textit{Monografía General del Cantón Píllaro.}} %Ortiga, Allpaquinua Cuchimalva, Forastera, Allpaquinua,
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=3.5 in]{samplesweed}
-	%\caption{Normal architecture in a Convolutional Neural Network}
-	\label{figure4}
-	\end{figure}
-\end{itemize}
-\end{frame}
-%-----------------------------
+%-------------------------
 \AtBeginSection[]

### 2017-10-18 Lecture.tex
Cambios finales
cambios 18 de octubre del 2017

@@
 \section{Presentation}
-Ladies and Gentlemen, my name is Jos\'e J\'acome, I'm student of Mechatronics Engineering and I'm representing to the Universidad de las Fuerzas Armadas ESPE and my co-authors Andrea C\'ordova and Mauricio Barreno, I'm going to present you our paper "Precise Weed and Maize Classification through Convolutional Neuronal Networks", so let's start...
+Ladies and Gentlemen, my name is Jos\'e J\'acome, I'm a Mechatronics Engineering student and I'm representing the Universidad de las Fuerzas Armadas ESPE as well as the co-authors of this paper, Andrea C\'ordova and Mauricio Barreno.
+I will present to you our paper titled "Precise Weed and Maize Classification through Convolutional Neuronal Networks", so let's start...
 \section{Introduction}
-So first, we talk about Maize, it's one of the most important crops in the world, that Crop could be affected by weed in the yield up to 5000 Kg/Ha, so it is neccessary to develop solutions for Precision Agriculture with Robotics.
-It's possible due to AI has reached a near-to-human precision
+So first, lets begin talking about Maize, it's one of the most important crops in the world.
+This Crop can be significantly affected by weeds, causing a yield reduction of up to 5000 Kg/Ha, so it is necessary to develop solutions for this particular problem and Precision Agriculture with Robotics have a great potential for solving this kind of issues.
+It's application is possible due to the fact that AI has reached near-to-human precision
 \section{Purpose of the present study}
-Well, we are going to develop a "Clasifier" of Maize and Weed, so we have to do:
-Obtain Samples to conform datasets in Maize Crops, Make an Algorith of Image Processing to Segment Samples, after we test the accuracy in different network architectures of Convolutional Neural Networks for Maize and Weed Clasification, later it's neccesary to Benchmark the appropiate network architecture  and finally optimize the network for run in selected hardware
+The purpose of this study was to develop a Maize and Weed "Classifier" of Maize and Weed, so firstly we:
+Obtained Sample images to conform a maize dataset and Make an Algorith of Image Processing to Segment Samples.
+Afterwards we tested the accuracy in different network architectures of Convolutional Neural Networks for Maize and Weed Classification.
+Later it was necessary to Benchmark the appropriate network architecture  and finally optimize the network to run in a specific hardware.
 \section{Used Hardware and Software}
-To develop that objetives, we have chosen the present hardware: A popular embedded system: Raspberry Pi 3 with its camera to get the samples, a CPU Core i7 6Th Generation and a Nvidia Graphics Card the GTX950M.
+To obtain the desired result, we have chosen the following hardware: A popular embedded system: Raspberry Pi 3 with its camera to get the samples, a CPU Core i7 6Th Generation and a Nvidia Graphics Card the GTX950M.
 \\
@@
 \section{Image Processing}
-With the help of OpenCV, we developed an algorithm, a firs step was Acquiere a RGB from the Pi Camera, centered and in a vertical position of the plant, next to we normalized the Geen Channel to avoid lights and shadows of the Image, afterwards we substracted the Green Channel from the Blue and Red Channel with the next equation described with Wang and others.
-After the image need to be thresholded through the OTSU Method, next it's neccesary to Detect the contours and crop te image, after for get the max detail we masked the imagen.
-After we have some examples of the processing of images, for weed we have common plants in the Ecuadorin Highlands such as Ortiga, Allpaquinua and Malva.
+With the help of OpenCV, we developed an algorithm.
+A firs step was to Acquire a RGB image from the Pi Camera, centered and in a vertical position on reference to the plant, next to we normalized the Green Channel to avoid lights and shadows of the Image, afterwards we subtracted the Green Channel from the Blue and Red Channel with the next equation described by Wang.
+After this, the image needed to be thresholded through the OTSU Method.
+Following this, it was necessary to Detect the contours and crop the image.
+furthermore, to get a maximum detail we masked the image.
+In the end we show some examples of the image processing process.
+There are common plants in the Ecuadorin Highlands such as Ortiga, Allpaquinua and Malva that fall under weed classification.
 \section{Dataset}
-The dataset was conformed by samples took in Pillaro-Tungurahua-Ecuador a great producer of many crops such as maize, the samples were obtained in crops at stage V3-V7(3-7 leaves), after like Sladojevic said, we rotated images every 30º for improve the detection in any position, after the fifth part of the total images were chosen randomly to validate training and we have the following chart.
+The dataset was conformed by samples took in Pillaro-Tungurahua-Ecuador, a great producer of many crops such as maize, the samples were obtained in crops at stage V3-V7(3-7 leaves).
+Following the procedure established by Sladojevic, we rotated images every 30º to improve the detection of plants in any position.
+Following this, the fifth part of the total images were chosen randomly to validate the neural network training and we obtained following chart.
 \section{Convolutional Neural Networks}
-Let's talk something about CNN, It's a highly accurate method for image classification, aclas of deep, feed-forwar artificial NN, it was tested in classification of plants and have multiple architectures and applications.
+Let's talk about CNN, It's a highly accurate method for image classification, aclas of deep, feed-forward artificial NN.
+it has been widely tested in classification of plants and has multiple architectures and applications.
 We  can see a cNET architecture here, with the main layers such as Convolution, Pooling and Fully Connected.
 \section{Tested Architectures}
-We have chosen four architectures, the first two were choosen of the Caffe Zoo Model, a open resource of CNN Architectures, and the last two were choosen of the paper of Ciro Potena and others, sNET and cNET(beetroot).
-So, we have the following results, the net with best results was cNET with 96.4\% of accuracy and 13.72\$ of Loss.
+Four architectures were chosen, the first two were chosen from the Caffe Zoo Model, a open resource of CNN Architectures, and the last two were chosen from the paper by Ciro Potena and others, sNET and cNET(beetroot).
+So, the following results were obtained, the net with the best performance was cNET with 96.4\% of accuracy and 13.72\$ of Loss.
 \section{cNET Performance}
-cNET has 6 million of filters, so cNET can be improved by decresing the number of filtres, also Images can be batched and also Caffe ca be Multithreaded, and both nets were trained with 9000 iterations, so the result were better because the images of the dataset don't have too much features of shape and color to process.
+cNET has 6 million of filters, so cNET can be improved by decresing the number of filtres.
+Also Images can be batched and also Caffe ca be Multithreaded, and both nets were trained with 9000 iterations, so the final result was better because the dataset images don't have too many features of shape and color to process.
 \section{Estimated performance of cNET 16 filters}
-well, like I mentioned before, the nets in Caffe can be tuned, so we have the results with the next parameters and considering that 18 planst can be found in a single image of a row of crop, so.
+well, like I mentioned before, the nets in Caffe can be tuned, so we have performance results with these specific parameters.
+It was considereded that 18 plants can be found in a single image of a row of crop.
 \section{Conclusion}
 \begin{itemize}
-\item cNET showed the best results in classification of maize and weed
+\item cNET had the best performance in classification of maize and weed
 \item The reduction of the number of filters decreased the processing time and increased the network accuracy 
-\item GPU showed the best results, but with Multithreading and Batching CPU and Raspberry Pi can improve its processing time
-\item Due to the limitations of the Raspberry Pi, it can't be used to classify in real time, but a Neural Module(such as Intel Movidius) can improve that result
-\end{itemize}
+\item GPU showed the best results, but with Multithreading and Batching CPU and Raspberry Pi its processing time can be improved 
+\item Due to the limitations of the Raspberry Pi, it can't be used to classify in real time, but a Neural Module(such as Intel Movidius) can improve its performance \end{itemize}
 Thanks!

### 2017-10-18 Presentacion.tex
Cambios finales
cambios 18 de octubre del 2017

@@
 \begin{itemize}
-	\item Acquire  an RGB image through RPi Camera v2.1(Centered to the plant)
+	\item Acquire  an RGB image through RPi Camera v2.1(Centered on the plant)
 
@@
 	\item OTSU Thresholding
-	\item Detect contours and crop image to the contour 
+	\item Detect contours and crop image to obtain its contour 
 	\item Mask image
@@
 	\item A class of deep, feed-forward artificial neural networks
-	\item Tested on classification of plants, \footnote{B.
+	\item Tested for plant classification, \footnote{B.
 Cheng and E.
@@
 \begin{itemize}
-\item cNET showed the best results in classification of maize and weed
+\item cNET had the best performance in maize and weed classification
 \item The reduction of the number of filters decreased the processing time and increased the network accuracy 
